---
title: "Figure 2"
author: "Alex Benecke"
date: "September 6, 2018"
output: html_document
---

### **Figure 2**  Smooth Fits for each variable by strata and maturity (Maybe Sex)

i. display in table of plots Explanatory variables x and strata maturity (and Sex) on Y

Multiple species either multiple plots or overplotted with each other???

#### **Strat 1**

```{r Load Best Strat 1 Models, eval = FALSE, include = FALSE}
filenames_s1 <- list.files(c("output/output_GAM/best/blacknose/strat1",
                             "output/output_GAM/best/blacktip/strat1"
                             ,"output/output_GAM/best/sharpnose/strat1"
                             )
                           , pattern="*.rda", full.names=TRUE)

lapply(filenames_s1, load, .GlobalEnv)


rm( filenames_s1 )

### Create list of models



mod_lst_s1 <- list(bn_mod_s1 = list( # Blacknose
                                       bn_s1_FA_best = bn_s1_FA_best, ## bn s1
                                       bn_s1_FJ_best = bn_s1_FJ_best,
                                       bn_s1_MA_best = bn_s1_MA_best,
                                       bn_s1_MJ_best = bn_s1_MJ_best
                                       )
                ,
                bt_mod_s1 = list(    # Blacktip
                                       bt_s1_FA_best = bt_s1_FA_best, ## bt s1
                                       bt_s1_FJ_best = bt_s1_FJ_best,
                                       bt_s1_MA_best = bt_s1_MA_best,
                                       bt_s1_MJ_best = bt_s1_MJ_best
                                       )
                ,
                sn_mod_s1 = list(    # Sharpnose
                                       sn_s1_FA_best = sn_s1_FA_best, ## sn s1
                                       sn_s1_FJ_best = sn_s1_FJ_best,
                                       sn_s1_MA_best = sn_s1_MA_best,
                                       sn_s1_MJ_best = sn_s1_MJ_best
                                       )
                )

### Check list
length(mod_lst_s1);names(mod_lst_s1)
length(mod_lst_s1[[1]]);names(mod_lst_s1[[1]])
length(mod_lst_s1[[2]]);names(mod_lst_s1[[2]])
length(mod_lst_s1[[3]]);names(mod_lst_s1[[3]])
mod_lst_s1$bn_mod_s1$bn_s1_FA_best


rm(bn_s1_FA_best, bn_s1_FJ_best, bn_s1_MA_best, bn_s1_MJ_best
   ,
   bt_s1_FA_best, bt_s1_FJ_best, bt_s1_MA_best, bt_s1_MJ_best
   ,
   sn_s1_FA_best, sn_s1_FJ_best, sn_s1_MA_best, sn_s1_MJ_best 
   )
```


##### **Blacknose**

**Variable Order**

| Depth | Temperature | Turbidity | Dissolved Oxygen | Salinity | Distance to Shore | Year |
|:-----:|:-----------:|:---------:|:----------------:|:--------:|:-----------------:|:----:|
|  1    |    2        |    3      |       4          |    5     |         6         |   7  |

```{r strat1 Model structures Blacknose Fig2, include = FALSE, eval=FALSE}
## Blacknose
    ## Strat 1
 ## FA
plot(mod_lst_s1$bn_mod_s1$bn_s1_FA_best, pages = 1, scale = 0)
bn_row_1 <- c( 1, 2, 0, 3, 4, 5, 6)
            #  D, T, T, O, S, D, Y
  ## FJ
plot(mod_lst_s1$bn_mod_s1$bn_s1_FJ_best, pages = 1, scale = 0)
bn_row_2 <- c( 7, 8, 0, 0, 0, 9, 10)
            #  D, T, T, O, S, D, Y
  ## MA
plot(mod_lst_s1$bn_mod_s1$bn_s1_MA_best, pages = 1, scale = 0)
bn_row_3 <- c( 11, 12, 13, 14, 15, 16, 17)
            #  D, T, T, O, S, D, Y
  ## MJ
plot(mod_lst_s1$bn_mod_s1$bn_s1_MJ_best, pages = 1, scale = 0)
bn_row_4 <-  c( 18, 19, 0, 20, 0, 21, 22)
            #  D, T, T, O, S, D, Y

(bn_mat_s1 <- matrix(c(bn_row_1, bn_row_2, bn_row_3, bn_row_4),
                  nrow = 4, ncol = 7, byrow = TRUE) )
bn.lay.s1 <- layout( bn_mat_s1 )
layout.show( bn.lay.s1 )
```


##### **Blacktip**

**Variable Order**

| Depth | Temperature | Turbidity | Dissolved Oxygen | Salinity | Distance to Shore | Year |
|:-----:|:-----------:|:---------:|:----------------:|:--------:|:-----------------:|:----:|
|  1    |    2        |    3      |       4          |    5     |         6         |   7  |

```{r strat1 Blacktip Model structures  Fig2, include = FALSE, eval=FALSE}
## Blacktip
    ## Strat 1
 ## FA
plot(mod_lst_s1$bt_mod_s1$bt_s1_FA_best, pages = 1)
bt_row_1 <-   c( 0, 1, 2, 3, 4, 5, 6)
            #  D, T, T, O, S, D, Y
  ## FJ
plot(mod_lst_s1$bt_mod_s1$bt_s1_FJ_best, pages = 1)
bt_row_2 <- c( 7, 8, 9, 10, 0, 11, 12)
            #  D, T, T, O, S, D, Y
  ## MA
plot(mod_lst_s1$bt_mod_s1$bt_s1_MA_best, pages = 1)
bt_row_3 <- c( 13, 14, 15, 16, 0, 17, 18)
            #  D, T, T, O, S, D, Y
  ## MJ
plot(mod_lst_s1$bt_mod_s1$bt_s1_MJ_best, pages = 1)
bt_row_4 <- c( 0, 19, 20, 21, 22, 0, 23)
            #  D, T, T, O, S, D, Y


(bt_mat_s1 <- matrix(c(bt_row_1, bt_row_2, bt_row_3, bt_row_4),
                  nrow = 4, ncol = 7, byrow = TRUE) )
bt.lay.s1 <- layout( bt_mat_s1 )
layout.show( bt.lay.s1 )
```



##### **Sharpnose**

**Variable Order**

| Depth | Temperature | Turbidity | Dissolved Oxygen | Salinity | Distance to Shore | Year |
|:-----:|:-----------:|:---------:|:----------------:|:--------:|:-----------------:|:----:|
|  1    |    2        |    3      |       4          |    5     |         6         |   7  |

```{r strat1 Sharpnose Model structures Fig2, include = FALSE, eval=FALSE}
## Sharpnose
    ## Strat 1
 ## FA
plot(mod_lst_s1$sn_mod_s1$sn_s1_FA_best, pages = 1)
sn_row_1 <- c( 1, 2, 3, 4, 5, 6, 7)
            #  D, T, T, O, S, D, Y
  ## FJ
plot(mod_lst_s1$sn_mod_s1$sn_s1_FJ_best, pages = 1)
sn_row_2 <- c( 8, 9, 10, 0, 0, 0, 11)
            #  D, T, T, O, S, D, Y
  ## MA
plot(mod_lst_s1$sn_mod_s1$sn_s1_MA_best, pages = 1)
sn_row_3 <- c( 12, 13, 14, 15, 16, 0, 17)
            #  D, T, T, O, S, D, Y
  ## MJ
plot(mod_lst_s1$sn_mod_s1$sn_s1_MJ_best, pages = 1)
sn_row_4 <- c( 18, 19, 0, 0, 20, 0, 21)
            #  D, T, T, O, S, D, Y

(sn_mat_s1 <- matrix(c(sn_row_1, sn_row_2, sn_row_3, sn_row_4),
                  nrow = 4, ncol = 7, byrow = TRUE) )
sn.lay.s1 <- layout( sn_mat_s1 )
layout.show( sn.lay.s1 )
```

I will have to make a unique layout for each species. By looking at the formula of the best fit model I've determined which terms are included and will use this information to create a matrix for *layout()*.

##### Figure 2 loop **Strat 1**

```{r Layouts for Figure 2 strat 1, include = FALSE, eval=FALSE}
  # Strat 1
lay_mat_s1 <- list(bn_mat_s1,
                   bt_mat_s1,
                   sn_mat_s1
                   )
```

```{r figure 2 strat 1 tiff file paths, include = FALSE, eval=FALSE}
# Strata 1
file_name_s1 <- numeric( length(lay_mat_s1) )

letr_s1 <- letters[c(seq(1, 14, by = 2))]


for(i in 1:length(file_name_s1) ){
  
  file_name_s1[i] <- paste0("6_figures\\figures\\Figure_2_(",letr_s1[i], ").tiff")
}

file_name_s1
```

```{r  Figure 2 prep strat 1, include=FALSE, eval=FALSE}

cex_txt <- 1
cex_lab <- 1.5
cex_axis <- 1.25
my_lwd <- 1.75
y_line <- 1.25
x_line <- 0

letter_line <- 0
letter_at <- 0

sleep_time <- 0.01
```

```{r Figure 2 Strata 1 plots Loop, include=FALSE, eval = FALSE}
# Strata 1

for(i in 1:length(mod_lst_s1) ){ ## loop through species level of mod_lst_s1
  
  tiff(filename =  file_name_s1[i], height = 2000, width = 2500, res = 300)
  
  par(oma = c(1.5, 3.25, 1.5, 1), # two rows of text at the outer left and bottom margin
    mar = c(1, 1, 1, 1), # space for one row of text at ticks and to separate plots
    mgp = c(1.75, 0.75, 0))
  
  layout( lay_mat_s1[[i]] )
  
    
    for(j in 1:length( mod_lst_s1[[i]] ) ){ ### loop through Sex, and Maturity level of mod_lst_s1 
      
      for(k in 2:8){ ## Loop through specific variables in each level of sex and maturity for specific species
    
    plot(mod_lst_s1[[i]][[j]], select = k,
         scale = 0,
         shade = TRUE,
         xlab = "", ylab = "",
         main = "",
         lwd= my_lwd, 
         cex.axis = cex_axis, 
         cex.lab = cex_lab, 
         bty = "n")
    
    abline( h = 0, col = "blue", lty = 3)  
    
    Sys.sleep(sleep_time)
    
    }
      
    }
    Sys.sleep(sleep_time)
    
    
  
  
  ### Y labels
    mtext("Female Adult ",
        side = 2, 
        at = 0.875,
        line = y_line,
        cex = cex_txt, 
        outer = TRUE)
  
    mtext("Female Juvenile",
        side = 2,
        at = 0.625,
        line = y_line,
        cex = cex_txt,
        outer = TRUE)
    
      mtext("Male Adult",
        side = 2, 
        at = 0.375,
        line = y_line,
        cex = cex_txt,
        outer = TRUE)
      
        mtext("Male Juvenile",
        side = 2, 
        at = 0.125,
        line = y_line,
        cex = cex_txt,
        outer = TRUE)
  ### X Labels
        mtext("Depth",
        side = 3, 
        at = 1/14,
        line = x_line,
        cex = cex_txt,
        outer = TRUE)
        
        mtext("Temp",
        side = 3, 
        at = 3/14,
        line = x_line,
        cex = cex_txt,
        outer = TRUE)
        
        mtext("Turb",
        side = 3, 
        at = 5/14,
        line = x_line,
        cex = cex_txt,
        outer = TRUE)
        
        mtext("Oxy",
        side = 3, 
        at = 1/2,
        line = x_line,
        cex = cex_txt,
        outer = TRUE)
        
        mtext("Sal",
        side = 3, 
        at = 9/14,
        line = x_line,
        cex = cex_txt,
        outer = TRUE)
        
        mtext("Distance",
        side = 3, 
        at = 11/14,
        line = x_line,
        cex = cex_txt,
        outer = TRUE)
       
         mtext("Year",
        side = 3, 
        at = 13/14,
        line = x_line,
        cex = cex_txt,
        outer = TRUE)
        
         ### Figure letter
        mtext(paste0("(", letr_s1[i], ")"),
        side = 3, 
        at = letter_at,
        line = letter_line,
        cex = cex_txt,
        outer = TRUE) 
         
        
        Sys.sleep(sleep_time)
        
        dev.off()
        
}

```




#### **Strat 2** Figure 2

```{r Load Best Strat 2 Models, eval = FALSE, include = FALSE}
filenames_s2 <- list.files(c("output/output_GAM/best/blacknose/strat2",
                             "output/output_GAM/best/blacktip/strat2",
                             "output/output_GAM/best/sharpnose/strat2"), pattern="*.rda", full.names=TRUE)

lapply(filenames_s2, load, .GlobalEnv)

rm( filenames_s2 )


### Create list of models

mod_lst_s2 <- list(bn_mod_s2 = list( # Blacknose
                                       bn_s2_FA_best = bn_s2_FA_best, ## bn s2
                                       bn_s2_FJ_best = bn_s2_FJ_best,
                                       bn_s2_MA_best = bn_s2_MA_best,
                                       bn_s2_MJ_best = bn_s2_MJ_best
                                       )
                ,
                bt_mod_s2 = list(    # Blacktip
                                       bt_s2_FA_best = bt_s2_FA_best, ## bt s2
                                       bt_s2_FJ_best = bt_s2_FJ_best,
                                       bt_s2_MA_best = bt_s2_MA_best,
                                       bt_s2_MJ_best = bt_s2_MJ_best
                                       )
                ,
                sn_mod_s2 = list(    # Sharpnose
                                       sn_s2_FA_best = sn_s2_FA_best, ## sn s2
                                       sn_s2_FJ_best = sn_s2_FJ_best,
                                       sn_s2_MA_best = sn_s2_MA_best,
                                       sn_s2_MJ_best = sn_s2_MJ_best
                                       )
                )
length(mod_lst_s2);names(mod_lst_s2)
length(mod_lst_s2[[1]]);names(mod_lst_s2[[1]])
length(mod_lst_s2[[2]]);names(mod_lst_s2[[2]])
length(mod_lst_s2[[3]]);names(mod_lst_s2[[3]])


rm(bn_s2_FA_best, bn_s2_FJ_best, bn_s2_MA_best, bn_s2_MJ_best
   ,
   bt_s2_FA_best, bt_s2_FJ_best, bt_s2_MA_best, bt_s2_MJ_best
   ,
   sn_s2_FA_best, sn_s2_FJ_best, sn_s2_MA_best, sn_s2_MJ_best)
```


##### **Blacknose**

**Variable Order**

| Depth | Temperature | Turbidity | Dissolved Oxygen | Salinity | Distance to Shore | Year |
|:-----:|:-----------:|:---------:|:----------------:|:--------:|:-----------------:|:----:|
|  1    |    2        |    3      |       4          |    5     |         6         |   7  |

```{r Model structures Blacknose Fig2, include = FALSE, eval=FALSE}
## Blacknose
    ## Strat 2
 ## FA
plot(mod_lst_s2$bn_mod_s2$bn_s2_FA_best, pages = 1)
bn_row_5 <- c( 0, 1, 0, 2, 0, 0, 3)
            #  D, T, T, O, S, D, Y
  ## FJ
plot(mod_lst_s2$bn_mod_s2$bn_s2_FJ_best, pages = 1)
bn_row_6 <- c( 0, 4, 0, 0, 5, 6, 7)
            #  D, T, T, O, S, D, Y
  ## MA
plot(mod_lst_s2$bn_mod_s2$bn_s2_MA_best, pages = 1)
bn_row_7 <- c( 8, 0, 0, 9, 10, 11, 12)
            #  D, T, T, O, S, D, Y
  ## MJ
plot(mod_lst_s2$bn_mod_s2$bn_s2_MJ_best, pages = 1)
bn_row_8 <- c( 0, 0, 13, 14, 15, 0, 16)
            #  D, T, T, O, S, D, Y

(bn_mat_s2 <- matrix(c(bn_row_5, bn_row_6, bn_row_7, bn_row_8),
                  nrow = 4, ncol = 7, byrow = TRUE) )

bn.lay.s2 <- layout( bn_mat_s2 )
layout.show( bn.lay.s2 )
```


##### **Blacktip**

**Variable Order**

| Depth | Temperature | Turbidity | Dissolved Oxygen | Salinity | Distance to Shore | Year |
|:-----:|:-----------:|:---------:|:----------------:|:--------:|:-----------------:|:----:|
|  1    |    2        |    3      |       4          |    5     |         6         |   7  |

```{r Blacktip Model structures  Fig2, include = FALSE, eval=FALSE}
## Blacktip
    ## Strat 2
 ## FA
plot(mod_lst_s2$bt_mod_s2$bt_s2_FA_best, pages = 1)
bt_row_5 <- c( 0, 0, 0, 1, 2, 0, 3)
            #  D, T, T, O, S, D, Y
  ## FJ
plot(mod_lst_s2$bt_mod_s2$bt_s2_FJ_best, pages = 1)
bt_row_6 <- c( 4, 5, 6, 7, 8, 0, 9)
            #  D, T, T, O, S, D, Y
  ## MA
plot(mod_lst_s2$bt_mod_s2$bt_s2_MA_best, pages = 1)
bt_row_7 <- c( 10, 0, 0, 0, 11, 12, 13)
            #  D, T, T, O, S, D, Y
  ## MJ
plot(mod_lst_s2$bt_mod_s2$bt_s2_MJ_best, pages = 1)
bt_row_8 <- c( 14, 0, 15, 16, 17, 0, 18)
            #  D, T, T, O, S, D, Y

(bt_mat_s2 <- matrix(c(bt_row_5, bt_row_6, bt_row_7, bt_row_8),
                  nrow = 4, ncol = 7, byrow = TRUE) )

bt.lay.s2 <- layout( bt_mat_s2 )
layout.show( bt.lay.s2 )
```



##### **Sharpnose**

**Variable Order**

| Depth | Temperature | Turbidity | Dissolved Oxygen | Salinity | Distance to Shore | Year |
|:-----:|:-----------:|:---------:|:----------------:|:--------:|:-----------------:|:----:|
|  1    |    2        |    3      |       4          |    5     |         6         |   7  |

```{r Sharpnose Model structures Fig2, include = FALSE, eval=FALSE}
## Sharpnose
    ## Strat 2
 ## FA
plot(mod_lst_s2$sn_mod_s2$sn_s2_FA_best, pages = 1)
sn_row_5 <- c( 1, 2, 3, 0, 0, 0, 4)
            #  D, T, T, O, S, D, Y
  ## FJ
plot(mod_lst_s2$sn_mod_s2$sn_s2_FJ_best, pages = 1)
sn_row_6 <- c( 0, 5, 6, 0, 0, 7, 8)
            #  D, T, T, O, S, D, Y
  ## MA
plot(mod_lst_s2$sn_mod_s2$sn_s2_MA_best, pages = 1)
sn_row_7 <- c( 9, 0, 10, 0, 0, 0, 11)
            #  D, T, T, O, S, D, Y
  ## MJ
plot(mod_lst_s2$sn_mod_s2$sn_s2_MJ_best, pages = 1)
sn_row_8 <- c( 0, 12, 0, 13, 14, 0, 15)
            #  D, T, T, O, S, D, Y

(sn_mat_s2 <- matrix(c(sn_row_5, sn_row_6, sn_row_7, sn_row_8),
                  nrow = 4, ncol = 7, byrow = TRUE) )

sn.lay.s2 <- layout( sn_mat_s2 )
layout.show( sn.lay.s2 )
```

##### Figure 2 loop **Strat 2**

```{r Layouts for Figure 2 , include = FALSE, eval=FALSE}
# strat 2

lay_mat_s2 <- list(bn_mat_s2,
                   bt_mat_s2,
                   sn_mat_s2
                   )
```

```{r figure 2 tiff file paths, include = FALSE, eval=FALSE}
# Strata 2

file_name_s2 <- numeric( length(lay_mat_s2) )

letr_s2 <- letters[c(seq(2, 14, by = 2))]

for(i in 1:length(file_name_s2) ){
  
  file_name_s2[i] <- paste0("6_figures\\figures\\Figure_2_(",letr_s2[i], ").tiff")
}

file_name_s2
```

```{r  Figure 2 prep, eval=FALSE, include=FALSE}

cex_txt <- 1
cex_lab <- 1.5
cex_axis <- 1.25
my_lwd <- 1.75
y_line <- 1.25
x_line <- 0

letter_line <- 0
letter_at <- 0

sleep_time <- 0.01

```


```{r  Figure 2 Strata 2 plots Loop, include=FALSE, eval = FALSE}
# Strata 2
for(i in 1:length(mod_lst_s2) ){ ### loop through species level in mod_lst_s2
  
  tiff(filename =  file_name_s2[i], height = 2000, width = 2500, res = 300)
  
  par(oma = c(1.5, 3.25, 1.5, 1), # two rows of text at the outer left and bottom margin
    mar = c(1, 1, 1, 1), # space for one row of text at ticks and to separate plots
    mgp = c(1.75, 0.75, 0))
  
  layout( lay_mat_s2[[i]] )
  
for(j in 1:length(mod_lst_s2[[i]])){ ## Loop through Sex and maturity levels for a species
  
  for(k in 2:8){ ## loop through explanatory variables in one level of sex and maturity for a species
    
    plot(mod_lst_s2[[i]][[j]], select = k,
         scale = 0,
         shade = TRUE,
         xlab = "", ylab = "",
         main = "",
         lwd= my_lwd, 
         cex.axis = cex_axis, 
         cex.lab = cex_lab, 
         bty = "n")
    
    abline( h = 0, col = "blue", lty = 3)    
    
  }   
  
} 
  
  
  ### Y labels
    mtext("Female Adult ",
        side = 2, 
        at = 0.875,
        line = y_line,
        cex = cex_txt, 
        outer = TRUE)
  
    mtext("Female Juvenile",
        side = 2,
        at = 0.625,
        line = y_line,
        cex = cex_txt,
        outer = TRUE)
    
      mtext("Male Adult",
        side = 2, 
        at = 0.375,
        line = y_line,
        cex = cex_txt,
        outer = TRUE)
      
        mtext("Male Juvenile",
        side = 2, 
        at = 0.125,
        line = y_line,
        cex = cex_txt,
        outer = TRUE)
  ### X Labels
        mtext("Depth",
        side = 3, 
        at = 1/14,
        line = x_line,
        cex = cex_txt,
        outer = TRUE)
        
        mtext("Temp",
        side = 3, 
        at = 3/14,
        line = x_line,
        cex = cex_txt,
        outer = TRUE)
        
        mtext("Turb",
        side = 3, 
        at = 5/14,
        line = x_line,
        cex = cex_txt,
        outer = TRUE)
        
        mtext("Oxy",
        side = 3, 
        at = 1/2,
        line = x_line,
        cex = cex_txt,
        outer = TRUE)
        
        mtext("Sal",
        side = 3, 
        at = 9/14,
        line = x_line,
        cex = cex_txt,
        outer = TRUE)
        
        mtext("Distance",
        side = 3, 
        at = 11/14,
        line = x_line,
        cex = cex_txt,
        outer = TRUE)
       
         mtext("Year",
        side = 3, 
        at = 13/14,
        line = x_line,
        cex = cex_txt,
        outer = TRUE)
        
         ### Figure letter
        mtext(paste0("(", letr_s2[i], ")"),
        side = 3, 
        at = letter_at,
        line = letter_line,
        cex = cex_txt,
        outer = TRUE) 
         
        
        Sys.sleep(sleep_time)
        
        dev.off()
        
}
```

![**Figure 2 a** Blacknose Strat 1](figures\Figure_2_(a).tiff)

![**Figure 2 b** Blacknose  Strat 2](figures\Figure_2_(b).tiff)


![**Figure 2 c** Blacktip Strat 1](figures\Figure_2_(c).tiff)

![**Figure 2 d** Blacktip  Strat 2](figures\Figure_2_(d).tiff)


![**Figure 2 e** Sharpnose Strat 1](figures\Figure_2_(e).tiff)

![**Figure 2 f** Sharpnose  Strat 2](figures\Figure_2_(f).tiff)















