---
title: "Model Sensitivity to k"
author: "Alex Benecke"
date: "July 26, 2018"
output: 
  html_document:
    df_print: paged
    toc: true
    toc_float: true
    toc_depth: 4
    fig_width: 8
    fig_height: 6
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Load Packages}
library(mgcv)
library(FSA)
library(dplyr)
library(magrittr)
library(tidyverse)

source("5_functions/dropbox_fn.R") # For interacting with dropbox
proj = "shark" # Specify project where data is stored 


```

```{r Load Data}
sn_pos <- read_csv_fn( "data/clean-data/sharpnose.csv", proj) %>%
  subset(pres == 1) %>%
  mutate(YEAR = factor(YEAR), 
         MONTH = factor(strftime(DATE, format = "%b")))



str(sn_pos)
```



The point of this document is to explore the model sensitivity to the selection of $k$. ...

I will randomly select $k$ values for the smooth of Lat and Lon ($ 60 \leq k \leq 80$) and for the smooths of the explanitory variables ($5 \leq k \leq 20$) and use these values to fit 50 global models.
$$g_{1}(y) = g_{2}(Lon, Lat) + \sum^{n}_{i=1} s_{i}(x_{i}) + factor(Bottom ~ Substrate) + re_{yr} + \epsilon $$


First I will need to create a vector of the $k$ values I will test



## Larger range of k's

Lets repeat with a larger range of potential k's


```{r k vectors, eval = FALSE}
n.<- 500
(k_ll <- sample(x = seq(40 , 100, 1), size = n., replace = T))

(k_ex1 <- sample(x = seq(5 , 20, 1), size = n., replace = T))
(k_ex2 <- sample(k_ex1, size = n.))
(k_ex3 <- sample(k_ex1, size = n.))
(k_ex4 <- sample(k_ex1, size = n.))
(k_ex5 <- sample(k_ex1, size = n.))
```

Real quick I will create a list of names


```{r, eval = FALSE}
(names <- numeric(500))

for(i in 1:500){
  
  names[i] <- paste0("model", "_", i)
  
}

names
```

Now I will write a loop that will fit the global gam model 50 times while randomly sellecting a k value from the vector of potential k's I cereated above.
```{r, eval=FALSE}
(random_k_models <- vector("list", 500))

mat. <- c()

system.time(
for(i in 1:500){
  
  random_k_models[[i]] <- gam((cpe +1) ~ s(STARTLON, STARTLAT, k = k_ll[i]) + 
                                s(AVG.DEPTH, k = k_ex1[i]) + 
                                s(TEMPBOTM, k = k_ex2[i]) + 
                                s(TURBBOTM, k = k_ex3[i]) +
                                s(OXYBOTM, k = k_ex4[i]) + 
                                s(SALBOTM, k = k_ex5[i]) + 
                                s(YEAR, bs = "re"),
                              data = sn_pos,
                              family = Gamma(link = log))
  
 mat.[i] <- paste( paste0("model", "_", i), AIC(random_k_models[[i]]), BIC(random_k_models[[i]]), k_ll[i], k_ex1[i], k_ex2[i], k_ex3[i], k_ex4[i], k_ex5[i], sep = ",")
 
write(mat., file = "data/rand.samp.k.val.sim.csv")


}
)
names(random_k_models) <- c(names)


random_k_models$model_1
```
```{r}

#save( random_k_models, file = "output/output_model-building/random_k_models.rda")

load( file = "output/output_model-building/random_k_models.rda")
```


```{r}
k_samp <- read_csv_fn( "data/clean-data/k_data/k_samp.csv", proj) %>%
  arrange(AIC)

head(k_samp)
#str(k_samp)
```


```{r}
edf_Lat_Lon <- numeric(500)
edf_Depth <- numeric(500)
edf_Temp <- numeric(500)
edf_Turb <- numeric(500)
edf_Oxy <- numeric(500)
edf_Sal <- numeric(500)


for(i in 1:length(random_k_models)){
  
  edf_Lat_Lon[i] <- summary(random_k_models[[i]])$edf[1]
  edf_Depth[i] <- summary(random_k_models[[i]])$edf[2]
  edf_Temp[i] <- summary(random_k_models[[i]])$edf[3]
  edf_Turb[i] <- summary(random_k_models[[i]])$edf[4]
  edf_Oxy[i] <- summary(random_k_models[[i]])$edf[5]
  edf_Sal[i] <- summary(random_k_models[[i]])$edf[6]
  
}


plot(edf_Lat_Lon~k_samp$Lat.Lon)
plot(edf_Depth~k_samp$Depth)
plot(edf_Temp~k_samp$Temp)
plot(edf_Turb~k_samp$Turb)
plot(edf_Oxy~k_samp$Oxy)
plot(edf_Sal~k_samp$Sal)
```



Now lets get some summary information about the models

```{r, echo=FALSE}

AIC <- unlist(lapply(random_k_models, function(x) AIC(x)))
  
BIC <- unlist(lapply(random_k_models, function(x) BIC(x)))
  
GCV <- unlist(lapply(random_k_models, function(x) x$gcv.ubre))
  
  
min_AIC <- min(AIC)
  
delta_AIC <- numeric(length(AIC))

for(i in 1:length(AIC)){
  delta_AIC[i] = AIC[i] - min_AIC
  }


### Create results df
  
results <- data.frame(model = names(random_k_models),
                      AIC = AIC,
                      delta_AIC = delta_AIC,
                      GCV = GCV,
                      BIC = BIC) %>%
  arrange(AIC) 
  
results[c(1:10,90:100),] 
```




```{r, eval=TRUE}
all_edf <- lapply(random_k_models, function(x) summary(x)$'edf')

all_edf_vec <- unlist(all_edf)

#write_csv_fn(all_edf_vec, file = "data/clean-data/k_data/all_edf_vec.csv", proj, row.names = FALSE)

#edf_Lat_Lon <- lapply(all_edf, function(x) x[1])

#edf_Explanitory <- lapply(all_edf, function(x) x[c(2:7)])


```

```{r}
#all_edf <- read_csv_fn("data/clean-data/k_data/all_edf_vec.csv", proj) 



par(mfrow = c(1,1))

hist(unlist(all_edf), breaks = seq(0,60,1), xaxt="n")
axis(1, at=seq(0,60,1))
```

```{r}
### edf for lat lon smooth

edf_Lat_Lon <- lapply(all_edf, function(x) x[1])

#edf_Lat_Lon

range(unlist(edf_Lat_Lon))

hist(unlist(edf_Lat_Lon),breaks = seq(29,57,0.1), xaxt="n")
axis(1, at=seq(29,57,1))

```

```{r}
### edf for Explanitory variables

edf_Explanitory <- lapply(all_edf, function(x) x[c(2:7)])

#edf_Explanitory

range(unlist(edf_Explanitory))

hist(unlist(edf_Explanitory), breaks = seq(0,15,1), xaxt="n")
axis(1, at=seq(0,15,1))


  ### edf for individual explanatory variables
v2 <- numeric(500)
v3 <- numeric(500)
v4 <- numeric(500)
v5 <- numeric(500)
v6 <- numeric(500)


for(i in 1:length(edf_Explanitory)){
  
  v2[i] <- edf_Explanitory[[i]][1]
  v3[i] <- edf_Explanitory[[i]][2]
  v4[i] <- edf_Explanitory[[i]][3]
  v5[i] <- edf_Explanitory[[i]][4]
  v6[i] <- edf_Explanitory[[i]][5]
  
}

Explanitory <- list(Depth = v2,
                        Temp = v3,
                        Turb = v4,
                        Oxy = v5,
                        Sal = v6)

par(mfrow = c(3,2))

for(i in 1:5){
  hist(Explanitory[[i]], main = names(Explanitory[i]))
}
```




Best model by AIC
```{r}
results[c(1:41),]


mod_262 <- random_k_models$model_262

gam.check(mod_262)

plot(mod_262)
```


Best Model by BIC

```{r}
BIC_results <- results %>% arrange(BIC) 


BIC_results[c(1:5),]


mod_463 <- random_k_models$model_463

gam.check(mod_463)

plot(mod_463)
```

This looks a bit Beter



