---
title: "Model Structure"
author: "Alex Benecke"
date: "August 21, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r Load Packages, include=FALSE}
require(FSA)
require(tidyverse)
require(dplyr)
require(magrittr)
require(scales)
require(pipeR)
require(kableExtra)
require(mgcv)



source("5_functions/dropbox_fn.R") # For interacting with dropbox
proj = "shark" # Specify project where data is stored 

source("5_functions/load_data.R")

source("5_functions/model_selection_fn.R")
```

```{r Load Data, results = 'hide'}
eff3 <- read_csv_fn( "data/clean-data/CPUE3.csv", proj, na.strings = c(NA, "")) %>%
  mutate(year = factor(year),
         pres = factor(pres), 
         month = ordered(month,
                         levels = c("Jul", "Aug", "Sep", "Oct", "Nov") )
         )


str(eff3)
headtail(eff3)

strat1_Adult <- load_data(data = eff3[eff3$maturity == "A",], strata = 1)
strat2_Adult <- load_data(data = eff3[eff3$maturity == "A",], strata = 2)

strat1_Juvenile <- load_data(data = eff3[eff3$maturity == "J",], strata = 1)
strat2_Juvenile <- load_data(data = eff3[eff3$maturity == "J",], strata = 2)
```


  I want to test various expinential family distributions to find out which one is the best. I think I want binomial with logit link for strata 1
However, I have seen a wide range of distributions used for strata 2 including Tweed with identity link, and negative binomial with log link vs the gamma with a log link I've been using. 

Next I want to find out if using a mean centered or standardized response variable is better than the un altered response.

Finnaly, what if any transformations of explanatory variables are preferable.


** I also need to Check if I can use by = Maturity in model so that I can fit smooths for each level of Maturity with less models. **


### **strata 1 Note** ###
https://www.statmethods.net/advstats/glm.html

Logistic Regression

Logistic regression is useful when you are predicting a binary outcome from a set of continuous predictor variables. It is frequently preferred over discriminant function analysis because of its less restrictive assumptions.
```{r}
# Logistic Regression
# where F is a binary factor and
# x1-x3 are continuous predictors
fit <- glm(F~x1+x2+x3,data=mydata,family=binomial())
summary(fit) # display results
confint(fit) # 95% CI for the coefficients
exp(coef(fit)) # exponentiated coefficients
exp(confint(fit)) # 95% CI for exponentiated coefficients
predict(fit, type="response") # predicted values
residuals(fit, type="deviance") # residuals
```

You can use **anova(fit1,fit2, test="Chisq")** to compare nested models. 

Additionally, cdplot(F~x, data=mydata) will display the conditional density plot of the binary outcome F on the continuous x variable.

###############

## Finding the best Theoretical distribution for my data

see https://stats.stackexchange.com/questions/132652/how-to-determine-which-distribution-fits-my-data-best

```{r Load additional packages}
library(fitdistrplus)
library(logspline)
```
```{r Isolate Response variable}
### CPUE
cpe <- eff3$CPUE

cpe.bn <- strat2_Adult$Female$blacknose$CPUE
cpe.bt <- strat2_Adult$Female$blacktip$CPUE
cpe.bu <- strat2_Adult$Female$bull$CPUE
cpe.sb <- strat2_Adult$Female$sandbar$CPUE
cpe.sn <- strat2_Adult$Female$sharpnose$CPUE
cpe.sp <- strat2_Adult$Female$spinner$CPUE
cpe.ti <- strat2_Adult$Female$tiger$CPUE



str(cpe)

### presence absence
pa <- eff3$pres
str(pa)
```



### PA dist

```{r}
descdist(pa, discrete = TRUE)

fit.poi <- fitdist(pa,
                     "pois") 

fit.nbiom <- fitdist(pa,
                     "nbinom")

#fit.binom <- fitdist(pa,
#                     "binom")

plot(fit.poi)
plot(fit.nbiom)

summary(fit.poi)
summary(fit.nbiom)
```



### CPUE dist
Lets fit A Gamma and weibull (Maybe norrmal) distribution

Possible distributions 
"norm", "lnorm", "pois", "exp", "gamma", "nbinom", "geom",
"beta", "unif", "logis"

#### Combined cpe
```{r}
### cpe
descdist(cpe, discrete = FALSE)

fit.weibull <- fitdist(cpe, "weibull", 
                       method = "mle", 
                       lower = c(0, 0),
                       start = list(scale = 1, shape = 1))
fit.gamma <- fitdist(cpe, "gamma", 
                     method = "mle", 
                     lower = c(0, 0), 
                     start = list(scale = 1, shape = 1))
fit.norm <- fitdist(cpe, "norm")

#fit.nb <- fitdist(cpe, "nb")


plot(fit.weibull)
plot(fit.gamma)
plot(fit.norm)

```

#### Blacknose cpe
```{r}
### bn
descdist(cpe.bn, discrete = FALSE)

fit.weibull.bn <- fitdist(cpe.bn, "weibull", 
                       method = "mle")
fit.gamma.bn <- fitdist(cpe.bn, "gamma", 
                     method = "mle")
fit.norm.bn <- fitdist(cpe.bn, "norm")

plot(fit.weibull.bn)
plot(fit.gamma.bn)
plot(fit.norm.bn)

summary(fit.weibull.bn)
summary(fit.gamma.bn)
summary(fit.norm.bn)
```

Gamma looks like the best here

#### Blacktip cpe
```{r}
descdist(cpe.bt, discrete = FALSE) ### looks like gamma ?or maybe weible?

fit.weibull.bt <- fitdist(cpe.bt, "weibull", 
                       method = "mle")
fit.gamma.bt <- fitdist(cpe.bt, "gamma", 
                     method = "mle")
fit.norm.bt <- fitdist(cpe.bt, "norm")

plot(fit.weibull.bt)
plot(fit.gamma.bt)
plot(fit.norm.bt)

summary(fit.weibull.bt)
summary(fit.gamma.bt)
summary(fit.norm.bt)

```

Gamma looks like the best here

#### Bull cpe
```{r}
descdist(cpe.bu, discrete = FALSE) ### maybe lognormal

fit.weibull.bu <- fitdist(cpe.bu, "weibull", 
                       method = "mle")
fit.lnorm.bu <- fitdist(cpe.bu, "lnorm")

fit.gamma.bu <- fitdist(cpe.bu, "gamma", 
                     method = "mle")
fit.norm.bu <- fitdist(cpe.bu, "norm")

plot(fit.weibull.bu)
plot(fit.lnorm.bu)
plot(fit.gamma.bu)
plot(fit.norm.bu)

summary(fit.weibull.bu)
summary(fit.lnorm.bu)
summary(fit.gamma.bu)
summary(fit.norm.bu)

```
Best is normal then weibull, and gamma

#### sandbar cpe
```{r}
descdist(cpe.sb, discrete = FALSE)

fit.weibull.sb <- fitdist(cpe.sb, "weibull", 
                       method = "mle")
fit.gamma.sb <- fitdist(cpe.sb, "gamma", 
                     method = "mle")
fit.norm.sb <- fitdist(cpe.sb, "norm")

plot(fit.weibull.sb)
plot(fit.gamma.sb)
plot(fit.norm.sb)

summary(fit.weibull.sb)
summary(fit.gamma.sb)
summary(fit.norm.sb)
```
Gamma looks like the best here

#### sharpnose cpe
```{r}
descdist(cpe.sn, discrete = FALSE)

fit.weibull.sn <- fitdist(cpe.sn, "weibull", 
                       method = "mle")
fit.gamma.sn <- fitdist(cpe.sn, "gamma", 
                     method = "mle")
fit.norm.sn <- fitdist(cpe.sn, "norm")
fit.exp.sn <- fitdist(cpe.sn, "exp")

plot(fit.weibull.sn)
plot(fit.gamma.sn)
plot(fit.norm.sn)
plot(fit.exp.sn)

summary(fit.weibull.sn)
summary(fit.gamma.sn)
summary(fit.norm.sn)
summary(fit.exp.sn)

```
Weibull looks best here Gamma is close


#### spinner cpe
```{r}
descdist(cpe.sp, discrete = FALSE)

fit.weibull.sp <- fitdist(cpe.sp, "weibull", 
                       method = "mle")
fit.gamma.sp <- fitdist(cpe.sp, "gamma", 
                     method = "mle")
fit.norm.sp <- fitdist(cpe.sp, "norm")
fit.exp.sp <- fitdist(cpe.sp, "exp")

plot(fit.weibull.sp)
plot(fit.gamma.sp)
plot(fit.norm.sp)
plot(fit.exp.sp)

summary(fit.weibull.sp)
summary(fit.gamma.sp)
summary(fit.norm.sp)
summary(fit.exp.sp)

```
Gamma looks like the best here

#### tiger cpe
```{r}
descdist(cpe.ti, discrete = FALSE)

fit.weibull.ti <- fitdist(cpe.ti, "weibull", 
                       method = "mle")
fit.gamma.ti <- fitdist(cpe.ti, "gamma", 
                     method = "mle")
fit.norm.ti <- fitdist(cpe.ti, "norm")

plot(fit.weibull.ti)
plot(fit.gamma.ti)
plot(fit.norm.ti)


summary(fit.weibull.ti)
summary(fit.gamma.ti)
summary(fit.norm.ti)


```
All very close normal looks best but really no difference

I expect the CPUE to have the same distribution for all species and so far Gamma seems to be the leader.






### Strata 1 Adult Female
```{r}
sn.S1FA.dat <- strat1_Adult$Female$sharpnose


system.time(
binomial.fit <- gam(pres ~ s(startlon, startlat, k = 40) +
                      s(startdepth, k = 5) +
                      s(tempbotm, k = 5) +
                      s(turbbotm, k = 5) +
                      s(oxybotm, k = 5) +
                      s(salbotm, k = 5) +
                      s(Dis.to.SHORE, k = 5) +
                      bottype4 + 
                      s(year, bs = "re"),
                    data = sn.S1FA.dat,
                    family = binomial(link = logit))
)
```
   user  system elapsed 
  19.06    0.81   20.14 
  
```{r}
summary(binomial.fit)

AIC(binomial.fit)

par(mfrow = c(2,2))
gam.check(binomial.fit)

```


### Strata 2 Adult Female
```{r}
s2.response <- "(CPUE + 1)"

s2.smooth.terms <- c("s(startlon, startlat, k = ( k_i[[i]]['k_0','Lat_Lon'] + 35))",
                     "s(I(startdepth^0.25), k = k_i[[i]]['k_0', 'Root_Dep'])",
                      "s(tempbotm, k = k_i[[i]]['k_0', 'Temp'])",
                      "s(turbbotm, k = k_i[[i]]['k_0', 'Turb'])",
                      "s(oxybotm, k = k_i[[i]]['k_0', 'Oxy'])",
                      "s(salbotm, k = k_i[[i]]['k_0', 'Sal'])",
                      "s(Dis.to.SHORE, k = k_i[[i]]['k_0', 'Dis'])",
                     "bottype4")

s2.smooth.terms <- c("s(startlon, startlat, k = 40)",
                     "s(I(startdepth^0.25), k = 5)",
                      "s(tempbotm, k = 5)",
                      "s(turbbotm, k = 5)",
                      "s(oxybotm, k = 5)",
                      "s(salbotm, k = 5)",
                      "s(Dis.to.SHORE, k = 5)",
                     "bottype4")

s2.re.var <- "s(year, bs = 're')"  
  

s2.smooth_names <- c("Lat_Lon","Root_Dep", "Temp", "Turb", "Oxy", "Sal", "Dis", "Bottm")

s2.re.smooth.name <- "yr"

s2.family <- Gamma(link = log) 

sn.FA.dat <- strat2_Adult$Female$sharpnose
```

#### Gamma Dist
```{r}
system.time(
gamma.fit <- gam((CPUE + 1) ~ s(startlon, startlat, k = 40) +
                   s(startdepth, k = 5) +
                   s(tempbotm, k = 5) +
                   s(turbbotm, k = 5) +
                   s(oxybotm, k = 5) +
                   s(salbotm, k = 5) +
                   s(Dis.to.SHORE, k = 5) +
                   bottype4 + 
                   s(year, bs = "re"),
                 data = sn.FA.dat,
                 family = Gamma(link = log))
)

```
   user  system elapsed 
   2.73    0.05    2.84 


### Tweedie Dist
```{r}
system.time(
  
  twd.fit <- gam((CPUE + 1) ~ s(startlon, startlat, k = 40) +
                   s(startdepth, k = 5) +
                   s(tempbotm, k = 5) +
                   s(turbbotm, k = 5) +
                   s(oxybotm, k = 5) +
                   s(salbotm, k = 5) +
                   s(Dis.to.SHORE, k = 5) +
                   bottype4 + 
                   s(year, bs = "re"),
                 data = sn.FA.dat,
                 family = tw(link = "identity"))
  
)
```
   user  system elapsed 
  19.56    0.05   19.75 


### Negbinomial

try *nb*

```{r, eval = FALSE}
system.time(
  
  nbnm.fit <- gam((CPUE + 1) ~ s(startlon, startlat, k = 40) +
                   s(startdepth, k = 5) +
                   s(tempbotm, k = 5) +
                   s(turbbotm, k = 5) +
                   s(oxybotm, k = 5) +
                   s(salbotm, k = 5) +
                   s(Dis.to.SHORE, k = 5) +
                   bottype4 + 
                   s(year, bs = "re"),
                 data = sn.FA.dat,
                 family = negative.binomial(link = log))
  
)
```


### Compare model fits

```{r}
summary(gamma.fit) ###
summary(twd.fit)

AIC(gamma.fit)
AIC(twd.fit)

par(mfrow = c(2,2))
gam.check(gamma.fit)

gam.check(twd.fit)
```


I think I'll stick to Gamma



## Using *'by = maturity'* in smooths
```{r}
eff3 <- read_csv_fn( "data/clean-data/CPUE3.csv", proj, na.strings = c(NA, "")) %>%
  mutate(year = factor(year, ordered = TRUE),
         pres = factor(pres), 
         month = ordered(month,
                         levels = c("Jul", "Aug", "Sep", "Oct", "Nov") )
         )


str(eff3)
headtail(eff3)

strat1 <- load_data(data = eff3, strata = 1)
str(strat1$Female$sharpnose)

strat2 <- load_data(data = eff3, strata = 2)
str(strat2$Female$sharpnose)


sn_s2M <- strat2$Male$sharpnose %>% subset( maturity == "A" | maturity == "J") %>% droplevels()
str(sn_s2M)

sn_s2MA<- strat2$Male$sharpnose %>% subset( maturity == "A" ) %>% droplevels()
str(sn_s2MA)


sn_s2MJ <- strat2$Male$sharpnose %>% subset( maturity == "J" ) %>% droplevels()
str(sn_s2MJ)


```


I want to see what my output will be if I include a 'by = maturity' term in the smooths for my explanatory variables. Since maturity is a factor variable I will need to include it as a main effect.

```{r Fit GAM by maturity Male sn S2}
system.time(
fit_by_mat_M <- gam((CPUE + 1) ~ s(startlon, startlat, k = 40, by = maturity) +
                      s(startdepth, k = 5, by = maturity) +
                      s(tempbotm, k = 5, by = maturity) +
                      s(turbbotm, k = 5, by = maturity) +
                      s(oxybotm, k = 5, by = maturity) +
                      s(salbotm, k = 5, by = maturity) +
                      s(Dis.to.SHORE, k = 5, by = maturity) +
                      bottype4 +
                      maturity +
                      s(year, bs = "re", by = maturity),
                    data = sn_s2M,
                    family = Gamma(link = log))
)
```
   user  system elapsed 
  39.13    0.77   40.52 
  
  **just Adult and Juveniles**
   user  system elapsed 
  15.76    0.38   16.27 

```{r}
fit_by_mat_M

summary(fit_by_mat_M)

par(mfrow = c(2,2))
gam.check(fit_by_mat_M)
```
```{r}
plot(fit_by_mat_M, 
     pages = 1)

par(mfrow = c(2,2))
par(mfrow = c(1,1))

plot(fit_by_mat_M,
     select = 1)

plot(fit_by_mat_M,
     select = 2)

plot(fit_by_mat_M,
     select = 3)


```



Certainly seems to reduce the amount of models I have to deal with but may pose a problem if a term is significant for one level of maturity but not another.



```{r Fit GAM by maturity Male Adult sn S2}
system.time(
fit_by_mat_MA <- gam((CPUE + 1) ~ s(startlon, startlat, k = 40) +
                      s(startdepth, k = 5) +
                      s(tempbotm, k = 5) +
                      s(turbbotm, k = 5) +
                      s(oxybotm, k = 5) +
                      s(salbotm, k = 5) +
                      s(Dis.to.SHORE, k = 5) +
                      bottype4 +
                      s(year, bs = "re"),
                    data = sn_s2MA,
                    family = Gamma(link = log))
)
```

   user  system elapsed 
   2.53    0.06    2.62

```{r Fit GAM by maturity Male Juvenile sn S2}
system.time(
fit_by_mat_MJ <- gam((CPUE + 1) ~ s(startlon, startlat, k = 40) +
                      s(startdepth, k = 5) +
                      s(tempbotm, k = 5) +
                      s(turbbotm, k = 5) +
                      s(oxybotm, k = 5) +
                      s(salbotm, k = 5) +
                      s(Dis.to.SHORE, k = 5) +
                      bottype4 +
                      s(year, bs = "re"),
                    data = sn_s2MJ,
                    family = Gamma(link = log))
)
```
   user  system elapsed 
   0.90    0.00    0.95

```{r}
AIC(fit_by_mat_M, fit_by_mat_MA, fit_by_mat_MJ) ### maybe not super informative

summary(fit_by_mat_M) ### 44.2%
summary(fit_by_mat_MA) ### 35.2%
summary(fit_by_mat_MJ) ### 35.1%


par(mfrow = c(2,2))
### lat Lon
plot(fit_by_mat_M, select = 1)
plot(fit_by_mat_M, select = 2)

plot(fit_by_mat_MA, select = 1)
plot(fit_by_mat_MJ, select = 1)

### depth
par(mfrow = c(2,2))

plot(fit_by_mat_M, select = 3)
plot(fit_by_mat_M, select = 4)

plot(fit_by_mat_MA, select = 2)
plot(fit_by_mat_MJ, select = 2)

### salinity
par(mfrow = c(2,2))

plot(fit_by_mat_M, select = 11)
abline(h = 0, col = "red", lty = 3)
plot(fit_by_mat_M, select = 12)
abline(h = 0, col = "red", lty = 3)

plot(fit_by_mat_MA, select = 6)
abline(h = 0, col = "red", lty = 3)
plot(fit_by_mat_MJ, select = 6)
abline(h = 0, col = "red", lty = 3)
```

I think it would be best to fit the models seperatly for Adults and Juveniles. Juveniles seem to be fit very differently when included with 'by = matyrity' rather than being fit on their own. Also as you can see for **salinity** the smooth is important for Adults but not Juveniles. I would want to remove the term from the juvenile model.(Although I may be anle to do this with select = TRUE this would slow down the computation significantly.)



## Link functions

https://stats.stackexchange.com/questions/141181/glm-verifying-a-choice-of-distribution-and-link-function#141221

Link functions for Gamma are, inverse, identity and log.

### Log Link

```{r log link}
system.time(
log_sn_MJ <- gam((CPUE + 1) ~ s(startlon, startlat, k = 40) +
                      s(startdepth, k = 5) +
                      s(tempbotm, k = 5) +
                      s(turbbotm, k = 5) +
                      s(oxybotm, k = 5) +
                      s(salbotm, k = 5) +
                      s(Dis.to.SHORE, k = 5) +
                      bottype4 +
                      s(year, bs = "re"),
                    data = sn_s2MA,
                    family = Gamma(link = log))
)
```
   user  system elapsed 
   2.60    0.00    2.65
   
```{r log2 link}
system.time(
log2_sn_MJ <- gam(CPUE ~ s(startlon, startlat, k = 40) +
                      s(startdepth, k = 5) +
                      s(tempbotm, k = 5) +
                      s(turbbotm, k = 5) +
                      s(oxybotm, k = 5) +
                      s(salbotm, k = 5) +
                      s(Dis.to.SHORE, k = 5) +
                      bottype4 +
                      s(year, bs = "re"),
                    data = sn_s2MA,
                    family = Gamma(link = log))
)
```
   user  system elapsed 
   0.85    0.00    0.89    

### Inverse Link 
 
```{r inverse link}
system.time(
inv_sn_MJ <- gam((CPUE + 1) ~ s(startlon, startlat, k = 40) +
                      s(startdepth, k = 5) +
                      s(tempbotm, k = 5) +
                      s(turbbotm, k = 5) +
                      s(oxybotm, k = 5) +
                      s(salbotm, k = 5) +
                      s(Dis.to.SHORE, k = 5) +
                      bottype4 +
                      s(year, bs = "re"),
                    data = sn_s2MA,
                    family = Gamma(link = inverse))
)
```
   user  system elapsed 
   0.82    0.00    0.85 

```{r inverse2 link}
system.time(
inv2_sn_MJ <- gam(CPUE ~ s(startlon, startlat, k = 40) +
                      s(startdepth, k = 5) +
                      s(tempbotm, k = 5) +
                      s(turbbotm, k = 5) +
                      s(oxybotm, k = 5) +
                      s(salbotm, k = 5) +
                      s(Dis.to.SHORE, k = 5) +
                      bottype4 +
                      s(year, bs = "re"),
                    data = sn_s2MA,
                    family = Gamma(link = inverse))
)
```
   user  system elapsed 
   0.78    0.00    0.81 
 
### Identity Link   
   
```{r identity link}
system.time(
id_sn_MJ <- gam((CPUE + 1) ~ s(startlon, startlat, k = 40) +
                      s(startdepth, k = 5) +
                      s(tempbotm, k = 5) +
                      s(turbbotm, k = 5) +
                      s(oxybotm, k = 5) +
                      s(salbotm, k = 5) +
                      s(Dis.to.SHORE, k = 5) +
                      bottype4 +
                      s(year, bs = "re"),
                    data = sn_s2MA,
                    family = Gamma(link = identity))
)
```
   user  system elapsed 
   3.84    0.00    3.89 
   
Warning messages:
1: In log(ifelse(y == 0, 1, y/mu)) : NaNs produced
2: Step size truncated due to divergence 
3: In log(ifelse(y == 0, 1, y/mu)) : NaNs produced
4: Step size truncated due to divergence

```{r identity2 link}
system.time(
id2_sn_MJ <- gam(CPUE ~ s(startlon, startlat, k = 40) +
                      s(startdepth, k = 5) +
                      s(tempbotm, k = 5) +
                      s(turbbotm, k = 5) +
                      s(oxybotm, k = 5) +
                      s(salbotm, k = 5) +
                      s(Dis.to.SHORE, k = 5) +
                      bottype4 +
                      s(year, bs = "re"),
                    data = sn_s2MA,
                    family = Gamma(link = identity))
)

```
   user  system elapsed 
   4.11    0.00    4.13 
   
Warning messages:
1: In log(ifelse(y == 0, 1, y/mu)) : NaNs produced
2: Step size truncated due to divergence 
3: In log(ifelse(y == 0, 1, y/mu)) : NaNs produced
4: In log(ifelse(y == 0, 1, y/mu)) : NaNs produced
5: In log(ifelse(y == 0, 1, y/mu)) : NaNs produced
6: Step size truncated due to divergence 
7: In log(ifelse(y == 0, 1, y/mu)) : NaNs produced
8: In log(ifelse(y == 0, 1, y/mu)) : NaNs produced

### Comparing Link Functions

```{r}
AIC(log_sn_MJ, inv_sn_MJ, id_sn_MJ)
AIC(log2_sn_MJ, inv2_sn_MJ, id2_sn_MJ)

anova.gam(log_sn_MJ, inv_sn_MJ, id_sn_MJ, test = "F")
anova.gam(log2_sn_MJ, inv2_sn_MJ, id2_sn_MJ, test = "F")

```

Looks like the inverse link function has the lowest AIC followed by log then identity. AIC is lower when I dont add 1 to CPUE which I no longer have to do since I removed the zeros.

```{r}
summary(log2_sn_MJ)
summary(inv2_sn_MJ)
summary(id2_sn_MJ)
```

The inverse link has the Lowest GCV and Highest R^2 and percent Deviance Explained.

```{r}
par(mfrow = c(2,2))

gam.check(log2_sn_MJ)
gam.check(inv2_sn_MJ)
gam.check(id2_sn_MJ)
```

I think the plot of Response vs Fitted Values looks better with the log link so I'm going to stick with that for now.

### Strata 1

the binomial family the links logit, probit, cauchit, (corresponding to logistic, normal and Cauchy CDFs respectively) log and cloglog (complementary log-log

```{r}
sn_s2F <- strat2$Female$sharpnose %>% subset( maturity == "A" | maturity == "J" ) %>% droplevels()
str(sn_s2F)

sn_s2FA <- strat2$Female$sharpnose %>% subset( maturity == "A" ) %>% droplevels()
str(sn_s2FA)

sn_s2FJ <- strat2$Female$sharpnose %>% subset( maturity == "J" ) %>% droplevels()
str(sn_s2FJ)

```

### logit
```{r logit link}
system.time(
logit_sn_FA <- gam(pres ~ s(startlon, startlat, k = 40) +
                      s(startdepth, k = 5) +
                      s(tempbotm, k = 5) +
                      s(turbbotm, k = 5) +
                      s(oxybotm, k = 5) +
                      s(salbotm, k = 5) +
                      s(Dis.to.SHORE, k = 5) +
                      bottype4 +
                      s(year, bs = "re"),
                    data = sn_s2FA,
                    family = binomial(link = logit))
)
```
   user  system elapsed 
   0.38    0.00    0.39 


### probit
```{r probit link}
system.time(
probit_sn_FA <- gam(pres ~ s(startlon, startlat, k = 40) +
                      s(startdepth, k = 5) +
                      s(tempbotm, k = 5) +
                      s(turbbotm, k = 5) +
                      s(oxybotm, k = 5) +
                      s(salbotm, k = 5) +
                      s(Dis.to.SHORE, k = 5) +
                      bottype4 +
                      s(year, bs = "re"),
                    data = sn_s2FA,
                    family = binomial(link = probit))
)
```
   user  system elapsed 
   0.40    0.00    0.41 

### cauchit
```{r cauchit link}
system.time(
cauch_sn_FA <- gam(pres ~ s(startlon, startlat, k = 40) +
                      s(startdepth, k = 5) +
                      s(tempbotm, k = 5) +
                      s(turbbotm, k = 5) +
                      s(oxybotm, k = 5) +
                      s(salbotm, k = 5) +
                      s(Dis.to.SHORE, k = 5) +
                      bottype4 +
                      s(year, bs = "re"),
                    data = sn_s2FA,
                    family = binomial(link = cauchit))
)
```
   user  system elapsed 
   0.95    0.02    1.03 

### log
```{r log link}
system.time(
log_sn_FA <- gam(pres ~ s(startlon, startlat, k = 40) +
                      s(startdepth, k = 5) +
                      s(tempbotm, k = 5) +
                      s(turbbotm, k = 5) +
                      s(oxybotm, k = 5) +
                      s(salbotm, k = 5) +
                      s(Dis.to.SHORE, k = 5) +
                      bottype4 +
                      s(year, bs = "re"),
                    data = sn_s2FA,
                    family = binomial(link = log))
)
```
   user  system elapsed 
   0.41    0.00    0.40 
   
### cloglog   
```{r cloglog link}
system.time(
cloglog_sn_FA <- gam(pres ~ s(startlon, startlat, k = 40) +
                      s(startdepth, k = 5) +
                      s(tempbotm, k = 5) +
                      s(turbbotm, k = 5) +
                      s(oxybotm, k = 5) +
                      s(salbotm, k = 5) +
                      s(Dis.to.SHORE, k = 5) +
                      bottype4 +
                      s(year, bs = "re"),
                    data = sn_s2FA,
                    family = binomial(link = cloglog))
)
```
   user  system elapsed 
   0.41    0.00    0.40

### compare strat 1 link models
```{r}
anova.gam(logit_sn_FA, probit_sn_FA, cauch_sn_FA, log_sn_FA, cloglog_sn_FA, test = "Chisq")

AIC(logit_sn_FA, probit_sn_FA, cauch_sn_FA, log_sn_FA, cloglog_sn_FA)
```
```{r}
summary(logit_sn_FA)
summary(probit_sn_FA)
summary(cauch_sn_FA)
summary(log_sn_FA)
summary(cloglog_sn_FA)


gam.check(logit_sn_FA)
gam.check(probit_sn_FA)
gam.check(cauch_sn_FA)
gam.check(log_sn_FA)
gam.check(cloglog_sn_FA)


```


Ya IDK i'll come back to this



## GCV vs ML vs REML

family.mgcv {mgcv}


smoothing parameter estimation by "REML" or "ML" (the latter does not integrate the unpenalized and parameteric effects out of the marginal likelihood optimized for the smoothing parameters)

```{r inverse2 link}
system.time(
default_sn_MJ <- gam(CPUE ~ s(startlon, startlat, k = 40) +
                      s(startdepth, k = 5) +
                      s(tempbotm, k = 5) +
                      s(turbbotm, k = 5) +
                      s(oxybotm, k = 5) +
                      s(salbotm, k = 5) +
                      s(Dis.to.SHORE, k = 5) +
                      bottype4 +
                      s(year, bs = "re"),
                    data = sn_s2MA,
                    family = Gamma(link = inverse))
)
```
   user  system elapsed 
   1.98    0.04    2.04 

```{r ML link}
system.time(
ML_sn_MJ <- gam(CPUE ~ s(startlon, startlat, k = 40) +
                      s(startdepth, k = 5) +
                      s(tempbotm, k = 5) +
                      s(turbbotm, k = 5) +
                      s(oxybotm, k = 5) +
                      s(salbotm, k = 5) +
                      s(Dis.to.SHORE, k = 5) +
                      bottype4 +
                      s(year, bs = "re"),
                    data = sn_s2MA,
                    family = Gamma(link = inverse),
                method = "ML")
)
```
   user  system elapsed 
   2.02    0.02    2.06 
Warning messages:
1: In log(ifelse(y == 0, 1, y/mu)) : NaNs produced
2: Step size truncated due to divergence 
3: In log(ifelse(y == 0, 1, y/mu)) : NaNs produced
4: Step size truncated due to divergence 

```{r REML link}
system.time(
REML_sn_MJ <- gam(CPUE ~ s(startlon, startlat, k = 40) +
                      s(startdepth, k = 5) +
                      s(tempbotm, k = 5) +
                      s(turbbotm, k = 5) +
                      s(oxybotm, k = 5) +
                      s(salbotm, k = 5) +
                      s(Dis.to.SHORE, k = 5) +
                      bottype4 +
                      s(year, bs = "re"),
                    data = sn_s2MA,
                    family = Gamma(link = inverse),
                  method = "REML")
)
```
   user  system elapsed 
   3.10    0.08    3.20 
Warning messages:
1: In log(ifelse(y == 0, 1, y/mu)) : NaNs produced
2: Step size truncated due to divergence 

```{r}
anova.gam(default_sn_MJ, ML_sn_MJ, REML_sn_MJ, test = "F")

AIC(default_sn_MJ, ML_sn_MJ, REML_sn_MJ)
```
```{r}
summary(default_sn_MJ)
summary(ML_sn_MJ)
summary(REML_sn_MJ)


gam.check(default_sn_MJ)
gam.check(ML_sn_MJ)
gam.check(REML_sn_MJ)
```

Just goint to stich to default












