---
title: "Year Residual Analysis - Selecting Model Structure"
author: "Alex Benecke"
date: "September 20, 2018"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 5    
---

```{r Load Packages, include=FALSE, eval=TRUE}

### Load Packages
library(FSA)
library(tidyverse)
library(dplyr)
library(magrittr)
library(scales)
library(mgcv)
library(sciplot)

### Load My Functions
source("5_functions/dropbox_fn.R") # For interacting with dropbox
proj = "shark" # Specify project where data is stored 

source("5_functions/load_data.R")
```

```{r Load Data, echo=FALSE, include=FALSE, eval=TRUE}
#### Load Combined Data ####
eff3 <- read_csv_fn( "data/clean-data/CPUE3.csv", proj , na.strings = c(NA, "")) %>%
  mutate(year = factor(year))
str(eff3)

#### Load Structured Data ####
  ## Strata 1
strat1_Adult <- load_data(data = eff3[eff3$maturity == "A",], strata = 1)
strat1_Juvenile <- load_data(data = eff3[eff3$maturity == "J",], strata = 1)
  ## Strata 2
strat2_Adult <- load_data(data = eff3[eff3$maturity == "A",], strata = 2)
strat2_Juvenile <- load_data(data = eff3[eff3$maturity == "J",], strata = 2)
```


The plan here is to decide if year should be included as a random effect factor variable or at all.


I'll be using strat2 AdulT Male Sharpnose.
```{r}

dat <- strat2_Adult$Male$sharpnose
str(dat)

```



```{r}
par(mfrow = c(1,1))

plot(CPUE ~ year,
     data = eff3[eff3$CPUE>0,])

plot(((CPUE-mean(CPUE))/sd(CPUE)) ~ year,
     data = eff3[eff3$CPUE>0,])


plot(CPUE ~ year,
     data = dat)

plot(((CPUE-mean(CPUE))/sd(CPUE)) ~ year,
     data = dat)
```





```{r}
glob_gam <- gam(CPUE ~ s(startlon, startlat, k = 50) +
                  s(startdepth) +
                  s(tempbotm) + 
                  s(turbbotm) +
                  s(oxybotm) +
                  s(salbotm) + 
                  s(Dis.to.Shore) +
                  bottype4 + 
                  year,
                family = Gamma(link = log),
                data = dat)


glob_gam

par(mfrow = c(2,2))
gam.check(glob_gam)

```



```{r}
glob_gam_log <- gam(log(CPUE +1) ~ s(startlon, startlat, k = 50) +
                  s(startdepth) +
                  s(tempbotm) + 
                  s(turbbotm) +
                  s(oxybotm) +
                  s(salbotm) + 
                  s(Dis.to.Shore) +
                  bottype4 + 
                  year,
                family = Gamma(link = log),
                data = dat)


glob_gam_log

par(mfrow = c(2,2))
gam.check(glob_gam_log)
```

 so idk but I feel like log(CPUE) doesn't make a huge difference.
 
 
 **residuals**
 
```{r}
glob_resid <- resid(glob_gam)
par(mfrow = c(1,1))
hist(glob_resid)

plot(glob_resid~dat$year)
```
 
Doesn't look like there is much of a pattern in the residuals when Year is included as a factor variable.

Lets see what happens when **year is left out**


```{r}
red_gam <- gam(CPUE ~ s(startlon, startlat, k = 50) +
                  s(startdepth) +
                  s(tempbotm) + 
                  s(turbbotm) +
                  s(oxybotm) +
                  s(salbotm) + 
                  s(Dis.to.Shore) +
                  bottype4 ,
                family = Gamma(link = log),
                data = dat)


red_gam

par(mfrow = c(2,2))
gam.check(red_gam)

```

```{r}
red_resid <- resid(red_gam)
par(mfrow = c(1,1))
hist(red_resid)

plot(red_resid~dat$year)
```


Looks like there is a little more variability in the residuals for each year but there doesn't appear to be any difference between years.


**Year random effect**
```{r}
re_gam <- gam(CPUE ~ s(startlon, startlat, k = 50) +
                  s(startdepth) +
                  s(tempbotm) + 
                  s(turbbotm) +
                  s(oxybotm) +
                  s(salbotm) + 
                  s(Dis.to.Shore) +
                  bottype4 + 
                  s(year, bs = "re"),
                family = Gamma(link = log),
                data = dat)


re_gam

par(mfrow = c(2,2))
gam.check(re_gam)
```

```{r}
re_resid <- resid(re_gam)
par(mfrow = c(1,1))
hist(re_resid)

plot(re_resid~dat$year)
```


**Year as numeric smooth** just for good measure and because it makes 4 plots
```{r}

#### Load Combined Data ####
eff32 <- read_csv_fn( "data/clean-data/CPUE3.csv", proj , na.strings = c(NA, "")) 
str(eff32)

#### Load Structured Data ####
  ## Strata 1
strat1_Adult2 <- load_data(data = eff32[eff32$maturity == "A",], strata = 1)
strat1_Juvenile2 <- load_data(data = eff32[eff32$maturity == "J",], strata = 1)
  ## Strata 2
strat2_Adult2 <- load_data(data = eff32[eff32$maturity == "A",], strata = 2)
strat2_Juvenile2 <- load_data(data = eff32[eff32$maturity == "J",], strata = 2)

dat2 <- strat2_Adult2$Male$sharpnose
str(dat2)


yrsm_gam <- gam(CPUE ~ s(startlon, startlat, k = 50) +
                  s(startdepth) +
                  s(tempbotm) + 
                  s(turbbotm) +
                  s(oxybotm) +
                  s(salbotm) + 
                  s(Dis.to.Shore) +
                  bottype4 + 
                  s(year, k = 17),
                family = Gamma(link = log),
                data = dat2)


yrsm_gam

par(mfrow = c(2,2))
gam.check(yrsm_gam)
```

```{r}
yrsm_resid <- resid(yrsm_gam)
par(mfrow = c(1,1))
hist(yrsm_resid)

plot(yrsm_resid~dat$year)
```

```{r}
par(mfrow = c(2,2))

plot(glob_resid~dat$year, main = "year linear pred (factor)")

plot(re_resid~dat$year, main = "random effect Year")

plot(red_resid~dat$year, main = "no year")



plot(yrsm_resid~dat$year, main = "numeric year smooth")

```



Im not seeing a difference here between using year as a linear predictor or using year as a random effect. (Also these boxplots suggest there is no real difference in the residuals each year even when year is excluded although we do see a slight improvement with year included).

```{r}
AIC(glob_gam, re_gam, red_gam, yrsm_gam)

anova.gam(glob_gam, re_gam, red_gam, yrsm_gam, test = "F")
```

Including year as a random effect improves our AIC slightly over the the model with year as a linear predictor ( $\Delta AIC = $ `r AIC(glob_gam, re_gam, red_gam, yrsm_gam)[1,2] - AIC(glob_gam, re_gam, red_gam, yrsm_gam)[2,2]`). It seems clear to me from the AIC that it is better to have year included than excluded (or included as a numeric smooth). Also I already included year as a random effect so I don't really want to go back and refit(Hope you concur).

