---
title: "Blacktip Best GAM Models"
author: "Alex Benecke"
date: "August 31, 2018"
output:   
  html_document:
    df_print: paged
    toc: true
    toc_float: true
    toc_depth: 5
    fig_width: 10
    fig_height: 10
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Load Packages, include=FALSE, eval=TRUE}

### Load Packages
library(FSA)
library(tidyverse)
library(dplyr)
library(magrittr)
library(scales)
library(mgcv)
library(sciplot)
library(pipeR)

### Load My Functions
source("5_functions/dropbox_fn.R") # For interacting with dropbox
proj = "shark" # Specify project where data is stored 

source("5_functions/load_data.R")
```

```{r Load Data, echo=FALSE, include=FALSE, eval=FALSE}
#### Load Combined Data ####
eff3 <- read_csv_fn( "data/clean-data/CPUE3.csv", proj , na.strings = c(NA, ""))
str(eff3)

#### Load Structured Data ####
  ## Strata 1
strat1_Adult <- load_data(data = eff3[eff3$maturity == "A",], strata = 1)
strat1_Juvenile <- load_data(data = eff3[eff3$maturity == "J",], strata = 1)
  ## Strata 2
strat2_Adult <- load_data(data = eff3[eff3$maturity == "A",], strata = 2)
strat2_Juvenile <- load_data(data = eff3[eff3$maturity == "J",], strata = 2)
```


# Models Fit #

## Strata 1

| Species   | Female Adult | Female Juvenile | Male Adult | Male Juvenile |
|:---------:|:------------:|:---------------:|:----------:|:-------------:|
| Blacknose |  OK          |  OK             |  OK        |  OK           |
| Blacktip  |  OK          |  OK             |  OK        |  OK           |
| Bull      |  OK          |  OK             |  OK        |  OK           |
| Sandbar   |  OK          |  OK             |  OK        |  OK           |
| Sharpnose |  OK          |  OK             |  OK        |  OK           |
| Spinner   |  OK          |  OK             |  OK        |  OK           |
| Tiger     |  OK          |  OK             |  OK        |  OK           |

## Strata 2

| Species   | Female Adult | Female Juvenile | Male Adult | Male Juvenile |
|:---------:|:------------:|:---------------:|:----------:|:-------------:|
| Blacknose |  OK          |  OK             |  OK        |  OK           |
| Blacktip  |  OK          |  OK             |  OK        |  OK           |
| Bull      |  Failed      |  Failed         |  Failed    |  Failed       |
| Sandbar   |  OK          |  OK             |  Failed    |  OK           |
| Sharpnose |  OK          |  OK             |  OK        |  OK           |
| Spinner   |  Failed      |  OK             |  Failed    |  OK           |
| Tiger     |  Failed      |  OK             |  Failed    |  OK           |


The **Primary Species** I will Use are going to be **Blacknose**, **Blacktip**, and **Sharpnose** because they were fit for all levels of sex and maturity in both strata




# Blacktip #

## Strata 1 Occurrence

### **Female Adult** S1
```{r, eval=TRUE, include=FALSE}
load(file = "output/output_GAM/strat1/Female/Adult/bt_s1_FA.rda")
```

```{r}
bt_s1_FA$results
```

```{r, eval = TRUE}
( bt_s1_FA_best <-  bt_s1_FA$model_fits$LatLon_Temp_Turb_Oxy_Sal_Dis )


par(mfrow = c(2,2))
gam.check( bt_s1_FA_best)



summary( bt_s1_FA_best)


plot( bt_s1_FA_best, pages = 1)

#10-10-2018#save( bt_s1_FA_best, file = "output/output_GAM/best/blacktip/bt_s1_FA_best.rda" )
```


```{r}
rm( bt_s1_FA, bt_s1_FA_best)
```




### **Female Juvenile** S1
```{r, eval=TRUE, include=FALSE}
load(file = "output/output_GAM/strat1/Female/Juvenile/bt_s1_FJ.rda")
```

```{r}
bt_s1_FJ$results
```

```{r, eval = TRUE}
( bt_s1_FJ_best <-  bt_s1_FJ$model_fits$LatLon_Dep_Temp_Turb_Oxy_Dis )


par(mfrow = c(2,2))
gam.check( bt_s1_FJ_best)



summary( bt_s1_FJ_best)


plot( bt_s1_FJ_best, pages = 1)




#10-10-2018#save( bt_s1_FJ_best, file = "output/output_GAM/best/blacktip/bt_s1_FJ_best.rda" )
```

```{r}
rm( bt_s1_FJ, bt_s1_FJ_best)
```




### **Male Adult** S1

```{r, eval=TRUE, include=FALSE}
load(file = "output/output_GAM/strat1/Male/Adult/bt_s1_MA.rda")
```

```{r}
bt_s1_MA$results
```

```{r, eval = TRUE}
( bt_s1_MA_best <-  bt_s1_MA$model_fits$LatLon_Dep_Temp_Turb_Oxy_Dis_Bottype )


par(mfrow = c(2,2))
gam.check( bt_s1_MA_best)



summary( bt_s1_MA_best)


plot( bt_s1_MA_best, pages = 1)


#10-10-2018#save( bt_s1_MA_best, file = "output/output_GAM/best/blacktip/bt_s1_MA_best.rda" )
```

```{r}
rm( bt_s1_MA, bt_s1_MA_best)
```




### **Male Juvenile** S1

```{r, eval=TRUE, include=FALSE}
load(file = "output/output_GAM/strat1/Male/Juvenile/bt_s1_MJ.rda")
```

```{r}
bt_s1_MJ$results
```

```{r, eval = TRUE}
( bt_s1_MJ_best <-  bt_s1_MJ$model_fits$LatLon_Temp_Turb_Oxy_Sal_Bottype )


par(mfrow = c(2,2))
gam.check( bt_s1_MJ_best)



summary( bt_s1_MJ_best)


plot( bt_s1_MJ_best, pages = 1)


#10-10-2018#save( bt_s1_MJ_best, file = "output/output_GAM/best/blacktip/bt_s1_MJ_best.rda" )
```
All smooths are zero everywhere. However, **Lat-Lon** looks pretty interesting showing an area with very high probability of occurrence. 

```{r}
rm( bt_s1_MJ, bt_s1_MJ_best)
```

  
  
## Strata 2 Zero-Truncated Abundance

### **Female Adult** S2

```{r, eval=TRUE, include=FALSE}
load(file = "output/output_GAM/strat2/Female/Adult/bt_s2_FA.rda")
```

```{r}
bt_s2_FA$results
```

```{r, eval = TRUE}
( bt_s2_FA_best <-  bt_s2_FA$model_fits$LatLon_Oxy_Sal )


par(mfrow = c(2,2))
gam.check( bt_s2_FA_best)



summary( bt_s2_FA_best)


plot( bt_s2_FA_best, pages = 1)


#10-10-2018#save( bt_s2_FA_best, file = "output/output_GAM/best/blacktip/bt_s2_FA_best.rda" )
```

```{r}
rm( bt_s2_FA, bt_s2_FA_best)
```





### **Female Juvenile** S2

```{r, eval=TRUE, include=FALSE}
load(file = "output/output_GAM/strat2/Female/Juvenile/bt_s2_FJ.rda")
```


```{r}
bt_s2_FJ$results
```

```{r, eval = TRUE}
( bt_s2_FJ_best <-  bt_s2_FJ$model_fits$LatLon_Dep_Temp_Turb_Oxy_Sal )


par(mfrow = c(2,2))
gam.check( bt_s2_FJ_best)



summary( bt_s2_FJ_best)


plot( bt_s2_FJ_best, pages = 1)


#10-10-2018#save( bt_s2_FJ_best, file = "output/output_GAM/best/blacktip/bt_s2_FJ_best.rda" )
```


```{r}
rm( bt_s2_FJ, bt_s2_FJ_best )
```


### **Male Adult** S2

```{r, eval=TRUE, include=FALSE}
load(file = "output/output_GAM/strat2/Male/Adult/bt_s2_MA.rda")
```


```{r}
bt_s2_MA$results
```

```{r, eval = TRUE}
( bt_s2_MA_best <-  bt_s2_MA$model_fits$LatLon_Dep_Sal_Dis )


par(mfrow = c(2,2))
gam.check( bt_s2_MA_best)



summary( bt_s2_MA_best)


plot( bt_s2_MA_best, pages = 1)




#10-10-2018#save( bt_s2_MA_best, file = "output/output_GAM/best/blacktip/bt_s2_MA_best.rda" )
```


```{r}
rm( bt_s2_MA, bt_s2_MA_best )
```




### **Male Juvenile** S2

```{r, eval=TRUE, include=FALSE}
load(file = "output/output_GAM/strat2/Male/Juvenile/bt_s2_MJ.rda")
```


```{r}
bt_s2_MJ$results
```

```{r, eval = TRUE}
( bt_s2_MJ_best <-  bt_s2_MJ$model_fits$LatLon_Dep_Turb_Oxy_Sal )


par(mfrow = c(2,2))
gam.check( bt_s2_MJ_best)



summary( bt_s2_MJ_best)


plot( bt_s2_MJ_best, pages = 1)


#10-10-2018#save( bt_s2_MJ_best, file = "output/output_GAM/best/blacktip/bt_s2_MJ_best.rda" )
```

```{r}
rm( bt_s2_MJ, bt_s2_MJ_best)
```









