---
title: "Blacknose Best GAM Models"
author: "Alex Benecke"
date: "August 31, 2018"
output:    
  html_document:
    df_print: paged
    toc: true
    toc_float: true
    toc_depth: 5
    fig_width: 10
    fig_height: 10
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Load Packages, include=FALSE, eval=TRUE}

### Load Packages
library(FSA)
library(tidyverse)
library(dplyr)
library(magrittr)
library(scales)
library(mgcv)
library(sciplot)

### Load My Functions
source("5_functions/dropbox_fn.R") # For interacting with dropbox
proj = "shark" # Specify project where data is stored 

source("5_functions/load_data.R")
```

```{r Load Data, echo=FALSE, include=FALSE, eval=FALSE}
#### Load Combined Data ####
eff3 <- read_csv_fn( "data/clean-data/CPUE3.csv", proj , na.strings = c(NA, ""))
str(eff3)

#### Load Structured Data ####
  ## Strata 1
strat1_Adult <- load_data(data = eff3[eff3$maturity == "A",], strata = 1)
strat1_Juvenile <- load_data(data = eff3[eff3$maturity == "J",], strata = 1)
  ## Strata 2
strat2_Adult <- load_data(data = eff3[eff3$maturity == "A",], strata = 2)
strat2_Juvenile <- load_data(data = eff3[eff3$maturity == "J",], strata = 2)
```

# Models Fit #

## Strata 1

| Species   | Female Adult | Female Juvenile | Male Adult | Male Juvenile |
|:---------:|:------------:|:---------------:|:----------:|:-------------:|
| Blacknose |  OK          |  OK             |  OK        |  OK           |
| Blacktip  |  OK          |  OK             |  OK        |  OK           |
| Bull      |  OK          |  OK             |  OK        |  OK           |
| Sandbar   |  OK          |  OK             |  OK        |  OK           |
| Sharpnose |  OK          |  OK             |  OK        |  OK           |
| Spinner   |  OK          |  OK             |  OK        |  OK           |
| Tiger     |  OK          |  OK             |  OK        |  OK           |

## Strata 2

| Species   | Female Adult | Female Juvenile | Male Adult | Male Juvenile |
|:---------:|:------------:|:---------------:|:----------:|:-------------:|
| Blacknose |  OK          |  OK             |  OK        |  OK           |
| Blacktip  |  OK          |  OK             |  OK        |  OK           |
| Bull      |  Failed      |  Failed         |  Failed    |  Failed       |
| Sandbar   |  OK          |  OK             |  Failed    |  OK           |
| Sharpnose |  OK          |  OK             |  OK        |  OK           |
| Spinner   |  Failed      |  OK             |  Failed    |  OK           |
| Tiger     |  Failed      |  OK             |  Failed    |  OK           |


The **Primary Species** I will Use are going to be **Blacknose**, **Blacktip**, and **Sharpnose** because they were fit for all levels of sex and maturity in both strata






# Blacknose #

## Strata 1 Occurrence

### **Female Adult** S1
```{r, eval=TRUE, include=FALSE}
load(file = "output/output_GAM/strat1/Female/Adult/bn_s1_FA.rda")
```

```{r}
bn_s1_FA$results
```


```{r}
(bn_s1_FA_best <- bn_s1_FA$model_fits$LatLon_Dep_Temp_Oxy_Sal_Dis)


par(mfrow = c(2,2))
gam.check( bn_s1_FA_best)



summary( bn_s1_FA_best)


plot( bn_s1_FA_best, pages = 1)

#10-10-2018#save( bn_s1_FA_best, file = "output/output_GAM/best/blacknose/bn_s1_FA_best.rda" )
```

**Turbbotm** and **Salbotm** edf = 1.

```{r}
rm( bn_s1_FA, bn_s1_FA_best)
```


### **Female Juvenile** S1
```{r, eval=TRUE, include=FALSE}
load(file = "output/output_GAM/strat1/Female/Juvenile/bn_s1_FJ.rda")
```

```{r}
bn_s1_FJ$results
```



```{r, eval = TRUE}
(bn_s1_FJ_best <- bn_s1_FJ$model_fits$LatLon_Dep_Temp_Dis )


par(mfrow = c(2,2))
gam.check( bn_s1_FJ_best)

summary( bn_s1_FJ_best)

plot( bn_s1_FJ_best, pages = 1)


#10-10-2018#save( bn_s1_FJ_best, file = "output/output_GAM/best/blacknose/bn_s1_FJ_best.rda" )
```

```{r}
rm( bn_s1_FJ, bn_s1_FJ_best)
```



### **Male Adult** S1
```{r, eval=TRUE, include=FALSE}
load(file = "output/output_GAM/strat1/Male/Adult/bn_s1_MA.rda")
```

```{r}
bn_s1_MA$results
```

```{r, eval = TRUE}
(bn_s1_MA_best <- bn_s1_MA$model_fits$LatLon_Dep_Temp_Turb_Oxy_Sal_Dis )


par(mfrow = c(2,2))
gam.check( bn_s1_MA_best)



summary( bn_s1_MA_best)


plot( bn_s1_MA_best, pages = 1)


#10-10-2018#save( bn_s1_MA_best, file = "output/output_GAM/best/blacknose/bn_s1_MA_best.rda" )
```

```{r}
rm( bn_s1_MA, bn_s1_MA_best)
```



### **Male Juvenile** S1

```{r, eval=TRUE, include=FALSE}
load(file = "output/output_GAM/strat1/Male/Juvenile/bn_s1_MJ.rda")
```

```{r}
bn_s1_MJ$results
```

```{r, eval = TRUE}
(bn_s1_MJ_best <- bn_s1_MJ$model_fits$LatLon_Dep_Temp_Oxy_Dis )


par(mfrow = c(2,2))
gam.check( bn_s1_MJ_best)



summary( bn_s1_MJ_best)


plot( bn_s1_MJ_best, pages = 1)


#10-10-2018#save( bn_s1_MJ_best, file = "output/output_GAM/best/blacknose/bn_s1_MJ_best.rda" )
```

```{r}
rm( bn_s1_MJ, bn_s1_MJ_best)
```


## Strata 2 Zero-Truncated Abundance

### **Female Adult** S2

```{r, eval=TRUE, include=FALSE}
load(file = "output/output_GAM/strat2/Female/Adult/bn_s2_FA.rda")
```

```{r}
bn_s2_FA$results
```

```{r, eval = TRUE}
( bn_s2_FA_best <-  bn_s2_FA$model_fits$LatLon_Temp_Oxy_Bottype )


par(mfrow = c(2,2))
gam.check( bn_s2_FA_best)



summary( bn_s2_FA_best)


plot( bn_s2_FA_best, pages = 1)


#10-10-2018#save( bn_s2_FA_best, file = "output/output_GAM/best/blacknose/bn_s2_FA_best.rda" )
```


```{r}
rm( bn_s2_FA, bn_s2_FA_best)
```


### **Female Juvenile** S2

```{r, eval=TRUE, include=FALSE}
load(file = "output/output_GAM/strat2/Female/Juvenile/bn_s2_FJ.rda")
```

```{r}
bn_s2_FJ$results
```


```{r, eval = FALSE}
( bn_s2_FJ_best <-  bn_s2_FJ$model_fits$LatLon_Temp_Sal_Dis )


par(mfrow = c(2,2))
gam.check( bn_s2_FJ_best)



summary( bn_s2_FJ_best)


plot( bn_s2_FJ_best, pages = 1)

par(mfrow = c(1,1))
plot(bn_s2_FJ_best,
     select = 4)
abline(h = 0,
       col = "red",
       lty = 3)


#10-10-2018#save( bn_s2_FJ_best, file = "output/output_GAM/best/blacknose/bn_s2_FJ_best.rda" )
```
*Temp*, *Turb*, *Sal*, *Dis* edf = 1. All smooths are zero everywhere.


```{r}
rm( bn_s2_FJ, bn_s2_FJ_best)
```



### **Male Adult** S2

```{r, eval=TRUE, include=FALSE}
load(file = "output/output_GAM/strat2/Male/Adult/bn_s2_MA.rda")
```

```{r}
bn_s2_MA$results
```


```{r, eval = FALSE}
( bn_s2_MA_best <-  bn_s2_MA$model_fits$LatLon_Dep_Oxy_Sal_Dis_Bottype )


par(mfrow = c(2,2))
gam.check( bn_s2_MA_best)



summary( bn_s2_MA_best)


plot( bn_s2_MA_best, pages = 1)


#10-10-2018#save( bn_s2_MA_best, file = "output/output_GAM/best/blacknose/bn_s2_MA_best.rda" )
```

```{r}
rm( bn_s2_MA, bn_s2_MA_best)
```




### **Male Juvenile** S2

```{r, eval=TRUE, include=FALSE}
load(file = "output/output_GAM/strat2/Male/Juvenile/bn_s2_MJ.rda")
```

```{r}
bn_s2_MJ$results
```

```{r, eval = FALSE}
( bn_s2_MJ_best <-  bn_s2_MJ$model_fits$LatLon_Turb_Oxy_Sal )


par(mfrow = c(2,2))
gam.check( bn_s2_MJ_best)



summary( bn_s2_MJ_best)


plot( bn_s2_MJ_best, pages = 1)

par(mfrow = c(1,1))
plot(bn_s2_MJ_best,
     select = 3)
abline(h = 0,
       col = "red",
       lty = 3)

#10-10-2018#save( bn_s2_MJ_best, file = "output/output_GAM/best/blacknose/bn_s2_MJ_best.rda" )
```
*Year* edf is essentially Zero. All smooths but *Turbbotm* are zero everywhere.


```{r}
rm( bn_s2_MJ, bn_s2_MJ_best)
```

























