---
title: "Sharpnose Best GAM Models"
author: "Alex Benecke"
date: "August 31, 2018"
output:   
  html_document:
    df_print: paged
    toc: true
    toc_float: true
    toc_depth: 5
    fig_width: 10
    fig_height: 10
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Load Packages, include=FALSE, eval=TRUE}

### Load Packages
library(FSA)
library(tidyverse)
library(dplyr)
library(magrittr)
library(scales)
library(mgcv)
library(sciplot)
library(pipeR)

### Load My Functions
source("5_functions/dropbox_fn.R") # For interacting with dropbox
proj = "shark" # Specify project where data is stored 

source("5_functions/load_data.R")
```

```{r Load Data, echo=FALSE, include=FALSE, eval=TRUE}
#### Load Combined Data ####

eff3 <- read_csv_fn( "data/clean-data/CPUE3.csv", proj, na.strings = c(NA,"")) %>%
  subset(common == "Sharpnose") %>%
  droplevels() %>%
  na.omit()

Adult_S1 <- load_data(data = eff3[eff3$maturity == "A",] %>% droplevels(), strata = 1)

Adult_Female_S1 <- Adult_S1$Female$sharpnose
Adult_Male_S1 <- Adult_S1$Male$sharpnose


Juvenile_S1 <- load_data(data = eff3[eff3$maturity == "J",] %>% droplevels(), strata = 1)

Juvenile_Female_S1 <- Juvenile_S1$Female$sharpnose
Juvenile_Male_S1 <- Juvenile_S1$Male$sharpnose



Adult_S2 <- load_data(data = eff3[eff3$maturity == "A",] %>% droplevels(), strata = 2)

Adult_Female_S2 <- Adult_S2$Female$sharpnose
Adult_Male_S2 <- Adult_S2$Male$sharpnose


Juvenile_S2 <- load_data(data = eff3[eff3$maturity == "J",] %>% droplevels(), strata = 2)

Juvenile_Female_S2 <- Juvenile_S2$Female
Juvenile_Male_S2 <- Juvenile_S2$Male
```


# Models Fit #

## Strata 1

| Species   | Female Adult | Female Juvenile | Male Adult | Male Juvenile |
|:---------:|:------------:|:---------------:|:----------:|:-------------:|
| Blacknose |  OK          |  OK             |  OK        |  OK           |
| Blacktip  |  OK          |  OK             |  OK        |  OK           |
| Bull      |  OK          |  OK             |  OK        |  OK           |
| Sandbar   |  OK          |  OK             |  OK        |  OK           |
| Sharpnose |  OK          |  OK             |  OK        |  OK           |
| Spinner   |  OK          |  OK             |  OK        |  OK           |
| Tiger     |  OK          |  OK             |  OK        |  OK           |

## Strata 2

| Species   | Female Adult | Female Juvenile | Male Adult | Male Juvenile |
|:---------:|:------------:|:---------------:|:----------:|:-------------:|
| Blacknose |  OK          |  OK             |  OK        |  OK           |
| Blacktip  |  OK          |  OK             |  OK        |  OK           |
| Bull      |  Failed      |  Failed         |  Failed    |  Failed       |
| Sandbar   |  OK          |  OK             |  Failed    |  OK           |
| Sharpnose |  OK          |  OK             |  OK        |  OK           |
| Spinner   |  Failed      |  OK             |  Failed    |  OK           |
| Tiger     |  Failed      |  OK             |  Failed    |  OK           |


The **Primary Species** I will Use are going to be **Blacknose**, **Blacktip**, and **Sharpnose** because they were fit for all levels of sex and maturity in both strata


# Sharpnose #

## Strata 1 Occurrence

### **Female Adult** S1
```{r, eval=TRUE, include=FALSE}
load(file = "output/output_GAM/strat1/Female/Adult/sn_s1_FA.rda")
```

```{r}
sn_s1_FA$results
```

```{r, eval = TRUE}
( sn_s1_FA_best <-  sn_s1_FA$model_fits$LatLon_DepTemp_Turb_Oxy )


par(mfrow = c(2,2))
gam.check( sn_s1_FA_best)



summary( sn_s1_FA_best)


plot( sn_s1_FA_best, 
      scale = 0,
      all.terms = TRUE,
      pages = 1)


#11-19-18#save( sn_s1_FA_best, file = "output/output_GAM/best/sharpnose/sn_s1_FA_best.rda" )
```

```{r}
rm( sn_s1_FA, sn_s1_FA_best)
```




### **Female Juvenile** S1
```{r, eval=TRUE, include=FALSE}
load(file = "output/output_GAM/strat1/Female/Juvenile/sn_s1_FJ.rda")
```

```{r}
sn_s1_FJ$results
```

```{r, eval = TRUE}
( sn_s1_FJ_best <-  sn_s1_FJ$model_fits$LatLon_DepTemp_Bottype )


par(mfrow = c(2,2))
gam.check( sn_s1_FJ_best)



summary( sn_s1_FJ_best)


plot( sn_s1_FJ_best, pages = 1)


#11-19-18#save( sn_s1_FJ_best, file = "output/output_GAM/best/sharpnose/sn_s1_FJ_best.rda" )
```

```{r}
rm( sn_s1_FJ,sn_s1_FJ_best)
```




### **Male Adult** S1
```{r, eval=TRUE, include=FALSE}
load(file = "output/output_GAM/strat1/Male/Adult/sn_s1_MA.rda")
```

```{r}
sn_s1_MA$results
```

```{r}
( sn_s1_MA_1 <-  sn_s1_MA$model_fits$LatLon_DepTemp_Turb_Oxy_Sal )


par(mfrow = c(2,2))
gam.check( sn_s1_MA_1)



summary( sn_s1_MA_1)


plot( sn_s1_MA_1, pages = 1)
```

Try fitting with oxybotm as linear pred
```{r}
  require(mgcv)
  require(magrittr)
  require(plyr)
  require(dplyr)


### Initialize Values

    k_i <- rbind( add_k = c(1, 1, 1, 1) ,
                       k_0 = c(5, 5, 5, 5) ,
                       k_prime = c(0, 0, 0, 0),  
                       edf_vec = c(0, 0, 0, 0),  
                       diff_df = c(0, 0, 0, 0) ) 

col_names <- c("LatLon", "DepTemp", "Turb", "Sal")

colnames(k_i) <- c("LatLon", "DepTemp", "Turb", "Sal")

old_gcv <- 1000000
new_gcv <- numeric(1)  
  
### Fit GAM
while( any( k_i[ 'add_k', ] == 1) & new_gcv <= old_gcv  ){
        
        old_gcv <- new_gcv
        
        sn_s1_MA_1.1 <- gam(pres ~ s(startlon, startlat, k = k_i['k_0', 'LatLon'] + 45) +
                                         te(startdepth, tempbotm, k = k_i['k_0', 'DepTemp']) + 
                                         s(turbbotm, k = k_i['k_0', 'Turb']) +
                                         oxybotm + 
                                         s(salbotm, k = k_i['k_0', 'Sal'])
                                       ,
                                       data = Adult_Male_S1
                                       ,
                                       family = binomial(link = logit) #Gamma(link = log)
                                       ,
                                       method = "REML") %>>%
          (~tmp)
        
        new_gcv <- tmp$gcv.ubre
        
        tmp %>>%
          summary() %>>%
          (~tmp2)
        
        k_i['edf_vec', ] <- tmp2$edf[1:ncol(k_i)]
        
        
        for(j in col_names ){
          
          k_i['k_prime', j] = k_i['k_0', j] - 1
          
          if( j == 'LatLon') {
            
            k_i['diff_df', j] <- k_i['k_prime', j] - k_i['edf_vec', j] -8
            
            ifelse( (k_i['diff_df', j] <= 10) == TRUE & (new_gcv <= old_gcv) == TRUE,
                    k_i['add_k', j] <- 1,
                    k_i['add_k', j] <- 0)
            ifelse( ( k_i['diff_df', j] <= 10) == TRUE & (new_gcv <= old_gcv) == TRUE,
                    k_i['k_0', j] <- k_i['k_0', j] + 5,
                    k_i['add_k', j] <- 0)
            
          } else{
            
            k_i['diff_df', j] <- k_i['k_prime', j] - k_i['edf_vec', j] 
            
            ifelse( (k_i['diff_df', j] <= 2) == TRUE & (new_gcv <= old_gcv) == TRUE,
                    k_i['add_k', j] <- 1,
                    k_i['add_k', j] <- 0)
            ifelse( (k_i['diff_df', j] <= 2) == TRUE & (new_gcv <= old_gcv) == TRUE,
                    k_i['k_0', j] <- k_i['k_0', j] + 1,
                    k_i['add_k', j] <- 0)
          }
        }
      }





par(mfrow = c(2,2))
gam.check( sn_s1_MA_1.1)



summary( sn_s1_MA_1.1)


plot( sn_s1_MA_1.1, pages = 1)


AIC(sn_s1_MA_1, sn_s1_MA_1.1)
```
**oxybotm** is not a significant linear predictor, however, AIC is significantly improved.



```{r, eval = TRUE}
( sn_s1_MA_best <-  sn_s1_MA_1.1 )


par(mfrow = c(2,2))
gam.check( sn_s1_MA_best)



summary( sn_s1_MA_best)


plot( sn_s1_MA_best, pages = 1)


#11-19-18#save( sn_s1_MA_best, file = "output/output_GAM/best/sharpnose/sn_s1_MA_best.rda" )
```

```{r}
rm( sn_s1_MA,sn_s1_MA_best)
```




### **Male Juvenile** S1
```{r, eval=TRUE, include=FALSE}
load(file = "output/output_GAM/strat1/Male/Juvenile/sn_s1_MJ.rda")
```

```{r}
sn_s1_MJ$results
```

```{r}
( sn_s1_MJ_1 <-  sn_s1_MJ$model_fits$LatLon_DepTemp_Oxy_Sal )


par(mfrow = c(2,2))
gam.check( sn_s1_MJ_1)



summary( sn_s1_MJ_1)


plot( sn_s1_MJ_1, pages = 1)
```

Try Salbotm as linear predictor

```{r}
require(mgcv)
require(magrittr)
require(plyr)
require(dplyr)


### Initialize Values

k_i <- rbind( add_k = c(1, 1, 1) ,
              k_0 = c(5, 5, 5) ,
              k_prime = c(0, 0, 0),  
              edf_vec = c(0, 0, 0),  
              diff_df = c(0, 0, 0) ) 

col_names <- c("LatLon", "DepTemp", "Oxy")
  
  colnames(k_i) <-  c("LatLon", "DepTemp", "Oxy")
  
  old_gcv <- 1000000
new_gcv <- numeric(1)  

### Fit GAM
while( any( k_i[ 'add_k', ] == 1) & new_gcv <= old_gcv  ){
  
  old_gcv <- new_gcv
  
  sn_s1_MJ_1.1 <- gam(pres ~ s(startlon, startlat, k = k_i['k_0', 'LatLon'] + 45) +
                 te(startdepth, tempbotm, k = k_i['k_0', 'DepTemp']) +
                 s(oxybotm, k = k_i['k_0', 'Oxy']) + 
                 salbotm 
               ,
               data = Juvenile_Male_S1
                 ,
               family = binomial(link = logit) #Gamma(link = log)
               ,
               method = "REML") %>>%
    (~tmp)
  
  new_gcv <- tmp$gcv.ubre
  
  tmp %>>%
    summary() %>>%
    (~tmp2)
  
  k_i['edf_vec', ] <- tmp2$edf[1:ncol(k_i)]
  
  
  for(j in col_names ){
    
    k_i['k_prime', j] = k_i['k_0', j] - 1
    
    if( j == 'LatLon') {
      
      k_i['diff_df', j] <- k_i['k_prime', j] - k_i['edf_vec', j] -8
      
      ifelse( (k_i['diff_df', j] <= 10) == TRUE & (new_gcv <= old_gcv) == TRUE,
              k_i['add_k', j] <- 1,
              k_i['add_k', j] <- 0)
      ifelse( ( k_i['diff_df', j] <= 10) == TRUE & (new_gcv <= old_gcv) == TRUE,
              k_i['k_0', j] <- k_i['k_0', j] + 5,
              k_i['add_k', j] <- 0)
      
    } else{
      
      k_i['diff_df', j] <- k_i['k_prime', j] - k_i['edf_vec', j] 
      
      ifelse( (k_i['diff_df', j] <= 2) == TRUE & (new_gcv <= old_gcv) == TRUE,
              k_i['add_k', j] <- 1,
              k_i['add_k', j] <- 0)
      ifelse( (k_i['diff_df', j] <= 2) == TRUE & (new_gcv <= old_gcv) == TRUE,
              k_i['k_0', j] <- k_i['k_0', j] + 1,
              k_i['add_k', j] <- 0)
    }
  }
}


par(mfrow = c(2,2))
gam.check( sn_s1_MJ_1.1)



summary( sn_s1_MJ_1.1)


plot( sn_s1_MJ_1.1, pages = 1)

AIC(sn_s1_MJ_1, sn_s1_MJ_1.1)
BIC(sn_s1_MJ_1, sn_s1_MJ_1.1)

```
**salbotm** not a significant linear pred, however, AIC is significantly better with it.

```{r, eval = TRUE}
( sn_s1_MJ_best <-  sn_s1_MJ_1.1 )


par(mfrow = c(2,2))
gam.check( sn_s1_MJ_best)



summary( sn_s1_MJ_best)


plot( sn_s1_MJ_best, pages = 1)


#11-19-18#save( sn_s1_MJ_best, file = "output/output_GAM/best/sharpnose/sn_s1_MJ_best.rda" )
```

```{r}
rm( sn_s1_MJ, sn_s1_MJ_best)
```



  
  
  
## Strata 2 Zero-Truncated Abundance

### **Female Adult** S2
```{r, eval=TRUE, include=FALSE}
load(file = "output/output_GAM/strat2/Female/Adult/sn_s2_FA.rda")
```

```{r}
sn_s2_FA$results
```


```{r, eval = TRUE}
( sn_s2_FA_best <-  sn_s2_FA$model_fits$LatLon_DepTemp_Turb )


par(mfrow = c(2,2))
gam.check( sn_s2_FA_best)



summary( sn_s2_FA_best)


plot( sn_s2_FA_best, pages = 1)


#11-19-18#save( sn_s2_FA_best, file = "output/output_GAM/best/sharpnose/sn_s2_FA_best.rda" )
```

```{r}
rm( sn_s2_FA, sn_s2_FA_best)
```





### **Female Juvenile** S2
```{r, eval=TRUE, include=FALSE}
load(file = "output/output_GAM/strat2/Female/Juvenile/sn_s2_FJ.rda")
```


```{r}
sn_s2_FJ$results
```

```{r, eval = TRUE}
( sn_s2_FJ_best <-  sn_s2_FJ$model_fits$LatLon_DepTemp_Turb_Bottype )


par(mfrow = c(2,2))
gam.check( sn_s2_FJ_best)



summary( sn_s2_FJ_best)


plot( sn_s2_FJ_best, pages = 1)


#11-19-18#save( sn_s2_FJ_best, file = "output/output_GAM/best/sharpnose/sn_s2_FJ_best.rda" )
```

```{r}
rm( sn_s2_FJ, sn_s2_FJ_best)
```




### **Male Adult** S2
```{r, eval=TRUE, include=FALSE}
load(file = "output/output_GAM/strat2/Male/Adult/sn_s2_MA.rda")
```


```{r}
sn_s2_MA$results
```


```{r, eval = TRUE}
( sn_s2_MA_best <-  sn_s2_MA$model_fits$LatLon_DepTemp_Turb_Sal_Bottype )


par(mfrow = c(2,2))
gam.check( sn_s2_MA_best)



summary( sn_s2_MA_best)


plot( sn_s2_MA_best, pages = 1)


#11-19-18#save( sn_s2_MA_best, file = "output/output_GAM/best/sharpnose/sn_s2_MA_best.rda" )
```

```{r}
rm( sn_s2_MA, sn_s2_MA_best)
```




### **Male Juvenile** S2
```{r, eval=TRUE, include=FALSE}
load(file = "output/output_GAM/strat2/Male/Juvenile/sn_s2_MJ.rda")
```


```{r}
sn_s2_MJ$results
```


```{r, eval = TRUE}
( sn_s2_MJ_best <-  sn_s2_MJ$model_fits$LatLon_Oxy )


par(mfrow = c(2,2))
gam.check( sn_s2_MJ_best)



summary( sn_s2_MJ_best)


plot( sn_s2_MJ_best, pages = 1)


#11-19-18#save( sn_s2_MJ_best, file = "output/output_GAM/best/sharpnose/sn_s2_MJ_best.rda" )
```

```{r}
rm( sn_s2_MJ, sn_s2_MJ_best)
```




