---
title: "Best GAM"
author: "Alex Benecke"
date: "July 30, 2018"
output:   
  html_document:
    df_print: paged
    toc: true
    toc_float: true
    toc_depth: 5
    fig_width: 10
    fig_height: 10
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE)
```

```{r Load Packages, include=FALSE, eval=TRUE}

### Load Packages
library(FSA)
library(tidyverse)
library(dplyr)
library(magrittr)
library(scales)
library(mgcv)
library(sciplot)

### Load My Functions
source("5_functions/dropbox_fn.R") # For interacting with dropbox
proj = "shark" # Specify project where data is stored 

source("5_functions/load_data.R")
```

```{r Load Data, echo=FALSE, include=FALSE, eval=FALSE}
#### Load Combined Data ####
eff3 <- read_csv_fn( "data/clean-data/CPUE3.csv", proj , na.strings = c(NA, ""))
str(eff3)

#### Load Structured Data ####
  ## Strata 1
strat1_Adult <- load_data(data = eff3[eff3$maturity == "A",], strata = 1)
strat1_Juvenile <- load_data(data = eff3[eff3$maturity == "J",], strata = 1)
  ## Strata 2
strat2_Adult <- load_data(data = eff3[eff3$maturity == "A",], strata = 2)
strat2_Juvenile <- load_data(data = eff3[eff3$maturity == "J",], strata = 2)
```


# Models Fit #

## Strata 1

| Species   | Female Adult | Female Juvenile | Male Adult | Male Juvenile |
|:---------:|:------------:|:---------------:|:----------:|:-------------:|
| Blacknose |  OK          |  OK             |  OK        |  OK           |
| Blacktip  |  OK          |  OK             |  OK        |  OK           |
| Bull      |  OK          |  OK             |  OK        |  OK           |
| Sandbar   |  OK          |  OK             |  OK        |  OK           |
| Sharpnose |  OK          |  OK             |  OK        |  OK           |
| Spinner   |  OK          |  OK             |  OK        |  OK           |
| Tiger     |  OK          |  OK             |  OK        |  OK           |

## Strata 2

| Species   | Female Adult | Female Juvenile | Male Adult | Male Juvenile |
|:---------:|:------------:|:---------------:|:----------:|:-------------:|
| Blacknose |  OK          |  OK             |  OK        |  OK           |
| Blacktip  |  OK          |  OK             |  OK        |  OK           |
| Bull      |  Failed      |  Failed         |  Failed    |  Failed       |
| Sandbar   |  OK          |  OK             |  Failed    |  OK           |
| Sharpnose |  OK          |  OK             |  OK        |  OK           |
| Spinner   |  Failed      |  OK             |  Failed    |  OK           |
| Tiger     |  Failed      |  OK             |  Failed    |  OK           |


The **Primary Species** I will Use are going to be **Blacknose**, **Blacktip**, and **Sharpnose** because they were fit for all levels of sex and maturity in both strata



# Blacknose #

## Strata 1 Occurrence

### **Female Adult** S1
```{r, eval=FALSE, include=FALSE}
load(file = "output/output_GAM/strat1/Female/Adult/")
```



### **Female Juvenile** S1
```{r, eval=FALSE, include=FALSE}
load(file = "output/output_GAM/strat1/Female/Juvenile/")
```


### **Male Adult** S1
```{r, eval=FALSE, include=FALSE}
load(file = "output/output_GAM/strat1/Male/Adult/")
```


### **Male Juvenile** S1
```{r, eval=FALSE, include=FALSE}
load(file = "output/output_GAM/strat1/Male/Juvenile/")
```

## Strata 2 Zero-Truncated Abundance

### **Female Adult** S2
```{r, eval=FALSE, include=FALSE}
load(file = "output/output_GAM/strat2/Female/Adult/")
```


### **Female Juvenile** S2
```{r, eval=FALSE, include=FALSE}
load(file = "output/output_GAM/strat2/Female/Juvenile/")
```


### **Male Adult** S2
```{r, eval=FALSE, include=FALSE}
load(file = "output/output_GAM/strat2/Male/Adult/")
```


### **Male Juvenile** S2
```{r, eval=FALSE, include=FALSE}
load(file = "output/output_GAM/strat2/Male/Juvenile")
```






# Blacktip #

## Strata 1 Occurrence

### **Female Adult** S1
```{r, eval=FALSE, include=FALSE}
load(file = "output/output_GAM/strat1/Female/Adult/")
```



### **Female Juvenile** S1
```{r, eval=FALSE, include=FALSE}
load(file = "output/output_GAM/strat1/Female/Juvenile/")
```


### **Male Adult** S1
```{r, eval=FALSE, include=FALSE}
load(file = "output/output_GAM/strat1/Male/Adult/")
```


### **Male Juvenile** S1
```{r, eval=FALSE, include=FALSE}
load(file = "output/output_GAM/strat1/Male/Juvenile/")
```

## Strata 2 Zero-Truncated Abundance

### **Female Adult** S2
```{r, eval=FALSE, include=FALSE}
load(file = "output/output_GAM/strat2/Female/Adult/")
```


### **Female Juvenile** S2
```{r, eval=FALSE, include=FALSE}
load(file = "output/output_GAM/strat2/Female/Juvenile/")
```


### **Male Adult** S2
```{r, eval=FALSE, include=FALSE}
load(file = "output/output_GAM/strat2/Male/Adult/")
```


### **Male Juvenile** S2
```{r, eval=FALSE, include=FALSE}
load(file = "output/output_GAM/strat2/Male/Juvenile")
```




# Sharpnose #

## Strata 1 Occurrence

### **Female Adult** S1
```{r, include=FALSE}
load(file = "output/output_GAM/strat1/Female/Adult/sn_s1_FA.rda")
```

```{r}
sn_s1_FA$results
```

 All three are the same the only difference is the combination of depth and temp. and Dis for the temp model
 
 [row 1] **Lat-Lon_Root-Dep_Temp_Turb_Oxy_Sal_Dis**
 `r sn_s1_FA$results[1, c(3:7)]`
 
 
 [row 20] **Dep not temp >> Lat-Lon_Root-Dep_Turb_Oxy_Sal_Dis**
 `r sn_s1_FA$results[20, c(3:7)]`
 
 [row 64] **Temp not dep >> Lat-Lon_Temp_Turb_Oxy_Sal**
 `r sn_s1_FA$results[64, c(3:7)]`

#### Top Model

```{r sn top model row 1}
(sn_s1_1 <- sn_s1_FA$model_fits$'Lat-Lon_Root-Dep_Temp_Turb_Oxy_Sal_Dis')

summary(sn_s1_1)

par(mfrow = c(2,2))
gam.check(sn_s1_1)



plot(sn_s1_1, pages = 1)

par(mfrow = c(1,1))

plot(sn_s1_1, select = 2)
abline(h = 0, lty = 3, col = "red")

plot(sn_s1_1, select = 3)
abline(h = 0, lty = 3, col = "red")

plot(sn_s1_1, select = 4)
abline(h = 0, lty = 3, col = "red")

plot(sn_s1_1, select = 5)
abline(h = 0, lty = 3, col = "red")

plot(sn_s1_1, select = 6)
abline(h = 0, lty = 3, col = "red")

plot(sn_s1_1, select = 7)
abline(h = 0, lty = 3, col = "red")


```

#### Depth Model

```{r sn top dep only model row 20}
(sn_s1_dep <- sn_s1_FA$model_fits$'Lat-Lon_Root-Dep_Turb_Oxy_Sal_Dis')

summary(sn_s1_dep)


par(mfrow = c(2,2))
gam.check(sn_s1_dep)


plot(sn_s1_dep, pages = 1)

par(mfrow = c(1,1))

plot(sn_s1_dep, select = 2)
abline(h = 0, lty = 3, col = "red")

plot(sn_s1_dep, select = 3)
abline(h = 0, lty = 3, col = "red")

plot(sn_s1_dep, select = 4)
abline(h = 0, lty = 3, col = "red")

plot(sn_s1_dep, select = 5)
abline(h = 0, lty = 3, col = "red")

plot(sn_s1_dep, select = 6)
abline(h = 0, lty = 3, col = "red")

plot(sn_s1_dep, select = 7)
abline(h = 0, lty = 3, col = "red")
```

#### Temp Model

```{r sn top temp only model row 64}
(sn_s1_temp <- sn_s1_FA$model_fits$'Lat-Lon_Temp_Turb_Oxy_Sal')

summary(sn_s1_temp)


par(mfrow = c(2,2))
gam.check(sn_s1_temp)


plot(sn_s1_temp, pages = 1)

par(mfrow = c(1,1))

plot(sn_s1_temp, select = 2)
abline(h = 0, lty = 3, col = "red")

plot(sn_s1_temp, select = 3)
abline(h = 0, lty = 3, col = "red")

plot(sn_s1_temp, select = 4)
abline(h = 0, lty = 3, col = "red")

plot(sn_s1_temp, select = 5)
abline(h = 0, lty = 3, col = "red")

```

#### Top Model without Root-Depth

```{r}
(sn_s1_1B <- sn_s1_FA$model_fits$'Lat-Lon_Temp_Turb_Oxy_Sal_Dis')


summary(sn_s1_1B)


par(mfrow = c(2,2))
gam.check(sn_s1_1B)


plot(sn_s1_1B, pages = 1)

par(mfrow = c(1,1))

plot(sn_s1_1B, select = 2)
abline(h = 0, lty = 3, col = "red")

plot(sn_s1_1B, select = 3)
abline(h = 0, lty = 3, col = "red")

plot(sn_s1_1B, select = 4)
abline(h = 0, lty = 3, col = "red")

plot(sn_s1_1B, select = 5)
abline(h = 0, lty = 3, col = "red")

plot(sn_s1_1B, select = 6)
abline(h = 0, lty = 3, col = "red")
```

#### Selecting best model sn_s1_FA

```{r sn s1 FA Compare models}
summary(sn_s1_1) ## 50%
summary(sn_s1_dep) ## 47.2%
summary(sn_s1_temp) ## 45.6$
summary(sn_s1_1B) ## 45.6%

anova.gam(sn_s1_1, sn_s1_dep, sn_s1_temp, sn_s1_1B, test = "Chisq")

AIC(sn_s1_1, sn_s1_dep, sn_s1_temp, sn_s1_1B)

```


  The results all say that the *row 1* model (*Lat-Lon_Root-Dep_Temp_Turb_Oxy_Sal_Dis*) is the best followed by that the model with just *Root-Depth* (*Lat-Lon_Root-Dep_Turb_Oxy_Sal_Dis*) and then the model with just *Temp* (*Lat-Lon_Temp_Turb_Oxy_Sal*) and no *Distance to shore* variable.
  
 I must choose the *Root-Dep* Model as the best model since it has the lowest AIC (beside the top model which I can't use).
```{r}
sn_s1_FA_best <- sn_s1_FA$model_fits$'Lat-Lon_Root-Dep_Turb_Oxy_Sal_Dis'
sn_s1_FA_best

#8-29-2018#save(sn_s1_FA_best, file = "output/output_GAM/best_strat1/sharpnose/sn_s1_FA_best.rda")
```
```{r Remove sn_s1_FA Models when kniting}
rm(sn_s1_FA, sn_s1_1, sn_s1_dep, sn_s1_temp, sn_s1_1B)
```


### **Female Juvenile** S1
```{r, include=FALSE}
load(file = "output/output_GAM/strat1/Female/Juvenile/sn_s1_FJ.rda")
```

```{r}
sn_s1_FJ$results
```

Top model according to AIC contains both *Root-Dep* and *Temp*.

[row 1] **Lat-Lon, Root-Dep, Temp, Turb, Oxy, Bottyp**
`r sn_s1_FJ$results[1, c(3:7)]`

*Temp* only Model
[row 12] **Lat-Lon, Temp, Turb, Oxy, Dis, Bottyp**
`r sn_s1_FJ$results[12, c(3:7)]`

*Root-Dep* only Model
[row 27] **Lat-Lon, Root-Dep, Turb, Oxy, Bottyp**
`r sn_s1_FJ$results[27, c(3:7)]`

#### Top Model

```{r sn_s1_FJ mod1}
(sn_s1_FJ_1 <- sn_s1_FJ$model_fits$`Lat-Lon_Root-Dep_Temp_Turb_Oxy_Bottyp`)


par(mfrow = c(2,2))
gam.check(sn_s1_FJ_1)


plot(sn_s1_FJ_1, pages = 1)

par(mfrow = c(1,1))

plot(sn_s1_FJ_1, select = 2)
abline(h = 0, lty = 3, col = "red")

plot(sn_s1_FJ_1, select = 3)
abline(h = 0, lty = 3, col = "red")

plot(sn_s1_FJ_1, select = 4)
abline(h = 0, lty = 3, col = "red")

plot(sn_s1_FJ_1, select = 5)
abline(h = 0, lty = 3, col = "red")

```

Very Flat Smooths **Everything is Zero** through it's Entire Range. edf not overly large for any term explanatory variables all less than 5 and Lat-Lon edf less than 30.

#### Temp Model

```{r sn_s1_FJ Temp mod}
(sn_s1_FJ_Temp <- sn_s1_FJ$model_fits$`Lat-Lon_Temp_Turb_Oxy_Dis_Bottyp`)


par(mfrow = c(2,2))
gam.check(sn_s1_FJ_Temp)


plot(sn_s1_FJ_Temp, pages = 1)

par(mfrow = c(1,1))

plot(sn_s1_FJ_Temp, select = 2)
abline(h = 0, lty = 3, col = "red")

plot(sn_s1_FJ_Temp, select = 3)
abline(h = 0, lty = 3, col = "red")

plot(sn_s1_FJ_Temp, select = 4)
abline(h = 0, lty = 3, col = "red")

plot(sn_s1_FJ_Temp, select = 5)
abline(h = 0, lty = 3, col = "red")

```

The only term that is not zero through it's entire range here is *Temp*. edf looks fairly low for all terms but not too close to k`.

#### Depth Model

```{r sn_s1_FJ Depth mod}
(sn_s1_FJ_Dep <- sn_s1_FJ$model_fits$`Lat-Lon_Root-Dep_Turb_Oxy_Bottyp`)


par(mfrow = c(2,2))
gam.check(sn_s1_FJ_Dep)


plot(sn_s1_FJ_Dep, pages = 1)

par(mfrow = c(1,1))

plot(sn_s1_FJ_Dep, select = 2)
abline(h = 0, lty = 3, col = "red")

plot(sn_s1_FJ_Dep, select = 3)
abline(h = 0, lty = 3, col = "red")

plot(sn_s1_FJ_Dep, select = 4)
abline(h = 0, lty = 3, col = "red")

plot(sn_s1_FJ_Dep, select = 5)
abline(h = 0, lty = 3, col = "red")

```

*Oxybotm* edf = 1. Very flat smooths Everything is zero through it's entire range **Except** *Root-Dep*.

#### Other Top Models (delta AIC < 4)

The Top 4 Models all have delta AIC less than 4. Lets look at a few of these.

```{r sn_s1_FJ mod2}
(sn_s1_FJ_2 <- sn_s1_FJ$model_fits$`Lat-Lon_Root-Dep_Temp_Turb_Oxy_Dis_Bottyp`)


par(mfrow = c(2,2))
gam.check(sn_s1_FJ_2)


plot(sn_s1_FJ_2, pages = 1)

par(mfrow = c(1,1))

plot(sn_s1_FJ_2, select = 2)
abline(h = 0, lty = 3, col = "red")

plot(sn_s1_FJ_2, select = 3)
abline(h = 0, lty = 3, col = "red")

plot(sn_s1_FJ_2, select = 4)
abline(h = 0, lty = 3, col = "red")

plot(sn_s1_FJ_2, select = 5)
abline(h = 0, lty = 3, col = "red")

plot(sn_s1_FJ_2, select = 6)
abline(h = 0, lty = 3, col = "red")

```
*Dis.to.SHORE* edf = 1, All other edf's are fairly low but not close to k`. All smooths are essentially Zero.


```{r sn_s1_FJ mod3}
(sn_s1_FJ_3 <- sn_s1_FJ$model_fits$`Lat-Lon_Root-Dep_Temp_Turb_Oxy_Sal_Bottyp`)


par(mfrow = c(2,2))
gam.check(sn_s1_FJ_3)


plot(sn_s1_FJ_3, pages = 1)

par(mfrow = c(1,1))

plot(sn_s1_FJ_3, select = 2)
abline(h = 0, lty = 3, col = "red")

plot(sn_s1_FJ_3, select = 3)
abline(h = 0, lty = 3, col = "red")

plot(sn_s1_FJ_3, select = 4)
abline(h = 0, lty = 3, col = "red")

plot(sn_s1_FJ_3, select = 5)
abline(h = 0, lty = 3, col = "red")

plot(sn_s1_FJ_3, select = 6)
abline(h = 0, lty = 3, col = "red")

```
*Salbotm* edf = 1. Smooths are very flat and essentially zero. 


```{r sn_s1_FJ mod4}
(sn_s1_FJ_4 <- sn_s1_FJ$model_fits$`Lat-Lon_Root-Dep_Temp_Turb_Oxy_Sal_Dis_Bottyp`)


par(mfrow = c(2,2))
gam.check(sn_s1_FJ_4)


plot(sn_s1_FJ_4, pages = 1)

par(mfrow = c(1,1))

plot(sn_s1_FJ_4, select = 2)
abline(h = 0, lty = 3, col = "red")

plot(sn_s1_FJ_4, select = 3)
abline(h = 0, lty = 3, col = "red")

plot(sn_s1_FJ_4, select = 4)
abline(h = 0, lty = 3, col = "red")

plot(sn_s1_FJ_4, select = 5)
abline(h = 0, lty = 3, col = "red")

plot(sn_s1_FJ_4, select = 6)
abline(h = 0, lty = 3, col = "red")

plot(sn_s1_FJ_4, select = 7)
abline(h = 0, lty = 3, col = "red")

```
*Dis.to.Shore* and *salbotm* edf = 1. All smooths very flat and essentially zero.

#### Choosing Best Model sn_s1_FJ
```{r}
summary(sn_s1_FJ_1)
summary(sn_s1_FJ_Temp)
summary(sn_s1_FJ_Dep)

###
summary(sn_s1_FJ$model_fits$`Lat-Lon_Temp_Turb_Oxy_Bottyp`) # Top mod no dep #
summary(sn_s1_FJ$model_fits$`Lat-Lon_Root-Dep_Turb_Oxy_Bottyp`) # Top mod no Temp #

anova.gam(sn_s1_FJ_1, sn_s1_FJ_Temp, sn_s1_FJ_Dep, test = "Chisq")



```

The best model I can see is the *Temp* Model **Lat-Lon_Temp_Turb_Oxy_Bottyp**

```{r}
sn_s1_FJ_best <- sn_s1_FJ$model_fits$'Lat-Lon_Temp_Turb_Oxy_Bottyp'
sn_s1_FJ_best

#8-29-2018#save(sn_s1_FJ_best, file = "output/output_GAM/best_strat1/sharpnose/sn_s1_FJ_best.rda")
```

### **Male Adult** S1
```{r, include=FALSE}
load(file = "output/output_GAM/strat1/Male/Adult/sn_s1_MA.rda")
```

```{r}
sn_s1_MA$results
```

 
 [row 1] **Lat-Lon_Root-Dep_Temp_Turb**
 `r sn_s1_MA$results[1, c(3:7)]`
 
 [row 17] **Dep not temp >> Lat-Lon_Root-Dep_Turb_Oxy_Sal_Dis**
 `r sn_s1_MA$results[17, c(3:7)]`
 
 [row 35] **Temp not dep >> Lat-Lon_Temp_Turb_Dis_Bottyp**
 `r sn_s1_MA$results[35, c(3:7)]`
 
#### Top Model 
 
```{r sn_s1_MA Model 1}
(sn_s1_MA_1 <- sn_s1_MA$model_fits$'Lat-Lon_Root-Dep_Temp_Turb')


par(mfrow = c(2,2))
gam.check(sn_s1_MA_1)


plot(sn_s1_MA_1, pages = 1)

par(mfrow = c(1,1))

plot(sn_s1_MA_1, select = 2)
abline(h = 0, lty = 3, col = "red")

plot(sn_s1_MA_1, select = 3)
abline(h = 0, lty = 3, col = "red")

plot(sn_s1_MA_1, select = 4)
abline(h = 0, lty = 3, col = "red")


```
This model looks pretty good. Except it includes both *temp* and *Depth*

#### Depth Model

```{r sn_s1_MA Depth Model}
(sn_s1_MA_dep <- sn_s1_MA$model_fits$'Lat-Lon_Root-Dep_Turb_Oxy_Sal_Dis')

par(mfrow = c(2,2))
gam.check(sn_s1_MA_dep)


plot(sn_s1_MA_dep, pages = 1)

par(mfrow = c(1,1))

plot(sn_s1_MA_dep, select = 2)
abline(h = 0, lty = 3, col = "red")

plot(sn_s1_MA_dep, select = 3)
abline(h = 0, lty = 3, col = "red")

plot(sn_s1_MA_dep, select = 4)
abline(h = 0, lty = 3, col = "red")

plot(sn_s1_MA_dep, select = 5)
abline(h = 0, lty = 3, col = "red")

plot(sn_s1_MA_dep, select = 6)
abline(h = 0, lty = 3, col = "red")

```
*Dis.to.SHORE* edf = 1, *Oxybotm* edf near 1 (1.19).

*Oxybotm*, *salbotm*, and *Dis.to.SHORE* are Zero everywhere

#### Temp Model


```{r sn_s1_MA Temp Model}
(sn_s1_MA_temp <- sn_s1_MA$model_fits$'Lat-Lon_Temp_Turb_Dis_Bottyp')

par(mfrow = c(2,2))
gam.check(sn_s1_MA_temp)


plot(sn_s1_MA_temp, pages = 1)

par(mfrow = c(1,1))

plot(sn_s1_MA_temp, select = 2)
abline(h = 0, lty = 3, col = "red")

plot(sn_s1_MA_temp, select = 3)
abline(h = 0, lty = 3, col = "red")

plot(sn_s1_MA_temp, select = 4)
abline(h = 0, lty = 3, col = "red")
```

The *Temp* model looks pretty good. 

*Dis.to.SHORE* is Zero Everywhere.

#### Choosinf best Model sn_s1_MA

```{r Compare sn_s1_MA Models}
summary(sn_s1_MA_1)
summary(sn_s1_MA_dep)
summary(sn_s1_MA_temp)

# Anova Fails data sets are not the same size
#anova.gam(sn_s1_MA_1, sn_s1_MA_dep, sn_s1_MA_temp, test = "Chisq")

AIC(sn_s1_MA_1, sn_s1_MA_dep, sn_s1_MA_temp)

```

The best model here seems to be the *depth* model **Lat-Lon_Root-Dep_Turb_Oxy_Sal_Dis**  

```{r sn_s1_MA Best Model}
(sn_s1_MA_best <- sn_s1_MA$model_fits$'Lat-Lon_Root-Dep_Turb_Oxy_Sal_Dis')


#8-29-2018#save(sn_s1_MA_best, file = "output/output_GAM/best_strat1/sharpnose/sn_s1_MA_best.rda")
```
```{r Remove sn_s1_MA Models when kniting}
rm(sn_s1_MA, sn_s1_MA_1, sn_s1_MA_dep, sn_s1_MA_temp)
```


### **Male Juvenile** S1
```{r, include=FALSE}
load(file = "output/output_GAM/strat1/Male/Juvenile/sn_s1_MJ.rda")
```

```{r}
sn_s1_MJ$results
```

Top 10 Models delta AIC less than 4.

 [row 1] **Lat-Lon_Root-Dep_Temp_Turb_Oxy_Sal_Bottyp**
 `r sn_s1_MJ$results[1, c(3:7)]`
 
  [row 16] **Temp not dep >> Lat-Lon_Temp_Turb_Oxy**
 `r sn_s1_MJ$results[16, c(3:7)]`
 
 [row 33] **Dep not temp >> Lat-Lon_Root-Dep_Turb_Oxy_Sal_Dis_Bottyp**
 `r sn_s1_MJ$results[33, c(3:7)]`
 


#### Top Model
```{r}
(sn_s1_MJ_1 <- sn_s1_MJ$model_fits$`Lat-Lon_Root-Dep_Temp_Turb_Oxy_Sal_Bottyp`)


par(mfrow = c(2,2))
gam.check(sn_s1_MJ_1)


plot(sn_s1_MJ_1, pages = 1)

par(mfrow = c(1,1))

plot(sn_s1_MJ_1, select = 2)
abline(h = 0, lty = 3, col = "red")

plot(sn_s1_MJ_1, select = 3)
abline(h = 0, lty = 3, col = "red")

plot(sn_s1_MJ_1, select = 4)
abline(h = 0, lty = 3, col = "red")

plot(sn_s1_MJ_1, select = 5)
abline(h = 0, lty = 3, col = "red")

plot(sn_s1_MJ_1, select = 6)
abline(h = 0, lty = 3, col = "red")



```
*salbotm*edf = 1. *turbbotm* edf near 1 (1.15). All smooths very flat and essentially zero.

#### Temp Model
```{r}
(sn_s1_MJ_temp <- sn_s1_MJ$model_fits$`Lat-Lon_Temp_Turb_Oxy`)


par(mfrow = c(2,2))
gam.check(sn_s1_MJ_temp)


plot(sn_s1_MJ_temp, pages = 1)

par(mfrow = c(1,1))

plot(sn_s1_MJ_temp, select = 2)
abline(h = 0, lty = 3, col = "red")

plot(sn_s1_MJ_temp, select = 3)
abline(h = 0, lty = 3, col = "red")

plot(sn_s1_MJ_temp, select = 4)
abline(h = 0, lty = 3, col = "red")

```
*oxybotm* edf = 1. With the exception of *tempbotm* all smooths are essentially 0.


#### Top Mod with no *Root-Depth* **sn_s1_MJ$model_fits$`Lat-Lon_Temp_Turb_Oxy_Sal_Bottyp`**

```{r}
(sn_s1_MJ_temp2 <- sn_s1_MJ$model_fits$`Lat-Lon_Temp_Turb_Oxy_Sal_Bottyp`)


par(mfrow = c(2,2))
gam.check(sn_s1_MJ_temp2)


plot(sn_s1_MJ_temp2, pages = 1)

par(mfrow = c(1,1))

plot(sn_s1_MJ_temp2, select = 2)
abline(h = 0, lty = 3, col = "red")

plot(sn_s1_MJ_temp2, select = 3)
abline(h = 0, lty = 3, col = "red")

plot(sn_s1_MJ_temp2, select = 4)
abline(h = 0, lty = 3, col = "red")

plot(sn_s1_MJ_temp2, select = 5)
abline(h = 0, lty = 3, col = "red")

```


#### Depth Model
```{r}
(sn_s1_MJ_dep <- sn_s1_MJ$model_fits$`Lat-Lon_Root-Dep_Turb_Oxy_Sal_Dis_Bottyp`)


par(mfrow = c(2,2))
gam.check(sn_s1_MJ_dep)


plot(sn_s1_MJ_dep, pages = 1)

par(mfrow = c(1,1))

plot(sn_s1_MJ_dep, select = 2)
abline(h = 0, lty = 3, col = "red")

plot(sn_s1_MJ_dep, select = 3)
abline(h = 0, lty = 3, col = "red")

plot(sn_s1_MJ_dep, select = 4)
abline(h = 0, lty = 3, col = "red")

plot(sn_s1_MJ_dep, select = 5)
abline(h = 0, lty = 3, col = "red")

plot(sn_s1_MJ_dep, select = 6)
abline(h = 0, lty = 3, col = "red")

```
*oxybotm*, *salbotm*, *Dis.to.SHORE* edf = 1. All Smooths essentially zero.


#### Choosing Best Model


```{r}
summary(sn_s1_MJ_1)
summary(sn_s1_MJ_temp)
summary(sn_s1_MJ_dep)

###
summary(sn_s1_MJ$model_fits$`Lat-Lon_Temp_Turb_Oxy_Sal_Bottyp`) # Top mod no dep # This may be a bit better than temp higher dev explained, rsq BUT UBRE is Higher
summary(sn_s1_MJ$model_fits$`Lat-Lon_Root-Dep_Turb_Oxy_Sal_Bottyp`) # Top mod no Temp # Not as good

anova.gam(sn_s1_FJ_1, sn_s1_FJ_Temp, sn_s1_MJ_temp2, sn_s1_FJ_Dep, test = "Chisq")
anova.gam(sn_s1_FJ_1, sn_s1_FJ_Temp, sn_s1_FJ_Dep, test = "Chisq")

AIC(sn_s1_FJ_1, sn_s1_FJ_Temp, sn_s1_MJ_temp2, sn_s1_FJ_Dep) ### this is strange AIC given here is different than the AIC in the results table

```

The Best Model is the *Temp2* Model **Lat-Lon_Temp_Turb_Oxy_Sal_Bottyp**. 


```{r}
sn_s1_MJ_best <- sn_s1_MJ$model_fits$'Lat-Lon_Temp_Turb_Oxy_Sal_Bottyp'
sn_s1_MJ_best

#8-29-2018#save(sn_s1_MJ_best, file = "output/output_GAM/best_strat1/sharpnose/sn_s1_MJ_best.rda")
```



## Strata 2 Zero-Truncated Abundance

### **Female Adult** S2
```{r, include=FALSE}
load(file = "output/output_GAM/strat2/Female/Adult/sn_s2_FA.rda")
```

```{r}
sn_s2_FA$results
```

Top 9 models delta AIC < 4


Top model **Lat-Lon_Root-Dep_Temp_Turb** [row 1]

**Temp** Model **Lat-Lon_Temp_Turb_Sal_Dis** [row 17]

**Depth** Model **Lat-Lon_Root-Dep_Turb_Sal** [row 33]

#### Top Model
```{r}
(sn_s2_FA_1 <- sn_s2_FA$model_fits$`Lat-Lon_Root-Dep_Temp_Turb`)

par(mfrow = c(2,2))
gam.check(sn_s2_FA_1)


plot(sn_s2_FA_1, pages = 1)

```


#### Temp Model

```{r}
(sn_s2_FA_temp <- sn_s2_FA$model_fits$`Lat-Lon_Temp_Turb_Sal_Dis`)

par(mfrow = c(2,2))
gam.check(sn_s2_FA_temp)


plot(sn_s2_FA_temp, pages = 1)

```
*Dis.to.SHORE* edf = 1.

#### Choosing Best Model sn_s2_FA

```{r}
summary(sn_s2_FA_1)
summary(sn_s2_FA_temp)

anova.gam(sn_s2_FA_1, sn_s2_FA_temp, test = "Chisq")

AIC(sn_s2_FA_1, sn_s2_FA_temp)


```

```{r}
sn_s2_FA_best <- sn_s2_FA$model_fits$`Lat-Lon_Temp_Turb_Sal_Dis`
sn_s2_FA_best


#8-29-2018#save(sn_s2_FA_best, file = "output/output_GAM/best_strat2/sharpnose/sn_s2_FA_best.rda")
```



### **Female Juvenile** S2
```{r, include=FALSE}
load(file = "output/output_GAM/strat2/Female/Juvenile/sn_s2_FJ.rda")
```

```{r}
sn_s2_FJ$results
```

delta AIC < 4 for top 7 models

**Top Model** is **Lat-Lon_Temp_Turb_Dis_Bottyp**
This is also the **Temp Model**
I'll just go with the top model as the best in this case

```{r}
sn_s2_FJ_best <- sn_s2_FJ$model_fits$`Lat-Lon_Temp_Turb_Dis_Bottyp`
sn_s2_FJ_best

par(mfrow = c( 2,2))
gam.check(sn_s2_FJ_best)

plot(sn_s2_FJ_best, pages = 1)


#8-29-2018#save(sn_s2_FJ_best, file = "output/output_GAM/best_strat2/sharpnose/sn_s2_FJ_best.rda")
```
*Dis.to.SHORE* edf = 1. Turbbotm very wiggly.




### **Male Adult** S2
```{r, include=FALSE}
load(file = "output/output_GAM/strat2/Male/Adult/sn_s2_MA.rda")
```

```{r}
sn_s2_MA$results
```

**Top Model** is **Depth** Model **

```{r}
(sn_s2_MA_best <- sn_s2_MA$model_fits$'Lat-Lon_Root-Dep_Turb_Oxy_Sal_Bottyp')

par(mfrow = c(2,2))
gam.check(sn_s2_MA_best)

summary(sn_s2_MA_best)

#8-29-2018#save(sn_s2_MA_best, file = "output/output_GAM/best_strat2/sharpnose/sn_s2_MA_best.rda")
```



### **Male Juvenile** S2
```{r, include=FALSE}
load(file = "output/output_GAM/strat2/Male/Juvenile/sn_s2_MJ.rda")
```

```{r}
sn_s2_MJ$results
```

```{r}
(sn_s2_MJ_best <- sn_s2_MJ$model_fits$'Lat-Lon_Temp_Turb_Oxy_Sal')


par(mfrow = c(2,2))
gam.check(sn_s2_MJ_best)

summary(sn_s2_MJ_best)

#8-29-2018#save(sn_s2_MJ_best, file = "output/output_GAM/best_strat2/sharpnose/sn_s2_MJ_best.rda")

```
*Year* edf is essentially zero.







# Sandbar


















