---
title: "Data Exploration"
author: "Alex Benecke"
date: "August 15, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Load Packages, include=FALSE}
require(FSA)
require(tidyverse)
require(dplyr)
require(magrittr)
require(scales)
require(pipeR)
require(kableExtra)



source("5_functions/dropbox_fn.R") # For interacting with dropbox
proj = "shark" # Specify project where data is stored 

source("5_functions/load_data.R")
```

```{r Load Data, results = 'hide'}
eff3 <- read_csv_fn( "data/clean-data/CPUE3.csv", proj)

eff3$count <- 1

str(eff3)
headtail(eff3)

strat1_Adult <- load_data(data = eff3[eff3$maturity == "A",], strata = 1)
strat2_Adult <- load_data(data = eff3[eff3$maturity == "A",], strata = 2)

strat1_Juvenile <- load_data(data = eff3[eff3$maturity == "J",], strata = 1)
strat2_Juvenile <- load_data(data = eff3[eff3$maturity == "J",], strata = 2)

```

```{r Make unique Station.ID, results = 'hide'}

### S1 Adult

for(i in 1:length(strat1_Adult)){
  
  for(j in 1:length(strat1_Adult[[i]])){
    
      for(k in 1:nrow(strat1_Adult[[i]][[j]])){
    
    strat1_Adult[[i]][[j]]$Station.ID[k] <- paste0("Station_", k)
    
  }
    
  }
  
}

headtail(strat1_Adult[[1]][[5]])
str(strat1_Adult[[1]][[5]])

### S1 Juvenile

for(i in 1:length(strat1_Juvenile)){
  
  for(j in 1:length(strat1_Juvenile[[i]])){
    
      for(k in 1:nrow(strat1_Juvenile[[i]][[j]])){
    
    strat1_Juvenile[[i]][[j]]$Station.ID[k] <- paste0("Station_", k)
    
  }
    
  }
  
}


headtail(strat1_Juvenile[[1]][[5]])
str(strat1_Juvenile[[1]][[5]])
### S2 Adult

for(i in 1:length(strat2_Adult)){
  
  for(j in 1:length(strat2_Adult[[i]])){
    
      for(k in 1:nrow(strat2_Adult[[i]][[j]])){
    
    strat2_Adult[[i]][[j]]$Station.ID[k] <- paste0("Station_", k)
    
  }
    
  }
  
}


headtail(strat2_Adult[[1]][[5]])
str(strat2_Adult[[1]][[5]])
### S2 Juvenile


for(i in 1:length(strat2_Juvenile)){
  
  for(j in 1:length(strat2_Juvenile[[i]])){
    
      for(k in 1:nrow(strat2_Juvenile[[i]][[j]])){
    
    strat2_Juvenile[[i]][[j]]$Station.ID[k] <- paste0("Station_", k)
    
  }
    
  }
  
}


headtail(strat2_Juvenile[[1]][[5]])
str(strat2_Juvenile[[1]][[5]])





```


## Sample sizes

### Table of Positive catch sites per year
```{r Make Data frame for numver of sites with positive catch each year, results = 'hide'}
Species <- levels(eff3$common)

for(i in 1:length( levels( eff3$common ) ) ){
  
 ## Female Adult
  aggregate(pres ~ year, data =strat1_Adult$Female[[i]], FUN = sum, drop = FALSE)[,"pres"] %>%
    t() %>%
    data.frame() %>%
    mutate( Species = Species[i], Sex = "Female", Maturity = "Adult") %>>%
    (~tmp_FA)
  
  colnames(tmp_FA) <- c(seq(2001,2017,1), "Species", "Sex", "Maturity")


 ## Female Juvenile
  aggregate(pres ~ year, data =strat1_Juvenile$Female[[i]], FUN = sum, drop = FALSE)[,"pres"] %>%
    t() %>%
    data.frame() %>%
    mutate( Species = Species[i], Sex = "Female", Maturity = "Juvenile") %>>%
    (~tmp_FJ)
  
  colnames(tmp_FJ) <- c(seq(2001,2017,1), "Species", "Sex", "Maturity")


 ## Male Adult
  aggregate(pres ~ year, data =strat1_Adult$Male[[i]], FUN = sum, drop = FALSE)[,"pres"] %>%
    t() %>%
    data.frame() %>%
    mutate( Species = Species[i], Sex = "Male", Maturity = "Adult")  %>>%
    (~tmp_MA)
  
  colnames(tmp_MA) <- c(seq(2001,2017,1), "Species", "Sex", "Maturity")


 ## Male Juvenile
  aggregate(pres ~ year, data =strat1_Juvenile$Male[[i]], FUN = sum, drop = FALSE)[,"pres"] %>%
    t() %>%
    data.frame() %>%
    mutate( Species = Species[i], Sex = "Male", Maturity = "Juvenile") %>>%
    (~tmp_MJ)
  
  colnames(tmp_MJ) <- c(seq(2001,2017,1), "Species", "Sex", "Maturity")

if(i == 1){
  
  rbind(tmp_FA, tmp_FJ, tmp_MA, tmp_MJ) %>>%
    (~tmp.df)  
  
} else{
  
  rbind(tmp.df, tmp_FA, tmp_FJ, tmp_MA, tmp_MJ) %>>%
    (~tmp.df)
  
}

}



pres.tbl <- tmp.df %>%
  select(Species, Sex, Maturity, "2001":"2017")
pres.tbl



pres.tbl$Total <- apply(pres.tbl[,4:20], 1, FUN = sum)
pres.tbl

 
#tmpa <- aggregate(Total ~ Species + Sex , data = pres.tbl, FUN = sum, drop = FALSE) %>%
#  arrange(Species)
#tmpa

#pres.tbl$Sex.Total <- rep(tmpa$Total,each = 2)
#pres.tbl

#tmpb <- aggregate(Total ~ Species , data = pres.tbl, FUN = sum, drop = FALSE) %>%
#  arrange(Species)
#tmpb


#pres.tbl$Species.Total <- rep(tmpb$Total,each = 4)

pres.tbl

```


```{r,include=FALSE, eval=FALSE}
### Get total for combined species by Sex and Maturity for each Year

### All Species
#pres.tbl

### Female Adult
FA <- subset(pres.tbl, Sex =="Female" & Maturity == "Adult")
FA <- apply(FA[,c(4:20)], 2, FUN = sum) %>% t() %>%  data.frame()
colnames(FA) <- seq(2001, 2017, 1)

FA$Species <- "All Species"
FA$Sex <- "Female"
FA$Maturity <- "Adult"

FA %<>% select(Species, Sex, Maturity, "2001":"2017")
#FA

### Female Juvenile
FJ <- subset(pres.tbl, Sex =="Female" & Maturity == "Juvenile")
FJ <- apply(FJ[,c(4:20)], 2, FUN = sum)%>% t() %>%  data.frame()
colnames(FJ) <- seq(2001, 2017, 1)

FJ$Species <- "All Species"
FJ$Sex <- "Female"
FJ$Maturity <- "Juvenile"

FJ %<>% select(Species, Sex, Maturity, "2001":"2017")
#FJ

### Male Adult
MA <- subset(pres.tbl, Sex =="Male" & Maturity == "Adult")
MA <- apply(MA[,c(4:20)], 2, FUN = sum)%>% t() %>%  data.frame()
colnames(MA) <- seq(2001, 2017, 1)

MA$Species <- "All Species"
MA$Sex <- "Male"
MA$Maturity <- "Adult"

MA %<>% select(Species, Sex, Maturity, "2001":"2017")
#MA

### Male Juvenile
MJ <- subset(pres.tbl, Sex =="Male" & Maturity == "Juvenile")
MJ <- apply(MJ[,c(4:20)], 2, FUN = sum)%>% t() %>%  data.frame()
colnames(MJ) <- seq(2001, 2017, 1)

MJ$Species <- "All Species"
MJ$Sex <- "Male"
MJ$Maturity <- "Juvenile"

MJ %<>% select(Species, Sex, Maturity, "2001":"2017")
#MJ


sex.mat.tbl <- rbind(FA, FJ, MA, MJ)


#sex.mat.tbl$Species.Total <- NA

sex.mat.tbl$Total <- apply(sex.mat.tbl[,c(4:20)], 1, FUN = sum)

tmp.sex.total <- rbind(sum(FA[,c(4:20)],FJ[,c(4:20)]), sum(MA[,c(4:20)],MJ[,c(4:20)]))
#tmp.sex.total

sex.mat.tbl$Sex.Total <- rep(tmp.sex.total, each = 2)
sex.mat.tbl$Species.Total <- NA

sex.mat.tbl
```

```{r, results = 'hide'}

### Get total number of sites sampled each year
aggregate(count ~ year, data =strat1_Adult$Female[[i]], FUN = sum, drop = FALSE)[,"count"] %>%
    t() %>%
    data.frame() %>%
    mutate( Species = "Total Stations", Sex = "", Maturity = "") %>>%
    (~all.sites.yr.sum)
  
  colnames(all.sites.yr.sum) <- c(seq(2001,2017,1), "Species", "Sex", "Maturity")

all.sites.yr.sum %<>%
  select(Species, Sex, Maturity, "2001":"2017")

all.sites.yr.sum

all.sites.yr.sum$Total <- apply(all.sites.yr.sum[,c(4:20)], 1, FUN = sum)

all.sites.yr.sum


#all.sites.yr.sum$Sex.Total <- NA
#all.sites.yr.sum$Species.Total <- NA
all.sites.yr.sum


pres.tbl <- rbind(pres.tbl, all.sites.yr.sum)
pres.tbl

#8-20-2018#write_csv_fn(pres.tbl, file = "data/clean-data/table-data/pres_tbl.csv", proj = proj)

```





```{r Make table of positive catch sites per year}
pres.tbl %>%
  kable() %>%
  kable_styling(full_width = F, 
                position = "center", 
                font_size = 10,
                bootstrap_options = "striped") %>%
  column_spec(1, bold = T, background = "White") %>%
  column_spec(2, background = "White") %>%
  column_spec(21, border_left = T) %>%
  collapse_rows(c(1:3), valign = "middle")
```


I will not be able to use **Maturity** for **Tiger**, and Possibly **Spinner**, and **Bull**. 


### Table Percent Sites sampled per year with Positive catch


```{r Prep Percent pos catch table, results='hide'}
all.sites.yr.sum <- pres.tbl[29,-c(22:23)]
row.names(all.sites.yr.sum) <- c(1)         

all.sites.yr.sum


tmp <- pres.tbl[c(1:28),-c(22:23)]
tmp


for(i in 1:nrow(tmp)){
  
  tmp[i,c(4:21)] <- round((tmp[i,c(4:21)]/all.sites.yr.sum[1,c(4:21)])*100, 1)
  
}


tmp

percent.pres.tbl <- tmp


percent.pres.tbl

#8-20-2018#write_csv_fn(percent.pres.tbl, file = "data/clean-data/table-data/percent_pres_tbl.csv", proj = proj)


```

```{r Make table of Percent positive of each species by year}
percent.pres.tbl %>%
  kable() %>%
  kable_styling(full_width = F, 
                position = "center", 
                font_size = 10,
                bootstrap_options = "striped") %>%
  column_spec(1, bold = T, background = "White") %>%
  column_spec(2, background = "White") %>%
  column_spec(21, border_left = T) %>%
  collapse_rows(c(1:3), valign = "middle")
```



I need a table of descriptive stats

## Variables

I will make a table with each variable and its range and mean

```{r, results='hide'}
head(strat1_Adult$Male$sharpnose)

var.tbl <- eff3 %>%
  select(year, startlat, startlon, startdepth, tempbotm, fluorobotm, turbbotm, oxybotm, salbotm, Dis.to.SHORE, CPUE, Adj.CPUE)

head(var.tbl)

length(var.tbl)



Min <- round(apply(var.tbl, 2, FUN =  min, na.rm = T),0)
Max <- round(apply(var.tbl, 2, FUN =  max, na.rm = T),0)
Mean <- round(apply(var.tbl, 2, FUN =  mean, na.rm = T),0)
SD <- round(apply(var.tbl, 2, FUN =  sd, na.rm = T),0)

var.tbl.2 <- rbind(Min, Max, Mean, SD) %>% t() %>% data.frame()

var.tbl.2

#var.tbl.2$Variable <- rownames(var.tbl.2) 

#var.tbl.2

#var.tbl.2 %<>%  select(Variable, Min:Mean)

#var.tbl.2


#8-20-2018#write_csv_fn(var.tbl.2, file = "data/clean-data/table-data/var_tbl.csv", proj = proj)

```


```{r}
var.tbl.2 %>%
  kable() %>%
  kable_styling(full_width = F, 
                position = "center", 
                font_size = 10,
                bootstrap_options = "striped") 
```


| Variable                    | Range                                     | Mean | 2001 | 2002 | 2003 | 2004 | 2005 | ... | 2017 | 
|:---------------------------:|:-----------------------------------------:|:---:|:---:|:---:|:---:|:---:|:---:|:---:|
| Lattitude                   |  `r range(eff3$startlat , na.rm=T)`       |  `r mean(eff3$startlat , na.rm=T)`      |     |     |     |     |     |     | |
| Longitude                   |  `r range(eff3$startlon , na.rm=T)`       |  `r mean(eff3$startlon , na.rm=T)`      |     |     |     |     |     |     | |
| Depth (m)                   |  `r range(eff3$startdepth , na.rm=T)`     |  `r mean(eff3$startdepth , na.rm=T)`   |     |     |     |     |     |     | |
| Temperature (C)             |  `r range(eff3$tempbotm , na.rm=T)`       |  `r mean(eff3$tempbotm , na.rm=T)`      |     |     |     |     |     |     | | 
| Fluoro                      |  `r range(eff3$fluorobotm , na.rm=T)`     |  `r mean(eff3$fluorobotm , na.rm=T)`   |     |     |     |     |     |     | |
| Turbidity                   |  `r range(eff3$turbbotm , na.rm=T)`       |  `r mean(eff3$turbbotm , na.rm=T)`      |     |     |     |     |     |     | | 
| Bottom Oxygen               |  `r range(eff3$oxybotm , na.rm=T)`        |  `r mean(eff3$oxybotm , na.rm=T)`         |     |     |     |     |     |     | | 
| Salinity                    |  `r range(eff3$salbotm , na.rm=T)`        |  `r mean(eff3$salbotm , na.rm=T)`         |     |     |     |     |     |     | |
| Distance to Shore (km)      |  `r range(eff3$Dis.to.SHORE , na.rm=T)`   |  `r mean(eff3$Dis.to.SHORE , na.rm=T)`   |     |     |     |     |     |     | |
| CPUE                        |  `r range(eff3$CPUE , na.rm=T)`           |  `r mean(eff3$CPUE , na.rm=T)`              |     |     |     |     |     |     | |
| Adj.CPUE                    |  `r range(eff3$Adj.CPUE , na.rm=T)`       |  `r mean(eff3$Adj.CPUE , na.rm=T)`      |     |     |     |     |     |     | | 



### Need to do


Number Male Female and Unknown as well as Adult Juvenile and Unknown




