---
title: "Northern Gulf of Mexico Sharks (Draft)"
author: "Alex Benecke"
date: "July 20, 2018"
output:  
  html_document:
    df_print: paged
    toc: true
    toc_float: true
    toc_depth: 4
    fig_width: 8
    fig_height: 6
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Load Packages, include=FALSE}
### Load Packages
library(FSA)
library(tidyverse)
library(dplyr)
library(magrittr)
library(scales)
library(mgcv)
library(sciplot)
#source("plot_centered_mean.R")
source("functions/my_summary.R")
source("functions/k_est_fn.R")
source("functions/fit_gam.R")
```


```{r Load Data, echo=FALSE, include=FALSE}
blacknose <- read.csv("data/acronotus.df.csv") 
blacknose$DATE <- as.POSIXlt(blacknose$DATE)
blacknose$MONTH <- factor(strftime(blacknose$DATE, format = "%b"))
blacknose$YEAR <- factor(blacknose$YEAR)
tmp.bn <- blacknose[blacknose$cpe>0,]
      
str(blacknose)


blacktip <- read.csv("data/limbatus.df.csv")
blacktip$DATE <- as.POSIXlt(blacktip$DATE)
blacktip$MONTH  <- factor(strftime(blacktip$DATE, format = "%b"))
blacktip$YEAR <- factor(blacktip$YEAR)
tmp.bt <- blacktip[blacktip$cpe>0,]

str(blacktip)

bull <- read.csv("data/leucas.df.csv")
bull$DATE <- as.POSIXlt(bull$DATE)
bull$MONTH  <- factor(strftime(bull$DATE, format = "%b"))
bull$YEAR <- factor(bull$YEAR)
tmp.bu <- bull[bull$cpe>0,]

str(bull)

sandbar <- read.csv("data/plumbeus.df.csv")
sandbar$DATE <- as.POSIXlt(sandbar$DATE)
sandbar$MONTH  <- factor(strftime(sandbar$DATE, format = "%b"))
sandbar$YEAR <- factor(sandbar$YEAR)
tmp.sb <- sandbar[sandbar$cpe>0,]

str(sandbar)

sharpnose <- read.csv("data/terraenovae.df.csv")
sharpnose$DATE <- as.POSIXlt(sharpnose$DATE)
sharpnose$MONTH  <- factor(strftime(sharpnose$DATE, format = "%b"))
sharpnose$YEAR <- factor(sharpnose$YEAR)
tmp.sn <- sharpnose[sharpnose$cpe>0,]

str(sharpnose)

silky <- read.csv("data/falciformis.df.csv")
silky$DATE <- as.POSIXlt(silky$DATE)
silky$MONTH  <- factor(strftime(silky$DATE, format = "%b"))
silky$YEAR <- factor(silky$YEAR)
tmp.si <- silky[silky$cpe>0,]

str(silky)

spinner <- read.csv("data/brevipinna.df.csv")
spinner$DATE <- as.POSIXlt(spinner$DATE)
spinner$MONTH <- factor(strftime(spinner$DATE, format = "%b"))
spinner$YEAR <- factor(spinner$YEAR)
tmp.sp <- spinner[spinner$cpe>0,]

str(spinner)

tiger <- read.csv("data/cuvier.df.csv")
tiger$DATE <- as.POSIXlt(tiger$DATE)
tiger$MONTH  <- factor(strftime(tiger$DATE, format = "%b"))
tiger$YEAR <- factor(tiger$YEAR)
tmp.ti <- tiger[tiger$cpe>0,]

str(tiger)


sp.df <- list(blacknose = blacknose,
              blacktip = blacktip,
              bull = bull,
              sandbar = sandbar,
              sharpnose = sharpnose,
              silky = silky,
              spinner = spinner,
              tiger = tiger)


```

```{r Load Models, echo=FALSE}
load(file = "model-output/bn_gam_fits.rda")

load(file = "model-output/sp_gam_fits.rda")

load(file = "model-output/si_gam_fits.rda")

load(file = "model-output/bu_gam_fits.rda")

load(file = "model-output/bt_gam_fits.rda")

load(file = "model-output/sb_gam_fits.rda")

load(file = "model-output/ti_gam_fits.rda")

load(file = "model-output/sn_gam_fits.rda")

load(file = "model-output/bn_gam_select_1.rda")
load(file = "model-output/bt_gam_select.rda")
load(file = "model-output/bu_gam_select.rda") 
load(file = "model-output/sb_gam_select.rda")
load(file = "model-output/sn_gam_select.rda")
load(file = "model-output/sn_gam_select_2.rda")
load(file = "model-output/si_gam_select.rda")
load(file = "model-output/sp_gam_select.rda")
load(file = "model-output/ti_gam_select.rda")

```


## Abstract ##


## Introduction ##




...We used Generalized Additive Models (GAMs) to describe the spatial distribution and abundance of 8 species of northern Gulf of Mexico (GoM) sharks. 

## Methods ##

  The data used in this study were collected from an annual NOAA longline survey of northern Gulf of Mexico fishes. Sampling was conducted annually between July and November from 1995 to 2013, with the exception of 1998 for which no data is available. Stations were selected randomly each year and covered the entire northern Gulf of Mexico from Texas to Florida above $24.36^\circ$ Latitude (*Figure 2*). Eight shark species sharks (blacknose [$\textit{Carcharhinus acronotus}$], blacktip [$\textit{C. limbatus}$], bull [$\textit{C. leucas}$], sandbar [$\textit{C. plumbeus}$], sharpnose [$\textit{C. terraenova}$], silky [$\textit{C. falciformis}$], spinner [$\textit{C. brevipinna}$], and tiger [$\textit{C. cuvier}$]) commonly found in the northern Gulf of Mexico were captured and catch per unit effort (CPUE) was calculated for each species at each station. Additionally, a suite of environmental variables were recorded at each station including average depth (m), bottom salinity (PSU), bottom temperature ($^\circ$C), bottom fluorescence, bottom turbidity (FNU), and bottom dissolved oxygen ($mg*L^{-1}$). Information about the composition of the bottom substrate at each station was used to create a factor variable with eight levels pertaining to either dominance or sub-dominance of either mud, sand, gravel, or rock.
  
  
  To ensure only good quality data was used in the model building process basic descriptive statistics and plots were generated for CPUE and the explanatory variables. Erroneous salinity values were removed if values were greater than 40 or less than 15 PSU. Values for bottom dissolved oxygen were removed if they were equal to 0 or greater than 12 $mg*L^{-1}$. Bottom fluorometry and turbidity were not used as explanatory variables due to a high proportion of missing data (n = 1869, 925 respectively). Correlation between variables was assessed using a correlation matrix and pairwise scatter plots.
  
  
  We utilized a two strata generalized additive model (GAM) to investigate the relationship between the spatial distribution of northern GoM shark species and a suite of environmental variables. The first stratum modeled the presents-absence of northern GoM sharks assuming a binomial error distribution and a log link function. The second strata modeled the CPUE of northern GoM sharks including only stations with positive catch and assuming a gamma error distribution and a log link function. The full model is given as:
$$g_{1}(y) = g_{2}(Lon, Lat) + \sum^{n}_{i=1} s_{i}(x_{i}) + factor(Bottom ~ Substrate) + re_{yr} + \epsilon $$
where $g_1()$ is the link function for the response variable $y$, $g_{2}(Lon, Lat)$ is 2-dimensional isotropic thin plate regression spline (TPRS) smooth of Latitude and Longitude, $s_{i}(x_i)$ is the $i^{th}$ 1-dimensional TPRS smooth of the $i^th$ predictor variable $x$, $factor(Bottom Substrate)$ is a factor variable for bottom substrate, $re_{yr}$ is a random effect for year, and $\epsilon$ is random error. Basis dimensions ($k$) were estimated using the formula suggested by Kim and Gu (2004) k=10*n^(2/9) where n is the number of data.


  We use a multi-model approach identify the best fit model for each shark species. A total of 127 models were fit for each strata and shark species using Maximum Likelihood (ML) estimation using the *‘mgcv’* package in R (R Core Team 2018, Wood 2004, 2011). All models nested within the full model were considered and the best fit model was selected using AIC. The most parsimonious model with a  $\Delta$AIC ˂ 2 was selected as the final model. 



## Results ##




## Discussion ##



## References ##

Kim, Y.I., Gu, C. (2004) Smoothing spline Gaussian regression: more scalable computation via efficient approximation. Journal of the Royal Statistical Society, Series B 66, 337-356.

R Core Team (2018). R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria. URL https://www.R-project.org/                                								(R version 3.5.0)

Wood, S.N. (2011) Fast stable restricted maximum likelihood and marginal likelihood estimation of semiparametric generalized linear models. Journal of the Royal Statistical Society (B) 73(1):3-36

Wood, S.N. (2004) Stable and efficient multiple smoothing parameter estimation for generalized additive models. Journal of the American Statistical Association. 99:673-686.


## Tables ##

### Table 1

**Note:** *Simplify Table 1 to be only the best models for each species. Or maybe top few models for each species*

#### (a) Blacknose
```{r, cache=TRUE}
bn_gam_select_1$results


```

Number of models `r nrow(bn_gam_select_1$results)`

 user  system elapsed 
 
 4.43    3.02 1239.10 $\approx$ 20 min

#### (b) Blacktip
```{r, cache=TRUE}
bt_gam_select$results


```

Number of models `r nrow(bt_gam_select$results)`

 user  system elapsed 
 
 3.72    2.60 1291.12 $\approx$ 21 min

#### (c) Bull
```{r, cache=TRUE}
bu_gam_select$results


```


Number of models `r nrow(bu_gam_select$results)`

 user  system elapsed 
 
 1.94    2.45 1161.04 $\approx$ 19 min

#### (d) Sandbar
```{r, cache=TRUE}
sb_gam_select$results

```


Number of models `r nrow(sb_gam_select$results)`

 user  system elapsed 
 
 1.77    2.87  746.13 $\approx$ 12 min

#### (e) Sharpnose
```{r, cache=TRUE}
sn_gam_select_2$results


```

Number of models `r nrow(sn_gam_select_2$results)`

 user  system elapsed 
 
 3.92    5.59 4214.18 $\approx$ 1 hr 10 min

#### (f) Silky
```{r, cache=TRUE}
si_gam_select$results


```

Number of models `r nrow(si_gam_select$results)`


#### (g) Spinner 

```{r, cache=TRUE}
sp_gam_select$results


```

Number of models `r nrow(sp_gam_select$results)`


#### (h) Tiger
```{r, cache=TRUE}
ti_gam_select$results


```

Number of models `r nrow(ti_gam_select$results)`








## Figures ##

**Note:** *These are just placeholders I will do a nicer ggplot later* 

### Figure 1


```{r Figue 1, echo=FALSE, fig.align = "center"}
plot(STARTLAT~STARTLON,
     data = sharpnose)
```


### Figure 2

```{r Descriptive Statistics, echo=FALSE, include=FALSE}
(bn.stat <- my_summary(blacknose))

(sp.stat <- my_summary(spinner))

(si.stat <- my_summary(silky))

(bu.stat <- my_summary(bull))

(bt.stat <- my_summary(blacktip))

(sb.stat <- my_summary(sandbar))

(ti.stat <- my_summary(tiger))

(sn.stat <- my_summary(sharpnose))

```

```{r Figure 2 Number of Sites Sampled, echo=FALSE, fig.align = "center"}

par(mfrow = c(1,1))

mids <- barplot(bn.stat$annual$n_Sites_Sampled, 
                xlab="", ylim = c(0,300),
                main = "Number of Sites Sampled")
axis(1, at = mids,
     labels = bn.stat$annual$Year,
     las=2)
```

