---
title: "Best GAM"
author: "Alex Benecke"
date: "July 30, 2018"
output:   
  html_document:
    df_print: paged
    toc: true
    toc_float: true
    toc_depth: 5
    fig_width: 10
    fig_height: 10
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

```{r Load Packages, include=FALSE, eval=TRUE}

### Load Packages
library(FSA)
library(tidyverse)
library(dplyr)
library(magrittr)
library(scales)
library(mgcv)
library(sciplot)

### Load My Functions
source("5_functions/dropbox_fn.R") # For interacting with dropbox
proj = "shark" # Specify project where data is stored 

source("5_functions/load_data.R")
```

```{r Load Data, echo=FALSE, include=FALSE, eval=FALSE}
#### Load Combined Data ####
eff3 <- read_csv_fn( "data/clean-data/CPUE3.csv", proj , na.strings = c(NA, ""))
str(eff3)

#### Load Structured Data ####
  ## Strata 1
strat1_Adult <- load_data(data = eff3[eff3$maturity == "A",], strata = 1)
strat1_Juvenile <- load_data(data = eff3[eff3$maturity == "J",], strata = 1)
  ## Strata 2
strat2_Adult <- load_data(data = eff3[eff3$maturity == "A",], strata = 2)
strat2_Juvenile <- load_data(data = eff3[eff3$maturity == "J",], strata = 2)
```


# Models Fit #

## Strata 1

| Species   | Female Adult | Female Juvenile | Male Adult | Male Juvenile |
|:---------:|:------------:|:---------------:|:----------:|:-------------:|
| Blacknose |  OK          |  OK             |  OK        |  OK           |
| Blacktip  |  OK          |  OK             |  OK        |  OK           |
| Bull      |  OK          |  OK             |  OK        |  OK           |
| Sandbar   |  OK          |  OK             |  OK        |  OK           |
| Sharpnose |  OK          |  OK             |  OK        |  OK           |
| Spinner   |  OK          |  OK             |  OK        |  OK           |
| Tiger     |  OK          |  OK             |  OK        |  OK           |

## Strata 2

| Species   | Female Adult | Female Juvenile | Male Adult | Male Juvenile |
|:---------:|:------------:|:---------------:|:----------:|:-------------:|
| Blacknose |  OK          |  OK             |  OK        |  OK           |
| Blacktip  |  OK          |  OK             |  OK        |  OK           |
| Bull      |  Failed      |  Failed         |  Failed    |  Failed       |
| Sandbar   |  OK          |  OK             |  Failed    |  OK           |
| Sharpnose |  OK          |  OK             |  OK        |  OK           |
| Spinner   |  Failed      |  OK             |  Failed    |  OK           |
| Tiger     |  Failed      |  OK             |  Failed    |  OK           |


The **Primary Species** I will Use are going to be **Blacknose**, **Blacktip**, and **Sharpnose** because they were fit for all levels of sex and maturity in both strata


# Strata 1 #
## Female ##

### Adult ###
```{r Load S1_FA, eval=FALSE}
#### Strata 1 ####
  ## Female Adult
filenames_s1_FA <- list.files("output/output_GAM/strat1/Female_Adult", pattern="*.rda", full.names=TRUE)

for( i in 1:length( filenames_s1_FA ) ){ load( file = filenames_s1_FA[ i ] ) }

rm( filenames_s1_FA )
```
```{r, echo=FALSE, eval=TRUE}
load("output/output_GAM/strat1/Female_Adult/bn_s1_FA.rda")
load("output/output_GAM/strat1/Female_Adult/bt_s1_FA.rda")
load("output/output_GAM/strat1/Female_Adult/sn_s1_FA.rda")
```


#### Blacknose
```{r, eval=TRUE}
bn_s1_FA$results ### top 3 dAIC < 4

bn.top_s1_FA <- bn_s1_FA$model_fits$Lat_Lon_Root_Dep_Temp_Turb_Oxy_Sal

summary(bn.top_s1_FA)
```

  **turbbotm** not significant and edf = 1.
  **salbotm** p-value suggests significance but edf is approximatly equal to 1.

```{r, eval=TRUE}
par(mfrow = c(2,2))
gam.check(bn.top_s1_FA)
```

  Plot of Residuals against linear predictor looks strange to me. The histogram of the residuals has a gap in it.
  
  k` looks good for all variables.
  
```{r, eval=TRUE}
par(mfrow = c(3,2))
#par(mfrow = c(1,1))

for(i in 2:7){
  
  plot(bn.top_s1_FA,
       select = i)
  abline(h = 0, col = "red", lty = 2)
  
}
```
**root startdepth**, **turbbotm**,  are zero throughout their entire range

**tempbotm**, **oxybotm** maybe zero throughout it's entire range.

**salbotm** looks linear and increasing very slightly.

  I want to look at another model without the **turbbotm** smooth.
```{r, eval=TRUE}
bn.2_s1_FA <- bn_s1_FA$model_fits$Lat_Lon_Root_Dep_Temp_Oxy_Sal

summary(bn.2_s1_FA)
```
  **salbotm** edf is still near 1 but i think this is ok.
  
```{r, eval=TRUE}
par(mfrow = c(2,2))
gam.check(bn.2_s1_FA)
```

  k` looks good for all variables
```{r, eval=TRUE}

par(mfrow = c(2,2))
#par(mfrow = c(1,1))

for(i in 2:5){
  
  plot(bn.2_s1_FA,
       select = i)
  abline(h = 0, col = "red", lty = 2)
  
}

par(mfrow = c(1,1))
  plot(bn.2_s1_FA,
       select = 6)
```
**root startdepth** is zero throughout it's entire range but is close near 2.5 and 3.5. 
**tempbotm**  zero throughouts it's entire range but it is very hard to tell near 18-19 or 27.
**Oxybotm** Zero below 8 Positive 8-10, and zero above 10 (but wide CI).
**salbotm** again appears linear and negative to left increasing to right (negative below approx. 32 and Pos above approx. 37.5 Zero between).


For good measure I want to look at the 2nd ranged model
```{r, eval=TRUE}
bn.top2_s1_FA <- bn_s1_FA$model_fits$Lat_Lon_Root_Dep_Temp_Turb_Sal_Dis

summary(bn.top2_s1_FA)
```

edf of both **turbbotm** and **salbotm** is 1 and p-value is not significant.

```{r, eval=TRUE}
par(mfrow = c(2,2))
gam.check(bn.top2_s1_FA)
```

```{r, eval=TRUE}
par(mfrow = c(2,3))
#par(mfrow = c(1,1))

for(i in 2:6){
  
  plot(bn.top2_s1_FA,
       select = i)
  abline(h = 0, col = "red", lty = 2)
  
}

par(mfrow = c(1,1))

plot(bn.top2_s1_FA,
       select = 2)
abline(h = 0, col = "red", lty = 2)

plot(bn.top2_s1_FA,
       select = 3,
     ylim = c(-10,10))
abline(h = 0, col = "red", lty = 2)

plot(bn.top2_s1_FA,
       select = 4,
     ylim = c(-2,2))
abline(h = 0, col = "red", lty = 2)

plot(bn.top2_s1_FA,
       select = 5,
     ylim = c(-5,5))
abline(h = 0, col = "red", lty = 2)

plot(bn.top2_s1_FA,
       select = 6,
     ylim = c(-5,5))
abline(h = 0, col = "red", lty = 2)

plot(bn.top2_s1_FA,
       select = 7)
abline(h = 0, col = "red", lty = 2)

```
**root startdepth** is zero thoroughout it's entire range.

**tempbotm** is positive approx. between 24 and 26 zero everywhere else.

**turbbotm** is zero everywhere

**salbotm** is zero everywhere

**Dis.to.SHORE** is zero everywhere





```{r, eval=TRUE}
bn.top3_s1_FA <- bn_s1_FA$model_fits$Lat_Lon_Root_Dep_Temp_Turb_Oxy

summary(bn.top3_s1_FA)
gam.check(bn.top3_s1_FA)
plot(bn.top3_s1_FA,pages = 1)

bn.top19_s1_FA <- bn_s1_FA$model_fits$Lat_Lon_Root_Dep_Temp_Oxy_Sal_Dis

summary(bn.top19_s1_FA)
gam.check(bn.top19_s1_FA)
#par(mfrow = c(1,1))
plot(bn.top19_s1_FA,pages = 1)

plot(bn.top19_s1_FA,
     select = 6)
abline(h = 0, col = "red", lty = 2)
```

  I think the best model to use is the one with the same structure as the top model but without the **turbbotm** smooth.

```{r}
bn_s1_FA_best <- bn_s1_FA$model_fits$Lat_Lon_Root_Dep_Temp_Oxy_Sal

#-saves_8/22/18-#save(bn_s1_FA_best, file = "output/output_GAM/best_strat1/Female_Adult/bn_s1_FA_best.rda")

```



#### Blacktip
```{r, eval=TRUE}
bt_s1_FA$results[c(1:20), c(1:4,7)]

bt.top_s1_FA <- bt_s1_FA$model_fits$Lat_Lon_Root_Dep_Temp_Turb_Oxy_Sal_Dis

summary(bt.top_s1_FA)
```

```{r, eval=TRUE}
par(mfrow = c(2,2))
gam.check(bt.top_s1_FA)
```

**depth**, **Turb**, **Sal** edf all = 1.

```{r, eval=TRUE}
plot(bt.top_s1_FA,
     pages = 1)


par(mfrow = c(2,3))

for(i in 2:7){
  
  plot(bt.top_s1_FA,
     select = i)
  abline(h = 0, col = "red", lty = 3)
  
}

```
**startdepth** is zero

**turbbotm** looks linear decreasing to zero near 75ish, negative past 80.

**Salbotm** is zero but if CI were closer would be linear increasing.

** Dis.to.SHORE** is zero

```{r, eval=TRUE}

bt.2_s1_FA <- bt_s1_FA$model_fits$Lat_Lon_Temp_Turb_Oxy

summary(bt.2_s1_FA)

par(mfrow = c(2,2))
gam.check(bt.2_s1_FA)


par(mfrow = c(2,2))

for(i in 2:5){
  
  plot(bt.2_s1_FA,
     select = i)
  abline(h = 0, col = "red", lty = 3)
  
}
```

```{r, eval=TRUE}
anova.gam(bt.top_s1_FA, bt.2_s1_FA, test = "Chisq") ## No difference

AIC(bt.top_s1_FA, bt.2_s1_FA)
```

```{r}
bt_s1_FA_best <- bt_s1_FA$model_fits$Lat_Lon_Temp_Turb_Oxy

#-saves_8/23/18-#save(bt_s1_FA_best, file = "output/output_GAM/best_strat1/Female_Adult/bt_s1_FA_best.rda")

```


#### Bull
```{r}
bu_s1_FA$results[c(1:20), c(1:4,7)]

bu.top_s1_FA <- bu_s1_FA$model_fits$Lat_Lon_Root_Dep_Dis

summary(bu.top_s1_FA)
```


#### Sandbar
```{r}
sb_s1_FA$results[c(1:20), c(1:4,7)]

sb.top_s1_FA <- sb_s1_FA$model_fits$Lat_Lon_Root_Dep_Temp_Turb_Sal_Dis

summary(sb.top_s1_FA)
```


#### Sharpnose
```{r, eval=TRUE}
sn_s1_FA$results[c(1:20), c(1:4,7)]

sn.top_s1_FA <- sn_s1_FA$model_fits$Lat_Lon_Root_Dep_Temp_Turb_Oxy_Dis

summary(sn.top_s1_FA)
```
**oxybotm** edf = 1

```{r, eval=TRUE}
par(mfrow = c(2,2))

gam.check(sn.top_s1_FA)
```


```{r, eval=TRUE}
par(mfrow = c(2,3))
par(mfrow = c(1,1))

for(i in 2:7 ){
  
  plot( sn.top_s1_FA,
       select = i)
  abline(h = 0, col = "red", lty = 3)

  }
```


#### Spinner
```{r}
sp_s1_FA$results[c(1:20), c(1:4,7)]

sp.top_s1_FA <- sp_s1_FA$model_fits$Lat_Lon_Root_Dep_Temp_Turb_Oxy_Dis

summary(sp.top_s1_FA)
```


#### Tiger
```{r}
ti_s1_FA$results[c(1:20), c(1:4,7)] # top 8 dAIC < 4

ti.top_s1_FA <- ti_s1_FA$model_fits$Lat_Lon

summary(ti.top_s1_FA)
```


### Juvenile ###
```{r Load S1_FJ, eval=FALSE}
#### Strata 1 ####
  ## Female Juvenile
filenames_s1_FJ <- list.files("output/output_GAM/strat1/Female_Juvenile", pattern="*.rda", full.names=TRUE)

for( i in 1:length( filenames_s1_FJ ) ){ load( file = filenames_s1_FJ[ i ] ) }

rm( filenames_s1_FJ )
```
```{r, echo=FALSE, eval=TRUE}
load("output/output_GAM/strat1/Female_Juvenile/bn_s1_FJ.rda")
load("output/output_GAM/strat1/Female_Juvenile/bt_s1_FJ.rda")
load("output/output_GAM/strat1/Female_Juvenile/sn_s1_FJ.rda")
```

#### Blacknose
```{r, eval=TRUE}
bn_s1_FJ$results[c(1:20), c(1:4,7)]

bn.top_s1_FJ <- bn_s1_FJ$model_fits$Lat_Lon_Root_Dep_Temp_Turb_Oxy_Sal

summary(bn.top_s1_FJ)
```


```{r, eval=TRUE}
par(mfrow = c(2,2))

gam.check(bn.top_s1_FJ)
```


```{r, eval=TRUE}
par(mfrow = c(1,1))

for(i in 2:7 ){
  
  plot( bn.top_s1_FJ,
       select = i)
  abline(h = 0, col = "red", lty = 3)

  }
```




#### Blacktip
```{r, eval=TRUE}
bt_s1_FJ$results[c(1:20), c(1:4,7)]

bt.top_s1_FJ <- bt_s1_FJ$model_fits$Lat_Lon_Root_Dep_Temp_Turb_Oxy_Dis

summary(bt.top_s1_FJ)
```


```{r, eval=TRUE}
par(mfrow = c(2,2))

gam.check(bt.top_s1_FJ)
```


```{r, eval=TRUE}
par(mfrow = c(1,1))

for(i in 2:7 ){
  
  plot( bt.top_s1_FJ,
       select = i)
  abline(h = 0, col = "red", lty = 3)

  }
```




#### Bull
```{r}
bu_s1_FJ$results[c(1:20), c(1:4,7)]

bu.top_s1_FJ <- bu_s1_FJ$model_fits$Lat_Lon_Root_Dep_Turb

summary(bu.top_s1_FJ)
```


#### Sandbar
```{r}
sb_s1_FJ$results[c(1:20), c(1:4,7)]

sb.top_s1_FJ <- sb_s1_FJ$model_fits$Lat_Lon_Root_Dep_Temp_Turb

summary(sb.top_s1_FJ)
```


#### Sharpnose
```{r, eval=TRUE}
sn_s1_FJ$results[c(1:20), c(1:4,7)]

sn.top_s1_FJ <- sn_s1_FJ$model_fits$Lat_Lon_Root_Dep_Temp_Turb_Oxy

summary(sn.top_s1_FJ)
```


```{r, eval=TRUE}
par(mfrow = c(2,2))

gam.check(sn.top_s1_FJ)
```


```{r, eval=TRUE}
par(mfrow = c(1,1))

for(i in 2:6 ){
  
  plot( sn.top_s1_FJ,
       select = i)
  abline(h = 0, col = "red", lty = 3)

  }
```




#### Spinner
```{r}
sp_s1_FJ$results[c(1:20), c(1:4,7)]

sp.top_s1_FJ <- sp_s1_FJ$model_fits$Lat_Lon_Root_Dep_Temp_Turb_Oxy_Sal_Dis

summary(sp.top_s1_FJ)
```


#### Tiger
```{r}
ti_s1_FJ$results[c(1:20), c(1:4,7)]

ti.top_s1_FJ <- ti_s1_FJ$model_fits$Lat_Lon_Root_Dep_Turb_Sal_Dis

summary(ti.top_s1_FJ)
```



## Male ##
### Adult ###
```{r Load S1_MA, eval=FALSE}
#### Strata 1 ####
  ## Male Adult
filenames_s1_MA <- list.files("output/output_GAM/strat1/Male_Adult", pattern="*.rda", full.names=TRUE)

for( i in 1:length( filenames_s1_MA ) ){ load( file = filenames_s1_MA[ i ] ) }

rm( filenames_s1_MA )
```
```{r, echo=FALSE, eval=TRUE}
load("output/output_GAM/strat1/Male_Adult/bn_s1_MA.rda")
load("output/output_GAM/strat1/Male_Adult/bt_s1_MA.rda")
load("output/output_GAM/strat1/Male_Adult/sn_s1_MA.rda")
```

#### Blacknose
```{r, eval=TRUE}
bn_s1_MA$results[c(1:20), c(1:4,7)]

bn.top_s1_MA <- bn_s1_MA$model_fits$Lat_Lon_Root_Dep_Temp_Turb_Oxy_Sal_Dis

summary(bn.top_s1_MA)
```


```{r, eval=TRUE}
par(mfrow = c(2,2))

gam.check(bn.top_s1_MA)
```


```{r, eval=TRUE}
par(mfrow = c(1,1))

for(i in 2:8 ){
  
  plot( bn.top_s1_MA,
       select = i)
  abline(h = 0, col = "red", lty = 3)

  }
```




#### Blacktip
```{r, eval=TRUE}
bt_s1_MA$results[c(1:20), c(1:4,7)]

bt.top_s1_MA <- bt_s1_MA$model_fits$Lat_Lon_Root_Dep_Temp_Turb_Oxy_Dis

summary(bt.top_s1_MA)
```


```{r, eval=TRUE}
par(mfrow = c(2,2))

gam.check(bt.top_s1_MA)
```


```{r, eval=TRUE}
par(mfrow = c(1,1))

for(i in 2:7 ){
  
  plot( bt.top_s1_MA,
       select = i)
  abline(h = 0, col = "red", lty = 3)

  }
```




#### Bull
```{r}
bu_s1_MA$results[c(1:20), c(1:4,7)]

bu.top_s1_MA <- bu_s1_MA$model_fits$Lat_Lon_Root_Dep_Turb_Dis

summary(bu.top_s1_MA)
```
WOW!!! lol only 1 male Adult Bull shark...

#### Sandbar
```{r}
sb_s1_MA$results[c(1:20), c(1:4,7)]

sb.top_s1_MA <- sb_s1_MA$model_fits$Lat_Lon_Root_Dep_Temp_Turb_Oxy_Dis

summary(sb.top_s1_MA)
```


#### Sharpnose
```{r, eval=TRUE}
sn_s1_MA$results[c(1:20), c(1:4,7)]

sn.top_s1_MA <- sn_s1_MA$model_fits$Lat_Lon_Root_Dep_Temp_Turb_Oxy_Sal

summary(sn.top_s1_MA)
```


```{r, eval=TRUE}
par(mfrow = c(2,2))

gam.check(sn.top_s1_MA)
```


```{r, eval=TRUE}
par(mfrow = c(1,1))

for(i in 2:7 ){
  
  plot( sn.top_s1_MA,
       select = i)
  abline(h = 0, col = "red", lty = 3)

  }
```




#### Spinner
```{r}
sp_s1_MA$results[c(1:20), c(1:4,7)]

sp.top_s1_MA <- sp_s1_MA$model_fits$Lat_Lon_Root_Dep_Temp_Turb_Oxy_Sal_Dis

summary(sp.top_s1_MA)
```
WOW!!! Unlikely

#### Tiger
```{r}
ti_s1_MA$results[c(1:20), c(1:4,7)]

ti.top_s1_MA <- ti_s1_MA$model_fits$Lat_Lon_Dis

summary(ti.top_s1_MA)
```
WOW!!! Unlikely


### Juvenile ###
```{r Load S1_MJ, eval=FALSE}
#### Strata 1 ####
  ## Male Juvenile
filenames_s1_MJ <- list.files("output/output_GAM/strat1/Male_Juvenile", pattern="*.rda", full.names=TRUE)

for( i in 1:length( filenames_s1_MJ ) ){ load( file = filenames_s1_MJ[ i ] ) }

rm( filenames_s1_MJ )
```
```{r,echo=FALSE, eval=TRUE}
load("output/output_GAM/strat1/Male_Juvenile/bn_s1_MJ.rda")
load("output/output_GAM/strat1/Male_Juvenile/bt_s1_MJ.rda")
load("output/output_GAM/strat1/Male_Juvenile/sn_s1_MJ.rda")
```

#### Blacknose
```{r, eval=TRUE}
bn_s1_MJ$results[c(1:20), c(1:4,7)]

bn.top_s1_MJ <- bn_s1_MJ$model_fits$Lat_Lon_Root_Dep_Temp_Turb_Oxy_Dis

summary(bn.top_s1_MJ)
```


```{r, eval=TRUE}
par(mfrow = c(2,2))

gam.check(bn.top_s1_MJ)
```


```{r, eval=TRUE}
par(mfrow = c(1,1))

for(i in 2:7 ){
  
  plot( bn.top_s1_MJ,
       select = i)
  abline(h = 0, col = "red", lty = 3)

  }
```




#### Blacktip
```{r, eval=TRUE}
bt_s1_MJ$results[c(1:20), c(1:4,7)]

bt.top_s1_MJ <- bt_s1_MJ$model_fits$Lat_Lon_Root_Dep_Temp_Turb_Oxy_Sal_Dis

summary(bt.top_s1_MJ)
```


```{r, eval=TRUE}
par(mfrow = c(2,2))

gam.check(bt.top_s1_MJ)
```


```{r, eval=TRUE}
par(mfrow = c(1,1))

for(i in 2:8 ){
  
  plot( bt.top_s1_MJ,
       select = i)
  abline(h = 0, col = "red", lty = 3)

  }
```




#### Bull
```{r}
bu_s1_MJ$results[c(1:20), c(1:4,7)]

bu.top_s1_MJ <- bu_s1_MJ$model_fits$Lat_Lon_Root_Dep_Turb_Oxy_Sal

summary(bu.top_s1_MJ)
```


#### Sandbar
```{r}
sb_s1_MJ$results[c(1:20), c(1:4,7)] ### Top 7 dAIC < 4
### Lat_Lon in Model 4

sb.top_s1_MJ <- sb_s1_MJ$model_fits$Root_Dep_Temp_Turb_Oxy_Sal_Dis

summary(sb.top_s1_MJ)


sb.top4_s1_MJ <- sb_s1_MJ$model_fits$Lat_Lon_Root_Dep_Temp_Turb_Oxy_Sal

summary(sb.top4_s1_MJ)
```


#### Sharpnose
```{r, eval=TRUE}
sn_s1_MJ$results[c(1:20), c(1:4,7)]

sn.top_s1_MJ <- sn_s1_MJ$model_fits$Lat_Lon_Root_Dep_Temp_Turb_Oxy_Sal

summary(sn.top_s1_MJ)
```


```{r, eval=TRUE}
par(mfrow = c(2,2))

gam.check(sn.top_s1_MJ)
```


```{r, eval=TRUE}
par(mfrow = c(1,1))

for(i in 2:7 ){
  
  plot( sn.top_s1_MJ,
       select = i)
  abline(h = 0, col = "red", lty = 3)

  }
```




#### Spinner
```{r}
sp_s1_MJ$results[c(1:20), c(1:4,7)]

sp.top_s1_MJ <- sp_s1_MJ$model_fits$Lat_Lon_Root_Dep_Temp_Turb_Oxy_Sal_Dis

summary(sp.top_s1_MJ)
```


#### Tiger
```{r}
ti_s1_MJ$results[c(1:20), c(1:4,7)] ### Top 21 dAIC < 4

ti.top_s1_MJ <- ti_s1_MJ$model_fits$Lat_Lon_Root_Dep_Turb

summary(ti.top_s1_MJ)
```


# Strata 2
## Female ##
### Adult ###
```{r Load S2_FA, eval=FALSE}
#### Strata 2 ####
  ## Female Adult
filenames_s2_FA <- list.files("output/output_GAM/strat2/Female_Adult", pattern="*.rda", full.names=TRUE)

for( i in 1:length( filenames_s2_FA ) ){ load( file = filenames_s2_FA[ i ] ) }

rm( filenames_s2_FA )
```
```{r,echo=FALSE, eval=TRUE}
load("output/output_GAM/strat2/Female_Adult/bn_s2_FA.rda")
load("output/output_GAM/strat2/Female_Adult/bt_s2_FA.rda")
load("output/output_GAM/strat2/Female_Adult/sn_s2_FA.rda")
```

#### Blacknose
```{r, eval=TRUE}
bn_s2_FA$results[c(1:20), c(1:4,7)]

bn.top.s2_FA <- bn_s2_FA$model_fits$Lat_Lon_Turb_Dis

summary(bn.top.s2_FA)
```


```{r, eval=TRUE}
par(mfrow = c(2,2))

gam.check(bn.top.s2_FA)
```


```{r, eval=TRUE}
par(mfrow = c(1,1))

for(i in 2:4 ){
  
  plot( bn.top.s2_FA,
       select = i)
  abline(h = 0, col = "red", lty = 3)

  }
```




#### Blacktip
```{r, eval=TRUE}
bt_s2_FA$results

bt.top.s2_FA <- bt_s2_FA$model_fits$Lat_Lon_Turb_Oxy_Sal_Dis_Bottm

summary(bt.top.s2_FA)
```


```{r, eval=TRUE}
par(mfrow = c(2,2))

gam.check(bt.top.s2_FA)
```


```{r, eval=TRUE}
par(mfrow = c(1,1))

for(i in 2:7 ){
  
  plot( bt.top.s2_FA,
       select = i)
  abline(h = 0, col = "red", lty = 3)

  }
```




#### Bull

*FAILED to fit model*

```{r, eval=FALSE}
bu_s2_FA$results

bu.top.s2_FA <- bu_s2_FA$model_fits

summary(bu.top.s2_FA)
```


#### Sandbar
```{r}
sb_s2_FA$results

sb.top.s2_FA <- sb_s2_FA$model_fits$Lat_Lon_Temp_Turb_Dis

summary(sb.top.s2_FA)
```


#### Sharpnose
```{r, eval=TRUE}
sn_s2_FA$results

sn.top.s2_FA <- sn_s2_FA$model_fits$Lat_Lon_Temp_Turb_Sal

summary(sn.top.s2_FA)
```


```{r, eval=TRUE}
par(mfrow = c(2,2))

gam.check(sn.top.s2_FA)
```


```{r, eval=TRUE}
par(mfrow = c(1,1))

for(i in 2:5 ){
  
  plot( sn.top.s2_FA,
       select = i)
  abline(h = 0, col = "red", lty = 3)

  }
```




#### Spinner

*Failed to Fit*

```{r, eval=FALSE}
sp_s2_FA$results

sp.top.s2_FA <- sp_s2_FA$model_fits

summary(sp.top.s2_FA)
```


#### Tiger


*Failed to Fit*

```{r, eval=FALSE}
ti_s2_FA$results

ti.top.s2_FA <- ti_s2_FA$model_fits

summary(ti.top.s2_FA)
```





### Juvenile ###
```{r Load S2_FJ, eval=FALSE}
#### Strata 2 ####
  ## Female Juvenile
filenames_s2_FJ <- list.files("output/output_GAM/strat2/Female_Juvenile", pattern="*.rda", full.names=TRUE)

for( i in 1:length( filenames_s2_FJ ) ){ load( file = filenames_s2_FJ[ i ] ) }

rm( filenames_s2_FJ )
```

```{r,echo=FALSE, eval=TRUE}
load("output/output_GAM/strat2/Female_Juvenile/bn_s2_FJ.rda")
load("output/output_GAM/strat2/Female_Juvenile/bt_s2_FJ.rda")
load("output/output_GAM/strat2/Female_Juvenile/sn_s2_FJ.rda")
```

#### Blacknose
```{r, eval=TRUE}
bn_s2_FJ$results

bn.top.s2_FJ <- bn_s2_FJ$model_fits$Lat_Lon_Temp_Turb_Oxy_Sal_Bottm

summary(bn.top.s2_FJ)
```


```{r, eval=TRUE}
par(mfrow = c(2,2))

gam.check(bn.top.s2_FJ)
```


```{r, eval=TRUE}
par(mfrow = c(1,1))

for(i in 2:7 ){
  
  plot( bn.top.s2_FJ,
       select = i)
  abline(h = 0, col = "red", lty = 3)

  }
```




#### Blacktip
```{r, eval=TRUE}
bt_s2_FJ$results

bt.top.s2_FJ <- bt_s2_FJ$model_fits$Lat_Lon_Root_Dep_Temp_Turb_Oxy_Sal

summary(bt.top.s2_FJ)
```


```{r, eval=TRUE}
par(mfrow = c(2,2))

gam.check(bt.top.s2_FJ)
```


```{r, eval=TRUE}
par(mfrow = c(1,1))

for(i in 2:7 ){
  
  plot( bt.top.s2_FJ,
       select = i)
  abline(h = 0, col = "red", lty = 3)

  }
```




#### Bull

*FAILED To Fit*

```{r, eval=FALSE}
bu_s2_FJ$results

bu.top.s2_FJ <- bu_s2_FJ$model_fits

summary(bu.top.s2_FJ)
```


#### Sandbar
```{r}
sb_s2_FJ$results

sb.top.s2_FJ <- sb_s2_FJ$model_fits$Lat_Lon_Turb_Dis

summary(sb.top.s2_FJ)
```


#### Sharpnose
```{r, eval=TRUE}
sn_s2_FJ$results

sn.top.s2_FJ <- sn_s2_FJ$model_fits$Lat_Lon_Temp_Turb_Dis_Bottm

summary(sn.top.s2_FJ)
```


```{r, eval=TRUE}
par(mfrow = c(2,2))

gam.check(sn.top.s2_FJ)
```


```{r, eval=TRUE}
par(mfrow = c(1,1))

for(i in 2:6 ){
  
  plot( sn.top.s2_FJ,
       select = i)
  abline(h = 0, col = "red", lty = 3)

  }
```




#### Spinner
```{r}
sp_s2_FJ$results

sp.top.s2_FJ <- sp_s2_FJ$model_fits$Lat_Lon_Temp_Turb_Sal_Dis

summary(sp.top.s2_FJ)
```


#### Tiger
```{r}
ti_s2_FJ$results

ti.top.s2_FJ <- ti_s2_FJ$model_fits$Lat_Lon_Temp_Turb_Dis_Bottm

summary(ti.top.s2_FJ)
```



## Male ##
### Adult ###
```{r Load S2_MA, eval=FALSE}
#### Strata 2 ####
  ## Male Adult
filenames_s2_MA <- list.files("output/output_GAM/strat2/Male_Adult", pattern="*.rda", full.names=TRUE)

for( i in 1:length( filenames_s2_MA ) ){ load( file = filenames_s2_MA[ i ] ) }

rm( filenames_s2_MA )
```
```{r, eval=TRUE}
load("output/output_GAM/strat2/Male_Adult/bn_s2_MA.rda")
load("output/output_GAM/strat2/Male_Adult/bt_s2_MA.rda")
load("output/output_GAM/strat2/Male_Adult/sn_s2_MA.rda")
```

#### Blacknose
```{r, eval=TRUE}
bn_s2_MA$results

bn.top.s2_MA <- bn_s2_MA$model_fits$Lat_Lon_Temp_Turb_Oxy_Sal_Bottm

summary(bn.top.s2_MA)
```


```{r, eval=TRUE}
par(mfrow = c(2,2))

gam.check(bn.top.s2_MA)
```


```{r, eval=TRUE}
par(mfrow = c(1,1))

for(i in 2:7 ){
  
  plot( bn.top.s2_MA,
       select = i)
  abline(h = 0, col = "red", lty = 3)

  }
```




#### Blacktip
```{r, eval=TRUE}
bt_s2_MA$results

bt.top.s2_MA <- bt_s2_MA$model_fits$Lat_Lon_Root_Dep_Temp_Turb_Sal_Dis

summary(bt.top.s2_MA)
```


```{r, eval=TRUE}
par(mfrow = c(2,2))

gam.check(bt.top.s2_MA)
```


```{r, eval=TRUE}
par(mfrow = c(1,1))

for(i in 2:7 ){
  
  plot( bt.top.s2_MA,
       select = i)
  abline(h = 0, col = "red", lty = 3)

  }
```




#### Bull

*FAILED To Fit*

```{r, eval=FALSE}
bu_s2_MA$results

bu.top.s2_MA <- bu_s2_MA$model_fits

summary(bu.top.s2_MA)
```


#### Sandbar

*FAILED To Fit*

```{r, eval=FALSE}
sb_s2_MA$results

sb.top.s2_MA <- sb_s2_MA$model_fits

summary(sb.top.s2_MA)
```


#### Sharpnose
```{r, eval=TRUE}
sn_s2_MA$results

sn.top.s2_MA <- sn_s2_MA$model_fits$Lat_Lon_Root_Dep_Turb_Oxy_Sal_Dis_Bottm

summary(sn.top.s2_MA)
```


```{r, eval=TRUE}
par(mfrow = c(2,2))

gam.check(sn.top.s2_MA)
```


```{r, eval=TRUE}
par(mfrow = c(1,1))

for(i in 2:8 ){
  
  plot( sn.top.s2_MA,
       select = i)
  abline(h = 0, col = "red", lty = 3)

  }
```




#### Spinner

*FAILED To Fit*

```{r, eval=FALSE}
sp_s2_MA$results

sp.top.s2_MA <- sp_s2_MA$model_fits

summary(sp.top.s2_MA)
```


#### Tiger

*FAILED To Fit*

```{r, eval=FALSE}
ti_s2_MA$results

ti.top.s2_MA <- ti_s2_MA$model_fits

summary(ti.top.s2_MA)
```


### Juvenile ###
```{r Load S2_MJ, eval=FALSE}
#### Strata 2 ####
  ## Male Juvenile
filenames_s2_MJ <- list.files("output/output_GAM/strat2/Male_Juvenile", pattern="*.rda", full.names=TRUE)

for( i in 1:length( filenames_s2_MJ ) ){ load( file = filenames_s2_MJ[ i ] ) }

rm( filenames_s2_MJ )
```
```{r,echo=FALSE, eval=TRUE}
load("output/output_GAM/strat2/Male_Juvenile/bn_s2_MJ.rda")
load("output/output_GAM/strat2/Male_Juvenile/bt_s2_MJ.rda")
load("output/output_GAM/strat2/Male_Juvenile/sn_s2_MJ.rda")
```

#### Blacknose
```{r, eval=TRUE}
bn_s2_MJ$results

bn.top.s2_MJ <- bn_s2_MJ$model_fits$Lat_Lon_Root_Dep_Temp_Turb_Oxy_Sal_Bottyp

summary(bn.top.s2_MJ)
```


```{r, eval=TRUE}
par(mfrow = c(2,2))

gam.check(bn.top.s2_MJ)
```


```{r, eval=TRUE}
par(mfrow = c(1,1))

for(i in 2:8 ){
  
  plot( bn.top.s2_MJ,
       select = i)
  abline(h = 0, col = "red", lty = 3)

  }
```




#### Blacktip
```{r, eval=TRUE}
bt_s2_MJ$results

bt.top.s2_MJ <- bt_s2_MJ$model_fits$Lat_Lon_Root_Dep_Turb_Oxy_Sal

summary(bt.top.s2_MJ)
```


```{r, eval=TRUE}
par(mfrow = c(2,2))

gam.check(bt.top.s2_MJ)
```


```{r, eval=TRUE}
par(mfrow = c(1,1))

for(i in 2:5 ){
  
  plot( bt.top.s2_MJ,
       select = i)
  abline(h = 0, col = "red", lty = 3)

  }
```




#### Bull

*Failed to fit*

```{r, eval=FALSE}
bu_s2_MJ$results

bu.top.s2_MJ <- bu_s2_MJ$model_fits

summary(bu.top.s2_MJ)
```


#### Sandbar
```{r}
sb_s2_MJ$results

sb.top.s2_MJ <- sb_s2_MJ$model_fits$Lat_Lon_Turb_Sal

summary(sb.top.s2_MJ)
```


#### Sharpnose
```{r, eval=TRUE}
sn_s2_MJ$results

sn.top.s2_MJ <- sn_s2_MJ$model_fits$Lat_Lon_Temp_Turb_Oxy_Sal

summary(sn.top.s2_MJ)
```


```{r, eval=TRUE}
par(mfrow = c(2,2))

gam.check(sn.top.s2_MJ)
```


```{r, eval=TRUE}
par(mfrow = c(1,1))

for(i in 2:6 ){
  
  plot( sn.top.s2_MJ,
       select = i)
  abline(h = 0, col = "red", lty = 3)

  }
```




#### Spinner
```{r}
sp_s2_MJ$results ### top 11 dAIC < 4
### Lat_Lon in Top 2

sp.top.s2_MJ <- sp_s2_MJ$model_fits$Root_Dep_Temp_Turb_Oxy_Sal

summary(sp.top.s2_MJ)

sp.top2.s2_MJ <- sp_s2_MJ$model_fits$Lat_Lon_Root_Dep_Temp_Turb_Oxy_Sal

summary(sp.top2.s2_MJ)
```


#### Tiger
```{r}
ti_s2_MJ$results ### Top 110 dAIC < 4

### Lat_Lon in Top 57

ti.top.s2_MJ <- ti_s2_MJ$model_fits$Temp_Oxy_Dis_Bottyp

summary(ti.top.s2_MJ)


ti.top57.s2_MJ <- ti_s2_MJ$model_fits$Lat_Lon_Oxy_Dis_Bottyp

summary(ti.top57.s2_MJ)
```



