---
title: "Blacknose Top GAM Models (First Look)"
author: "Alex Benecke"
date: "October 5, 2018"
output:     
  html_document:
    df_print: paged
    toc: true
    toc_float: true
    toc_depth: 5
    fig_width: 10
    fig_height: 10
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

### Load Packages
library(FSA)
library(tidyverse)
library(dplyr)
library(magrittr)
library(scales)
library(mgcv)
library(sciplot)
library(pipeR)

```

```{r, echo = FALSE}

Sp_Selct <- 1 #### <<<<<<<<<<<<  IMPORTANT MAKE SURE THIS  IS CORRECT

name_lst <- list(bn = c("bn_s1_FA", "bn_s1_FJ", "bn_s1_MA", "bn_s1_MJ", ### Sp_Selct = 1
                        "bn_s2_FA", "bn_s2_FJ", "bn_s2_MA", "bn_s2_MJ")
                 ,
                 bt = c("bt_s1_FA", "bt_s1_FJ", "bt_s1_MA", "bt_s1_MJ", ### Sp_Selct = 2
                        "bt_s2_FA", "bt_s2_FJ", "bt_s2_MA", "bt_s2_MJ")
                 ,
                 sn = c("sn_s1_FA", "sn_s1_FJ", "sn_s1_MA", "sn_s1_MJ", ### Sp_Selct = 3
                        "sn_s2_FA", "sn_s2_FJ", "sn_s2_MA", "sn_s2_MJ"))

filenames <- list.files(c("output/output_GAM/strat1/Female/Adult/",
                          "output/output_GAM/strat1/Female/Juvenile/",
                          "output/output_GAM/strat1/Male/Adult/",
                          "output/output_GAM/strat1/Male/Juvenile/",
                          "output/output_GAM/strat2/Female/Adult/",
                          "output/output_GAM/strat2/Female/Juvenile/",
                          "output/output_GAM/strat2/Male/Adult/",
                          "output/output_GAM/strat2/Male/Juvenile/")
                        ,
                        pattern="bn_*" #### <<<<<<<<<<<<  IMPORTANT MAKE SURE THIS  IS CORRECT
                        , full.names=TRUE, recursive = TRUE)

```

# Strata 1 

## Female 

### **Adult**

```{r, echo = FALSE}

selct_mod = 1 #### <<<<<<<<<<<<  IMPORTANT MAKE SURE THIS  IS CORRECT

load(file = filenames[selct_mod]) 

mod_lst <- get(name_lst[[Sp_Selct]][selct_mod])

mod_results <- mod_lst$results %>% data.frame()


best_models <- which(mod_results$delta_AIC < 4)

top_mods <- mod_results[ c(best_models), c(1:4,7)] 


```
```{r, echo=FALSE}
filenames[selct_mod]

name_lst[[Sp_Selct]][selct_mod]
```

`r top_mods `

#### *Best Model*

```{r, echo=FALSE}
  par(mfrow=c(2,2))
  as.character(mod_lst$results$model[best_models[1]]) %>%
    print() %>%
    mod_lst$model_fits[[.]] %>>%
    (~tmp) %>%
    gam.check()
  
  plot(tmp,
       pages = 1,
       scale = 0,
       all.terms = TRUE)
  
summary(tmp)  
  
```
```{r, echo=FALSE}
rm(selct_mod, mod_lst, mod_results, best_models, top_mods, tmp)
```



### **Juvenile**

```{r, echo = FALSE}

selct_mod = 2 #### <<<<<<<<<<<<  IMPORTANT MAKE SURE THIS  IS CORRECT

load(file = filenames[selct_mod]) 

mod_lst <- get(name_lst[[Sp_Selct]][selct_mod])

mod_results <- mod_lst$results %>% data.frame()


best_models <- which(mod_results$delta_AIC < 4)

top_mods <- mod_results[ c(best_models), c(1:4,7)] 


```
```{r, echo=FALSE}
filenames[selct_mod]

name_lst[[Sp_Selct]][selct_mod]
```

`r top_mods `

#### *Best Model*

```{r, echo=FALSE}
  par(mfrow=c(2,2))
  as.character(mod_lst$results$model[best_models[1]]) %>%
    print() %>%
    mod_lst$model_fits[[.]] %>>%
    (~tmp) %>%
    gam.check()
  
  plot(tmp,
       pages = 1,
       scale = 0,
       all.terms = TRUE)
  
summary(tmp)
```
```{r, echo=FALSE}
rm(selct_mod, mod_lst, mod_results, best_models, top_mods, tmp)
```



## Male 


### **Adult** 


```{r, echo = FALSE}

selct_mod = 3 #### <<<<<<<<<<<<  IMPORTANT MAKE SURE THIS  IS CORRECT

load(file = filenames[selct_mod]) 

mod_lst <- get(name_lst[[Sp_Selct]][selct_mod])

mod_results <- mod_lst$results %>% data.frame()


best_models <- which(mod_results$delta_AIC < 4)

top_mods <- mod_results[ c(best_models), c(1:4,7)] 


```
```{r, echo=FALSE}
filenames[selct_mod]

name_lst[[Sp_Selct]][selct_mod]
```

`r top_mods `

#### *Best Model*

```{r, echo=FALSE}
  par(mfrow=c(2,2))
  as.character(mod_lst$results$model[best_models[1]]) %>%
    print() %>%
    mod_lst$model_fits[[.]] %>>%
    (~tmp) %>%
    gam.check()
  
  plot(tmp,
       pages = 1,
       scale = 0,
       all.terms = TRUE)
  
summary(tmp)
```
```{r, echo=FALSE}
rm(selct_mod, mod_lst, mod_results, best_models, top_mods, tmp)
```




### **Juvenile**


```{r, echo = FALSE}

selct_mod = 4 #### <<<<<<<<<<<<  IMPORTANT MAKE SURE THIS  IS CORRECT

load(file = filenames[selct_mod]) 

mod_lst <- get(name_lst[[Sp_Selct]][selct_mod])

mod_results <- mod_lst$results %>% data.frame()


best_models <- which(mod_results$delta_AIC < 4)

top_mods <- mod_results[ c(best_models), c(1:4,7)] 


```
```{r, echo=FALSE}
filenames[selct_mod]

name_lst[[Sp_Selct]][selct_mod]
```

`r top_mods `

#### *Best Model*

```{r, echo=FALSE}
  par(mfrow=c(2,2))
  as.character(mod_lst$results$model[best_models[1]]) %>%
    print() %>%
    mod_lst$model_fits[[.]] %>>%
    (~tmp) %>%
    gam.check()
  
  plot(tmp,
       pages = 1,
       scale = 0,
       all.terms = TRUE)
  
summary(tmp)
```
```{r, echo=FALSE}
rm(selct_mod, mod_lst, mod_results, best_models, top_mods, tmp)
```




# Strata 2 


## Female

### **Adult** 



```{r, echo = FALSE}

selct_mod = 5 #### <<<<<<<<<<<<  IMPORTANT MAKE SURE THIS  IS CORRECT

load(file = filenames[selct_mod]) 

mod_lst <- get(name_lst[[Sp_Selct]][selct_mod])

mod_results <- mod_lst$results %>% data.frame()


best_models <- which(mod_results$delta_AIC < 4)

top_mods <- mod_results[ c(best_models), c(1:4,7)] 


```
```{r, echo=FALSE}
filenames[selct_mod]

name_lst[[Sp_Selct]][selct_mod]
```

`r top_mods `

#### *Best Model*

```{r, echo=FALSE}
  par(mfrow=c(2,2))
  as.character(mod_lst$results$model[best_models[1]]) %>%
    print() %>%
    mod_lst$model_fits[[.]] %>>%
    (~tmp) %>%
    gam.check()
  
  plot(tmp,
       pages = 1,
       scale = 0,
       all.terms = TRUE)
  
summary(tmp)
```
```{r, echo=FALSE}
rm(selct_mod, mod_lst, mod_results, best_models, top_mods, tmp)
```



### **Juvenile**



```{r, echo = FALSE}

selct_mod = 6 #### <<<<<<<<<<<<  IMPORTANT MAKE SURE THIS  IS CORRECT

load(file = filenames[selct_mod]) 

mod_lst <- get(name_lst[[Sp_Selct]][selct_mod])

mod_results <- mod_lst$results %>% data.frame()


best_models <- which(mod_results$delta_AIC < 4)

top_mods <- mod_results[ c(best_models), c(1:4,7)] 


```
```{r, echo=FALSE}
filenames[selct_mod]

name_lst[[Sp_Selct]][selct_mod]
```

`r top_mods `

#### *Best Model*

```{r, echo=FALSE}
  par(mfrow=c(2,2))
  as.character(mod_lst$results$model[best_models[1]]) %>%
    print() %>%
    mod_lst$model_fits[[.]] %>>%
    (~tmp) %>%
    gam.check()
  
  plot(tmp,
       pages = 1,
       scale = 0,
       all.terms = TRUE)
  
summary(tmp)
```
```{r, echo=FALSE}
rm(selct_mod, mod_lst, mod_results, best_models, top_mods, tmp)
```



## Male

### **Adult** 



```{r, echo = FALSE}

selct_mod = 7 #### <<<<<<<<<<<<  IMPORTANT MAKE SURE THIS  IS CORRECT

load(file = filenames[selct_mod]) 

mod_lst <- get(name_lst[[Sp_Selct]][selct_mod])

mod_results <- mod_lst$results %>% data.frame()


best_models <- which(mod_results$delta_AIC < 4)

top_mods <- mod_results[ c(best_models), c(1:4,7)] 


```
```{r, echo=FALSE}
filenames[selct_mod]

name_lst[[Sp_Selct]][selct_mod]
```

`r top_mods `

#### *Best Model*

```{r, echo=FALSE}
  par(mfrow=c(2,2))
  as.character(mod_lst$results$model[best_models[1]]) %>%
    print() %>%
    mod_lst$model_fits[[.]] %>>%
    (~tmp) %>%
    gam.check()
  
  plot(tmp,
       pages = 1,
       scale = 0,
       all.terms = TRUE)
  
summary(tmp)
```
```{r, echo=FALSE}
rm(selct_mod, mod_lst, mod_results, best_models, top_mods, tmp)
```



### **Juvenile**



```{r, echo = FALSE}

selct_mod = 8 #### <<<<<<<<<<<<  IMPORTANT MAKE SURE THIS  IS CORRECT

load(file = filenames[selct_mod]) 

mod_lst <- get(name_lst[[Sp_Selct]][selct_mod])

mod_results <- mod_lst$results %>% data.frame()


best_models <- which(mod_results$delta_AIC < 4)

top_mods <- mod_results[ c(best_models), c(1:4,7)] 


```
```{r, echo=FALSE}
filenames[selct_mod]

name_lst[[Sp_Selct]][selct_mod]
```

`r top_mods `

#### *Best Model*

```{r, echo=FALSE}
  par(mfrow=c(2,2))
  as.character(mod_lst$results$model[best_models[1]]) %>%
    print() %>%
    mod_lst$model_fits[[.]] %>>%
    (~tmp) %>%
    gam.check()
  
  plot(tmp,
       pages = 1,
       scale = 0,
       all.terms = TRUE)
  
summary(tmp)
```
```{r, echo=FALSE}
rm(selct_mod, mod_lst, mod_results, best_models, top_mods, tmp)
```


# Appendix

Need to repeat loading of models and make appendix section with all Models and Alternative Models with AIC less than 4

#### Alternative models $\Delta ~ AIC \leq 4$

```{r, include=FALSE, eval=FALSE}


for(i in 2:length(best_models)){
  
  par(mfrow=c(2,2))
  as.character(mod_lst$results$model[best_models[i]]) %>%
    print() %>%
    mod_lst$model_fits[[.]] %>>%
    (~tmp) %>%
    gam.check()
  
  plot(tmp,
       pages = 1,
       scale = 0)
  
}
```



### All Models

```{r, include=FALSE, eval=FALSE}
selct_mod = 1

 name_lst[[Sp_Selct]][selct_mod]

```




