---
title: "Fit Gams"
author: "Alex Benecke"
date: "August 6, 2018"
output:   
  html_document:
    df_print: paged
    toc: true
    toc_float: true
    toc_depth: 4
    fig_width: 8
    fig_height: 6
editor_options: 
  chunk_output_type: console
---

```{r Load Packages, include=FALSE}
### Load Packages
library(FSA)
library(tidyverse)
library(dplyr)
library(magrittr)
library(scales)
library(mgcv)
library(sciplot)
#source("plot_centered_mean.R")

source("5_functions/dropbox_fn.R") # For interacting with dropbox
proj = "shark" # Specify project where data is stored 

source("5_functions/model_selection_fn.R")
```

I will fit Gam Models here for all species using 2 strata.

i. Presence abscence uith binomial error distribution and log link

ii. CPUE positive catch only with a Gamma error distribution and a log link





```{r Load Data, echo=FALSE, include=FALSE}
### Blacknose
blacknose <- read_csv_fn( "data/clean-data/blacknose.csv", proj) %>%
  mutate(YEAR = factor(YEAR), 
         MONTH = factor(strftime(DATE, format = "%b")))

### Blacktip
blacktip <- read_csv_fn( "data/clean-data/blacktip.csv", proj) %>%
  mutate(YEAR = factor(YEAR), 
         MONTH = factor(strftime(DATE, format = "%b")))

### Bull
bull <- read_csv_fn( "data/clean-data/bull.csv", proj) %>%
  mutate(YEAR = factor(YEAR), 
         MONTH = factor(strftime(DATE, format = "%b")))

### Sandbar
sandbar <- read_csv_fn( "data/clean-data/sandbar.csv", proj) %>%
  mutate(YEAR = factor(YEAR), 
         MONTH = factor(strftime(DATE, format = "%b")))

### Sharpnose
sharpnose <- read_csv_fn( "data/clean-data/sharpnose.csv", proj) %>%
  mutate(YEAR = factor(YEAR), 
         MONTH = factor(strftime(DATE, format = "%b")))

### Silky
silky <- read_csv_fn( "data/clean-data/silky.csv", proj) %>%
  mutate(YEAR = factor(YEAR), 
         MONTH = factor(strftime(DATE, format = "%b")))

### Spinner
spinner <- read_csv_fn( "data/clean-data/spinner.csv", proj) %>%
  mutate(YEAR = factor(YEAR), 
         MONTH = factor(strftime(DATE, format = "%b")))

### Tiger
tiger <- read_csv_fn( "data/clean-data/tiger.csv", proj) %>%
  mutate(YEAR = factor(YEAR), 
         MONTH = factor(strftime(DATE, format = "%b")))

### Strata 1 list
strat1 <- list(blacknose = blacknose,
              blacktip = blacktip,
              bull = bull,
              sandbar = sandbar,
              sharpnose = sharpnose,
              silky = silky,
              spinner = spinner,
              tiger = tiger)


### Strata 2 List


strat2 <- list(blacknose = blacknose %>% subset(pres == 1),
              blacktip = blacktip %>% subset(pres == 1),
              bull = bull %>% subset(pres == 1),
              sandbar = sandbar %>% subset(pres == 1),
              sharpnose = sharpnose %>% subset(pres == 1),
              silky = silky %>% subset(pres == 1),
              spinner = spinner %>% subset(pres == 1),
              tiger = tiger %>% subset(pres == 1))
```


```{r check that strat1 and strat2 are different, include=FALSE}
nrow(strat2$blacknose)
nrow(strat1$blacknose)
```




## Strata 1 ##

```{r fit strata 1 GAM Models}

output_names_strat1 <- c("bn_gam_strat_1", "bt_gam_strat_1", "bu_gam_strat_1", "sb_gam_strat_1", 
                         "sn_gam_strat_1", "si_gam_strat_1", "sp_gam_strat_1", "ti_gam_strat_1")

time_fit_strat1 <- c("bn.time.1", "bt.time.1", "bu.time.1", "sb.time.1",
                     "sn.time.1", "si.time.1", "sp.time.1", "ti.time.1")



for(a in 1:length(strat1)){
  
time_fit_strat1[a] <- system.time(
  
  output_names_strat1[a] <-   gam_select_fn(data = strat1[[a]],
                                            family = binomial(link = log),
                                            response = "pres",
                                            smooth_terms = c("s(STARTLON, STARTLAT, k = k_i[[i]]['k_0','Lat-Lon'])",
                                                             "s(I(AVG.DEPTH^0.25), k = k_i[[i]]['k_0', 'Dep'])",
                                                             "s(TEMPBOTM, k = k_i[[i]]['k_0', 'Temp'])",
                                                             "s(TURBBOTM, k = k_i[[i]]['k_0', 'Turb'])",
                                                             "s(OXYBOTM, k = k_i[[i]]['k_0', 'Oxy'])",
                                                             "s(SALBOTM, k = k_i[[i]]['k_0', 'Sal'])",
                                                             "s(Dis.to.SHORE, k = k_i[[i]]['k_0', 'Dis'])",
                                                             "s(YEAR, bs = 're')"),
                                            smooth_names = c("Lat_Lon","Root_Dep", "Temp", "Turb",
                                                   "Oxy", "Sal", "Dis"),
                                            rand_eff_smooth = "yr",
                                            gamma = 1,
                                            in_parallel = FALSE,
                                            est_k = TRUE)
  
)

save(output_names_strat1[a], file = paste0("output/output_Gam/", output_names_strat1[a], ".rda"))
  
}


```

```{r test}

test_1 <-   gam_select_fn(data = strat1[[1]],
                family = binomial(link = log),
                response = "pres",
                smooth_terms = c("s(STARTLON, STARTLAT, k = k_i[[i]]['k_0','Lat-Lon'])",
                                 "s(I(AVG.DEPTH^0.25), k = k_i[[i]]['k_0', 'Dep'])",
                                 "s(TEMPBOTM, k = k_i[[i]]['k_0', 'Temp'])",
                                 "s(TURBBOTM, k = k_i[[i]]['k_0', 'Turb'])",
                                 "s(OXYBOTM, k = k_i[[i]]['k_0', 'Oxy'])",
                                 "s(SALBOTM, k = k_i[[i]]['k_0', 'Sal'])",
                                 "s(Dis.to.SHORE, k = k_i[[i]]['k_0', 'Dis'])",
                                 "s(YEAR, bs = 're')"),
                                  smooth_names = c("Lat_Lon","Dep", "Temp", "Turb",
                                                   "Oxy", "Sal", "Dis"),
                rand_eff_smooth = "yr",
                gamma = 1,
                in_parallel = FALSE,
                est_k = TRUE)

```


## Strata2


```{r fit strata 1 GAM Models}

output_names_strat2 <- c("bn_gam_strat_2", "bt_gam_strat_2", "bu_gam_strat_2", "sb_gam_strat_2", 
                         "sn_gam_strat_2", "si_gam_strat_2", "sp_gam_strat_2", "ti_gam_strat_2")

time_fit_strat2 <- c("bn.time.2", "bt.time.2", "bu.time.2", "sb.time.2",
                     "sn.time.2", "si.time.2", "sp.time.2", "ti.time.2")



for(a in 1:length(strat1)){
  
time_fit_strat2[b] <- system.time(
  
  output_names_strat2[b] <-   gam_select_fn(data = strat2[[b]],
                                            family = Gamma(link = log),
                                            response = "(cpe + 1)",
                                            smooth_terms = c("s(STARTLON, STARTLAT, k = k_i[[i]]['k_0','Lat-Lon'])",
                                                             "s(I(AVG.DEPTH^0.25), k = k_i[[i]]['k_0', 'Dep'])",
                                                             "s(TEMPBOTM, k = k_i[[i]]['k_0', 'Temp'])",
                                                             "s(TURBBOTM, k = k_i[[i]]['k_0', 'Turb'])",
                                                             "s(OXYBOTM, k = k_i[[i]]['k_0', 'Oxy'])",
                                                             "s(SALBOTM, k = k_i[[i]]['k_0', 'Sal'])",
                                                             "s(Dis.to.SHORE, k = k_i[[i]]['k_0', 'Dis'])",
                                                             "s(YEAR, bs = 're')"),
                                            smooth_names = c("Lat_Lon","Root_Dep", "Temp", "Turb",
                                                   "Oxy", "Sal", "Dis"),
                                            rand_eff_smooth = "yr",
                                            gamma = 1,
                                            in_parallel = FALSE,
                                            est_k = TRUE)
  
)

save(output_names_strat2[b], file = paste0("output/output_Gam/", output_names_strat2[b], ".rda"))
  
}


```

```{r test strata 2}

  gam_select_fn(data = strat2[[1]],
                family = Gamma(link = log),
                response = "(cpe + 1)",
                smooth_terms = c("s(STARTLON, STARTLAT, k = k_i[[i]]['k_0','Lat-Lon'])",
                                 "s(I(AVG.DEPTH^0.25), k = k_i[[i]]['k_0', 'Dep'])",
                                 "s(TEMPBOTM, k = k_i[[i]]['k_0', 'Temp'])",
                                 "s(TURBBOTM, k = k_i[[i]]['k_0', 'Turb'])",
                                 "s(OXYBOTM, k = k_i[[i]]['k_0', 'Oxy'])",
                                 "s(SALBOTM, k = k_i[[i]]['k_0', 'Sal'])",
                                 "s(Dis.to.SHORE, k = k_i[[i]]['k_0', 'Dis'])",
                                 "s(YEAR, bs = 're')"),
                                  smooth_names = c("Lat_Lon","Dep", "Temp", "Turb",
                                                   "Oxy", "Sal", "Dis"),
                rand_eff_smooth = "yr",
                gamma = 1,
                in_parallel = FALSE,
                est_k = TRUE)

``














