---
title: "GAM Model Fitting"
author: "Alex Benecke"
date: "August 15, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Load Packages}
library(FSA)
library(magrittr)

source("5_functions/load_data.R")

source("5_functions/dropbox_fn.R") # For interacting with dropbox
proj = "shark" # Specify project where data is stored 

source("5_functions/model_selection_fn.R")
```

```{r load data}
eff3 <- read_csv_fn( "data/clean-data/CPUE3.csv", proj, na.strings = c(NA,"")) %>%
  subset(common == "Blacknose" | common == "Blacktip" | common == "Sharpnose") %>%
  droplevels() %>%
  na.omit()

#eff3 <- read.csv("data/raw-data/CPUE3.csv", na.strings = c(NA, "")) %>%
#  mutate(year = factor(year), pres = factor(pres))
str(eff3)

```


## Strata 1 Presence
```{r Setup Strata 1}
s1.response <- "pres"

smooth.terms <- c("s(startdepth, k = k_i[[i]]['k_0', 'Dep'])",
                     "s(tempbotm, k = k_i[[i]]['k_0', 'Temp'])",
                     "s(turbbotm, k = k_i[[i]]['k_0', 'Turb'])",
                     "s(oxybotm, k = k_i[[i]]['k_0', 'Oxy'])",
                     "s(salbotm, k = k_i[[i]]['k_0', 'Sal'])",
                     "s(Dis.to.Shore, k = k_i[[i]]['k_0', 'Dis'])",
                     "bottype4")

constant_term = "s(startlon, startlat, k = k_i[[i]]['k_0', 'LatLon'] + 45)"

re_term <- "s(year, bs = 're')"
  

smooth_names <- c("LatLon","Dep", "Temp", "Turb", "Oxy", "Sal", "Dis", "Bottype")


s1.family <- binomial(link = logit) 

sp <- c("bn", "bt", "sn")

```


### Female Adult (Strata 1 Presence) 
```{r load data S1 Female Adult}

Adult_S1 <- load_data(data = eff3[eff3$maturity == "A",] %>% droplevels(), strata = 1)

Adult_Female_S1 <- Adult_S1$Female

str(Adult_Female_S1$blacknose)
str(Adult_Female_S1$blacktip)
str(Adult_Female_S1$sharpnose)
```

#### Fitting All S1 Adult Female GAM Models

```{r Fitting All S1_FA GAMs}

for(i in 1:length(Adult_Female_S1)){
  
  assign( paste0( "time_", sp[i], "_s1_FA" ),
         system.time(
          
           assign( paste0( sp[i], "_s1_FA" ),
                  gam_select_fn(data = Adult_Female_S1[[i]],
                                
                                response = s1.response,
                            
                                smooth_terms = smooth.terms,
                                
                                constant_term = constant_term,
                                
                                re_term = re_term,
                            
                                smooth_names = smooth_names,
                            
                                family = s1.family,
                            
                                est_k = TRUE)) 
           
         )
         )
  
}

save( bn_s1_FA, file = "output/output_GAM/strat1/Female/Adult/bn_s1_FA.rda"   )

save( bt_s1_FA, file = "output/output_GAM/strat1/Female/Adult/bt_s1_FA.rda"   )

save( sn_s1_FA, file = "output/output_GAM/strat1/Female/Adult/sn_s1_FA.rda"   )



time_s1_FA <- list(time_bn_s1_FA = time_bn_s1_FA,
                   time_bt_s1_FA = time_bt_s1_FA,
                   time_sn_s1_FA = time_sn_s1_FA)


save(time_s1_FA, file = "output/output_GAM/strat1/Female/Adult/time_s1_FA.rda")

```


### Female Juvenile (Strata 1 Presence)
```{r Load data S1 Female Juvenile}
Juvenile_S1 <- load_data(data = eff3[eff3$maturity == "J",] %>% droplevels(), strata = 1)

Juvenile_Female_S1 <- Juvenile_S1$Female

str(Juvenile_Female_S1$blacknose)
```

#### Fitting All s1 Juvenile Female GAMs 

```{r Fitting All S1_FJ GAMs}

for(i in 1:length(Juvenile_Female_S1)){
  
  assign( paste0( "time_", sp[i], "_s1_FJ" ),
         system.time(
          
           assign( paste0( sp[i], "_s1_FJ" ),
                  gam_select_fn(data = Juvenile_Female_S1[[i]],
                                
                                response = s1.response,
                            
                                smooth_terms = smooth.terms,
                                
                                constant_term = constant_term,
                                
                                re_term = re_term,
                            
                                smooth_names = smooth_names,
                            
                                family = s1.family,
                            
                                est_k = TRUE)) 
           
         )
         )
}

save( bn_s1_FJ, file = "output/output_GAM/strat1/Female/Juvenile/bn_s1_FJ.rda"   )

save( bt_s1_FJ, file = "output/output_GAM/strat1/Female/Juvenile/bt_s1_FJ.rda"   )

save( sn_s1_FJ, file = "output/output_GAM/strat1/Female/Juvenile/sn_s1_FJ.rda"   )




time_s1_FJ <- list(time_bn_s1_FJ = time_bn_s1_FJ,
                   time_bt_s1_FJ = time_bt_s1_FJ,
                   time_sn_s1_FJ = time_sn_s1_FJ)


save(time_s1_FJ, file = "output/output_GAM/strat1/Female/Juvenile/time_s1_FJ.rda")
```



### Male Adult (Strata 1 Presence)
```{r Load data s1 Adult Male}
Adult_Male_S1 <- Adult_S1$Male

str(Adult_Male_S1$blacknose)
```

#### Fitting All s1 Adult Male GAMs 

```{r Fitting All S1_MA GAMs}

for(i in 1:length(Adult_Male_S1)){
  
  assign( paste0( "time_", sp[i], "_s1_MA" ),
         system.time(
          
           assign( paste0( sp[i], "_s1_MA" ),
                  gam_select_fn(data = Adult_Male_S1[[i]],
                                
                                response = s1.response,
                            
                                smooth_terms = smooth.terms,
                                
                                constant_term = constant_term,
                                
                                re_term = re_term,
                            
                                smooth_names = smooth_names,
                            
                                family = s1.family,
                            
                                est_k = TRUE)) 
           
         )
         )
}

save( bn_s1_MA, file = "output/output_GAM/strat1/Male/Adult/bn_s1_MA.rda"   )

save( bt_s1_MA, file = "output/output_GAM/strat1/Male/Adult/bt_s1_MA.rda"   )

save( sn_s1_MA, file = "output/output_GAM/strat1/Male/Adult/sn_s1_MA.rda"   )




time_s1_MA <- list(time_bn_s1_MA = time_bn_s1_MA,
                   time_bt_s1_MA = time_bt_s1_MA,
                   time_sn_s1_MA = time_sn_s1_MA)


save(time_s1_MA, file = "output/output_GAM/strat1/Male/Adult/time_s1_MA.rda")
```



### Male Juvenile (Strata 1 Presence)
```{r Load data S1 Juvenile Male }
Juvenile_Male_S1 <- Juvenile_S1$Male

str(Juvenile_Male_S1$blacknose)
```

#### Fitting All s1 Juvenile Male GAMs 

```{r Fitting All S1_MJ GAMs}

for(i in 1:length(Juvenile_Male_S1)){
  
  assign( paste0( "time_", sp[i], "_s1_MJ" ),
         system.time(
          
           assign( paste0( sp[i], "_s1_MJ" ),
                  gam_select_fn(data = Juvenile_Male_S1[[i]],
                                
                                response = s1.response,
                            
                                smooth_terms = smooth.terms,
                                
                                constant_term = constant_term,
                                
                                re_term = re_term,
                            
                                smooth_names = smooth_names,
                            
                                family = s1.family,
                            
                                est_k = TRUE)) 
           
         )
         )
}

save( bn_s1_MJ, file = "output/output_GAM/strat1/Male/Juvenile/bn_s1_MJ.rda"   )

save( bt_s1_MJ, file = "output/output_GAM/strat1/Male/Juvenile/bt_s1_MJ.rda"   )

save( sn_s1_MJ, file = "output/output_GAM/strat1/Male/Juvenile/sn_s1_MJ.rda"   )



time_s1_MJ <- list(time_bn_s1_MJ = time_bn_s1_MJ,
                   time_bt_s1_MJ = time_bt_s1_MJ,
                   time_sn_s1_MJ = time_sn_s1_MJ)


save(time_s1_MJ, file = "output/output_GAM/strat1/Male/Juvenile/time_s1_MJ.rda")
```




## Strata 2 Abundance
```{r Setup Strata 2}
s2.response <- "log(CPUE + 1)"

smooth.terms <- c("s(startdepth, k = k_i[[i]]['k_0', 'Dep'])",
                     "s(tempbotm, k = k_i[[i]]['k_0', 'Temp'])",
                     "s(turbbotm, k = k_i[[i]]['k_0', 'Turb'])",
                     "s(oxybotm, k = k_i[[i]]['k_0', 'Oxy'])",
                     "s(salbotm, k = k_i[[i]]['k_0', 'Sal'])",
                     "s(Dis.to.Shore, k = k_i[[i]]['k_0', 'Dis'])",
                     "bottype4")

constant_term = "s(startlon, startlat, k = k_i[[i]]['k_0', 'LatLon'] + 45)"

re_term <- "s(year, bs = 're')"
  

smooth_names <- c("LatLon","Dep", "Temp", "Turb", "Oxy", "Sal", "Dis", "Bottype")

s2.family <- Gamma(link = log) 

sp <- c("bn", "bt", "sn")

```

### Female Adult (Strata 2 Abundance)  
```{r load data S2 Female Adult}

Adult_S2 <- load_data(data = eff3[eff3$maturity == "A",] %>% droplevels(), strata = 2)

Adult_Female_S2 <- Adult_S2$Female

str(Adult_Female_S2$blacknose)
```

#### Fitting All S2 Adult Female GAM Models

```{r Fitting All S2_FA GAMs}


for(i in 1:length(Adult_Female_S2)){
  
  assign( paste0( "time_", sp[i], "_s2_FA" ),
         system.time(
          
           assign( paste0( sp[i], "_s2_FA" ),
                  gam_select_fn(data = Adult_Female_S2[[i]],
                                
                                response = s2.response,
                            
                                smooth_terms = smooth.terms,
                                
                                constant_term = constant_term,
                                
                                re_term = re_term,
                            
                                smooth_names = smooth_names,
                            
                                family = s2.family,
                            
                                est_k = TRUE)) 
           
         )
         )
}


save( bn_s2_FA, file = "output/output_GAM/strat2/Female/Adult/bn_s2_FA.rda"   )

save( bt_s2_FA, file = "output/output_GAM/strat2/Female/Adult/bt_s2_FA.rda"   )

save( sn_s2_FA, file = "output/output_GAM/strat2/Female/Adult/sn_s2_FA.rda"   )


time_s2_FA <- list(time_bn_s2_FA = time_bn_s2_FA,
                   time_bt_s2_FA = time_bt_s2_FA,
                   time_sn_s2_FA = time_sn_s2_FA)


save(time_s2_FA, file = "output/output_GAM/strat2/Female/Adult/time_s2_FA.rda")

```


### Female Juvenile (Strata 2 Abundance)
```{r Load data S2 Female Juvenile}
Juvenile_S2 <- load_data(data = eff3[eff3$maturity == "J",] %>% droplevels(), strata = 2)

Juvenile_Female_S2 <- Juvenile_S2$Female

str(Juvenile_Female_S2$blacknose)
```

#### Fitting All s2 Juvenile Female GAMs 

```{r Fitting All S2_FJ GAMs}

for(i in 1:length(Juvenile_Female_S2)){
  
  assign( paste0( "time_", sp[i], "_s2_FJ" ),
         system.time(
          
           assign( paste0( sp[i], "_s2_FJ" ),
                  gam_select_fn(data = Juvenile_Female_S2[[i]],
                                
                                response = s2.response,
                            
                                smooth_terms = smooth.terms,
                                
                                constant_term = constant_term,
                                
                                re_term = re_term,
                            
                                smooth_names = smooth_names,
                            
                                family = s2.family,
                            
                                est_k = TRUE)) 
           
         )
         )
}

save( bn_s2_FJ, file = "output/output_GAM/strat2/Female/Juvenile/bn_s2_FJ.rda"   )

save( bt_s2_FJ, file = "output/output_GAM/strat2/Female/Juvenile/bt_s2_FJ.rda"   )

save( sn_s2_FJ, file = "output/output_GAM/strat2/Female/Juvenile/sn_s2_FJ.rda"   )



time_s2_FJ <- list(time_bn_s2_FJ = time_bn_s2_FJ,
                   time_bt_s2_FJ = time_bt_s2_FJ,
                   time_sn_s2_FJ = time_sn_s2_FJ)


save(time_s2_FJ, file = "output/output_GAM/strat2/Female/Juvenile/time_s2_FJ.rda")
```


### Male Adult (Strata 2 Abundance)
```{r Load data s2 Adult Male}
Adult_Male_S2 <- Adult_S2$Male

str(Adult_Male_S2$blacknose)
```

#### Fitting All s2 Adult Male GAMs 

```{r Fitting All S2_MA GAMs}

for(i in 1:length(Adult_Male_S2)){
  
  assign( paste0( "time_", sp[i], "_s2_MA" ),
         system.time(
          
           assign( paste0( sp[i], "_s2_MA" ),
                  gam_select_fn(data = Adult_Male_S2[[i]],
                                
                                response = s2.response,
                            
                                smooth_terms = smooth.terms,
                                
                                constant_term = constant_term,
                                
                                re_term = re_term,
                            
                                smooth_names = smooth_names,
                            
                                family = s2.family,
                            
                                est_k = TRUE)) 
           
         )
         )
}

save( bn_s2_MA, file = "output/output_GAM/strat2/Male/Adult/bn_s2_MA.rda"   )

save( bt_s2_MA, file = "output/output_GAM/strat2/Male/Adult/bt_s2_MA.rda"   )

save( sn_s2_MA, file = "output/output_GAM/strat2/Male/Adult/sn_s2_MA.rda"   )


time_s2_MA <- list(time_bn_s2_MA = time_bn_s2_MA,
                   time_bt_s2_MA = time_bt_s2_MA,
                   time_sn_s2_MA = time_sn_s2_MA)


save(time_s2_MA, file = "output/output_GAM/strat2/Male/Adult/time_s2_MA.rda")
```


### Male Juvenile (Strata 2 Abundance)

```{r Load data S2 Juvenile Male }
Juvenile_Male_S2 <- Juvenile_S2$Male

str(Juvenile_Male_S2$blacknose)
```

#### Fitting All s2 Juvenile Male GAMs 

```{r Fitting All S2_MJ GAMs}

for(i in 1:length(Juvenile_Male_S2)){
  
  assign( paste0( "time_", sp[i], "_s2_MJ" ),
         system.time(
          
           assign( paste0( sp[i], "_s2_MJ" ),
                  gam_select_fn(data = Juvenile_Male_S2[[i]],
                                
                                response = s2.response,
                            
                                smooth_terms = smooth.terms,
                                
                                constant_term = constant_term,
                                
                                re_term = re_term,
                            
                                smooth_names = smooth_names,
                            
                                family = s2.family,
                            
                                est_k = TRUE)) 
           
         )
         )
}

save( bn_s2_MJ, file = "output/output_GAM/strat2/Male/Juvenile/bn_s2_MJ.rda"   )

save( bt_s2_MJ, file = "output/output_GAM/strat2/Male/Juvenile/bt_s2_MJ.rda"   )

save( sn_s2_MJ, file = "output/output_GAM/strat2/Male/Juvenile/sn_s2_MJ.rda"   )


time_s2_MJ <- list(time_bn_s2_MJ = time_bn_s2_MJ,
                   time_bt_s2_MJ = time_bt_s2_MJ,
                   time_sn_s2_MJ = time_sn_s2_MJ)


save(time_s2_MJ, file = "output/output_GAM/strat2/Male/Juvenile/time_s2_MJ.rda")
```


